### 2016-03-16 photoz_paper/paper.tex
added files for photoz paper

\documentclass[reprint,aps,prd,superscriptaddress,showkeys,showpacs]{revtex4-1}
\usepackage{epsfig,amsmath,natbib}

\usepackage{aas_macros}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage{hyperref}
\usepackage{color}
\usepackage{pbox}
\usepackage{booktabs}
\usepackage[dvipsnames]{xcolor}

\hypersetup{
	colorlinks=false,
	citecolor=green
}

%%%%%%%%%%%%%%%%%
%Custom commands%
%%%%%%%%%%%%%%%%%

\newcommand{\bb}[1]{\mathbf{#1}}
\newcommand{\bbh}[1]{\mathbf{\hat{#1}}}
\newcommand{\h}[1]{\hat{#1}}
\newcommand\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
        \raise1pt\hbox{$<$}}}
\newcommand\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
        \raise1pt\hbox{$>$}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{Cosmology with photometric surveys: the effect of redshift errors on tomographic parameter constraints}

\author{Andrea Petri}
\email{apetri@phys.columbia.edu}
\affiliation{Department of Physics, Columbia University, New York, NY 10027, USA}
\affiliation{Physics Department, Brookhaven National Laboratory, Upton, NY 11973, USA}

\author{Morgan May}
\affiliation{Physics Department, Brookhaven National Laboratory, Upton, NY 11973, USA}

\author{Zolt\'an Haiman}
\affiliation{Department of Astronomy, Columbia University, New York, NY 10027, USA}

\date{\today}

\label{firstpage}

\begin{abstract}

\end{abstract}

\keywords{Weak Gravitational Lensing --- Simulations --- Methods: numerical, statistical}
\pacs{98.80.-k, 95.36.+x, 95.30.Sf, 98.62.Sb}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%% INTRO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
%

\citep{DodelsonSchneider13}

%%%%%%%%%%%%%%%%%%%%%%%%%% ACKNOWLEDGMENTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Acknowledgments}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{ref}

\label{lastpage}
\end{document}

### 2016-03-16 photoz_paper/Figures/generate.py

@@ -1,0 +1,28 @@
+#!/usr/bin/env python
+
+import sys,argparse
+sys.modules["mpi4py"] = None
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+from lenstools.statistics.ensemble import Ensemble
+from lenstools.statistics.database import Database
+
+
+###################################################################################################
+
+
+###########################################################################################################################################
+
+#Method dictionary
+method = dict()
+
+#Main
+def main():
+	cmd_args = parser.parse_args()
+	for fig in cmd_args.fig:
+		method[fig](cmd_args)
+
+if __name__=="__main__":
+	main()

### 2016-03-17 code/measure/measure_cross_power.py
hard code peak extremes and multipoles

@@ -45,8 +45,14 @@ def cross_power(maps,ell_edges,indices):
 measurer_kwargs = {
 	
 "measurer" : cross_power,
-"ell_edges" : pd.read_pickle("/global/homes/a/apetri/LSST100Parameters/data/edges.pkl")["ell_edges"].values,
-"indices" : zip(*np.triu_indices(5))
+"indices" : zip(*np.triu_indices(5)),
+"ell_edges" : np.array([  100.,   238.,   376.,   514.,   652.,   790.,   928.,  1066., 
+	1204.,  1342.,  1480.,  1618.,  1756.,  1894.,  2032.,  2170.,
+	2308.,  2446.,  2584.,  2722.,  2860.,  2998.,  3136.,  3274.,
+	3412.,  3550.,  3688.,  3826.,  3964.,  4102.,  4240.,  4378.,
+	4516.,  4654.,  4792.,  4930.,  5068.,  5206.,  5344.,  5482.,
+	5620.,  5758.,  5896.,  6034.,  6172.,  6310.,  6448.,  6586.,
+	6724.,  6862.,  7000.])
 	
 }
 

### 2016-03-17 code/library/featureDB.py
fix position file not found bug

@@ -49,8 +49,9 @@ def process_realization(realization,db_type,map_specs,sub_catalog,measurer,**kwa
 	"""
 
 	#Construct file names of shear and position catalogs
-	position_files = [ "/global/homes/a/apetri/LSST100Parameters/data/positions_bin{0}.fits".format(n) for n in range(1,len(map_specs["zbins"])+1) ]
-	shear_files = [ os.path.join(sub_catalog.storage_subdir,"WLshear_positions_bin{0}_{1:04d}r.fits".format(n,realization)) for n in range(1,len(map_specs["zbins"])+1) ]
+	position_file_path = os.path.join(sub_catalog.environment.storage,sub_catalog.cosmo_id,sub_catalog.geometry_id,sub_catalog.name)
+	position_files = [ os.path.join(position_file_path,"positions_bin{0}.fits".format(n)) for n in range(1,6) ]
+	shear_files = [ os.path.join(sub_catalog.storage_subdir,"WLshear_positions_bin{0}_{1:04d}r.fits".format(n,realization)) for n in range(1,6) ]
 
 	#Construct the kappa maps
 	maps = db_type.make_maps(shear_files,position_files,**map_specs)

### 2016-03-17 code/library/driver_mpi.py
override input table names and db names

@@ -138,8 +138,14 @@ def cosmo_constraints(batch,specs,settings=default_settings):
 	#First read in which kind of features are we combining
 	for feature in specs["features"]:
 
+		#Feature dbname
+		if "features_dbname" in specs[feature]:
+			features_dbname = specs[feature]["features_dbname"]
+		else:
+			features_dbname = getattr(settings,feature).dbname 
+
 		#Query the database
-		feature_dbfile = os.path.join(batch.storage,getattr(settings,feature).dbname)
+		feature_dbfile = os.path.join(batch.storage,features_dbname)
 		print("")
 		logdriver.info("Reading {0} from {1}".format(feature,feature_dbfile))
 
@@ -214,7 +220,13 @@ def cosmo_constraints(batch,specs,settings=default_settings):
 			#Read in the data#
 			##################
 
-			logdriver.info("Reading data to fit from table {0}".format(getattr(settings,feature).data_table))
+			#Allow to override the name of the data table
+			if "data_table" in specs[feature]:
+				data_table = specs[feature]["data_table"]
+			else:
+				data_table = getattr(settings,feature).data_table
+
+			logdriver.info("Reading data to fit from table {0}".format(data_table))
 			sql_query = getattr(settings,feature).data_query(feature_filter=specs[feature]["feature_filter"],redshift_filter=specs[feature]["redshift_filter"],realization_filter=specs[feature]["realization_filter"])
 			logdriver.info("SQL: {0}".format(sql_query))
 			query_results = db.query(sql_query)
@@ -300,8 +312,8 @@ def cosmo_constraints(batch,specs,settings=default_settings):
 	pcov_columns = ["{0}-{1}".format(i,j) for i,j in itertools.product(pnames,pnames)]
 
 	#Constraints database
-	outdbname = os.path.join(batch.home,"data",specs["dbname"])
-	logdriver.info("Saving constraints to {0}, table '{1}'".format(outdbname,specs["table_name"]))
+	outdbname = os.path.join(batch.home,"data",specs["output_dbname"])
+	logdriver.info("Saving constraints to {0}, table '{1}'".format(outdbname,specs["output_table_name"]))
 
 	#Number of PCA components to process
 	if "pca_components" in specs:
@@ -379,7 +391,7 @@ def cosmo_constraints(batch,specs,settings=default_settings):
 			row["feature_label"] = feature_label
 
 			#Insert the row
[…]

### 2016-03-18 code/library/driver_mpi.py
correctly select data table in SQL query

@@ -227,7 +227,7 @@ def cosmo_constraints(batch,specs,settings=default_settings):
 				data_table = getattr(settings,feature).data_table
 
 			logdriver.info("Reading data to fit from table {0}".format(data_table))
-			sql_query = getattr(settings,feature).data_query(feature_filter=specs[feature]["feature_filter"],redshift_filter=specs[feature]["redshift_filter"],realization_filter=specs[feature]["realization_filter"])
+			sql_query = getattr(settings,feature).data_query(data_table=data_table,feature_filter=specs[feature]["feature_filter"],redshift_filter=specs[feature]["redshift_filter"],realization_filter=specs[feature]["realization_filter"])
 			logdriver.info("SQL: {0}".format(sql_query))
 			query_results = db.query(sql_query)
 

### 2016-03-18 code/library/driver_mpi.py
query shortcut for parameter fits

@@ -130,6 +130,11 @@ def cosmo_constraints(batch,specs,settings=default_settings):
 	##Specs should be a dictionary with all the information needed to combine the features and compute the constraints##
 	####################################################################################################################
 
+	#Print a break in the output
+	print("#"*(10 + 1 + len(specs["feature_label_root"]) + 1 + 10))
+	print("#"*10 + " " + specs["feature_label_root"] + " " + "#"*10)
+	print("#"*(10 + 1 + len(specs["feature_label_root"]) + 1 + 10))
+
 	#Placeholders for emulator, data and covariance
 	emulator = Ensemble(columns=["model"])
 	covariance = Ensemble(columns=["realization"])

### 2016-03-18 code/library/featureDB.py

@@ -427,8 +427,6 @@ class FisherDatabase(Database):
 		pcov = query_row.values.reshape((len(parameters),)*2)
 		return self._constructor_ensemble(pcov,index=parameters,columns=parameters)
 
-	
-
 	#Retrieve the variance of a single parameter for a single feature_label
 	def query_parameter_simple(self,feature_label,table_name="pcov",parameter="w"):
 
@@ -455,6 +453,36 @@ class FisherDatabase(Database):
 
 		#Return the number of components and corresponding parameter variance
 		return query_results["bins"].values.astype(np.int),query_results["-".join([parameter,parameter])].values
+
+
+	#Retrieve the best fit parameters to the data
+	def query_parameter_fit(self,feature_label,table_name="pcov",parameters=["Om","w"]):
+
+		"""
+		Retrieve the variance of a single parameter for a single feature_label
+
+		:param feature_label: name of the feature to retrieve
+		:type feature_label: str.
+
+		:param table_name: name of the table to query
+		:type table_name: str.
+
+		:param parameters: parameters to retrieve
+		:type parameter: list.
+
+		:returns: parameters best fit 
+		:rtype: Ensemble
+
+		"""
+
+		#Build the SQL query and retrieve the results
+		sql_query = 'SELECT {0},bins FROM {1} WHERE feature_label="{2}"'.format(",".join(["{0}_fit".format(p) for p in parameters]),table_name,feature_label)
+		query_results = self.query(sql_query)
+
+		#Return the query
+		return query_results
+
+	######################################################################################################################################################################
 
 	#Plot shortcut by redshift
 	def plot_by_redshift(self,features,table_name,parameter,colors):

### 2016-03-18 photoz_paper/Figures/generate.py
generate first photoz bias figure

@@ -6,17 +6,93 @@ sys.modules["mpi4py"] = None
 import numpy as np
 import matplotlib.pyplot as plt
 
-from lenstools.statistics.ensemble import Ensemble
-from lenstools.statistics.database import Database
+from library.featureDB import FisherDatabase
 
+#Options
+parser = argparse.ArgumentParser()
+parser.add_argument("-t","--type",dest="type",default="png",help="format of the figure to save")
+parser.add_argument("fig",nargs="*")
+
+#Plot labels
+par2label = {
+
+"Om" : r"$\Omega_m$" ,
+"w" : r"$w$" ,
+"sigma8" : r"$\sigma_8$"
+
+}
+
+#Fiducial value
+par2value = {
+
+"Om" : 0.26 ,
+"w" : -1. ,
+"sigma8" : 0.8
+
+}
 
 ###################################################################################################
 
+def photoz_bias(cmd_args,db_name="data/fisher/constraints_photoz.sqlite",parameters=["Om","w"],feature_label="power_spectrum_pca",fontsize=22):
+	
+	#Init figure
+	fig,ax = plt.subplots()
+
+	############
+	#No photo-z#
+	############
+
+	with FisherDatabase(db_name) as db:
+		pfit = db.query_parameter_fit(feature_label,table_name="shape_noise",parameters=parameters)
+		p1,p2 = [ pfit[parameters[n]+"_fit"].values for n in [0,1] ]
+		ax.scatter(p1,p2,s=pfit["bins"],color="black",label="No photo-z")
+
+	##############
+	#With photo-z#
+	##############
+
+	with FisherDatabase(db_name) as db:
+		pfit = db.query_parameter_fit(feature_label,table_name="shape_noise_photoz",parameters=parameters)
+		p1,p2 = [ pfit[parameters[n]+"_fit"].values for n in [0,1] ]
+		ax.scatter(p1,p2,s=pfit["bins"],color="red",label="With photo-z")
+
+	#Get axes bounds
+	xlim = ax.get_xlim()
+	ylim = ax.get_ylim()
+
+	#Show the fiducial value
+	ax.plot(np.ones(100)*par2value[parameters[0]],np.linspace(*(ylim+(100,))),linestyle="-",color="green")
+	ax.plot(np.linspace(*(xlim+(100,))),np.ones(100)*par2value[parameters[1]],linestyle="-",color="green")
+
+	#Set the axes bounds
+	ax.set_xlim(xlim)
+	ax.set_ylim(ylim)
+
[…]

### 2016-03-18 code/measure/measure_pdf.py
added script to measure the PDF of a convergence map

@@ -1,0 +1,59 @@
+#!/usr/bin/env python-mpi
+
+import library.driver_mpi as driver
+from lenstools.statistics.ensemble import Ensemble
+
+import numpy as np
+import pandas as pd
+
+#Measure the PDF of a kappa map
+def pdf(maps,kappa_edges,indices):
+
+	"""
+
+	:param maps: list of convergence maps (one for each redshift bin)
+	:type maps: list.
+		
+	:param kappa_edges: convergence value bin edges
+	:type kappa_edges: array
+
+	:returns: Ensemble
+
+	"""
+
+	#Allocate memory
+	pdf_array = np.zeros((len(indices),len(kappa_edges)-1))
+		
+	#Measure the PDF
+	for n,i in enumerate(indices):
+		kappa,pdf_array[n] = maps[i].pdf(kappa_edges,norm=True)
+
+	#Build the Ensemble
+	columns = [ "k{0}".format(n) for n in range(1,len(kappa)+1) ]
+	ensemble = Ensemble(pdf_array,columns=columns)
+
+	#Add the indices labels
+	ensemble["b1"] = indices
+
+	#Return
+	return ensemble
+
+#Redshift bin index pairs and multipoles
+measurer_kwargs = {
+	
+"measurer" : pdf,
+"indices" : range(5),
+"kappa_edges" : np.array([ -2. ,  -1.7,  -1.4,  -1.1,  -0.8,  -0.5,  -0.2,   0.1,   
+	0.4, 0.7,   1. ,   1.3,   1.6,   1.9,   2.2,   2.5,   2.8,   3.1, 3.4,   3.7,   
+	4. ,   4.3,   4.6,   4.9,   5.2,   5.5,   5.8, 6.1,   6.4,   6.7,   7. , 7.3,   
+	7.6,   7.9,   8.2,   8.5, 8.8,   9.1,   9.4,   9.7,  10. ,  10.3,  10.6,  10.9,  
+	11.2, 11.5,  11.8,  12.1,  12.4,  12.7,  13. ])
+	
+}
+
+default_db_name = "pdf"
+
+###############################################################################################
+
+if __name__=="__main__":
+	driver.measure_main(measurer_kwargs,default_db_name)

### 2016-03-18 code/library/driver_mpi.py
calculate bias for multiple mock observations

@@ -131,6 +131,7 @@ def cosmo_constraints(batch,specs,settings=default_settings):
 	####################################################################################################################
 
 	#Print a break in the output
+	print("")
 	print("#"*(10 + 1 + len(specs["feature_label_root"]) + 1 + 10))
 	print("#"*10 + " " + specs["feature_label_root"] + " " + "#"*10)
 	print("#"*(10 + 1 + len(specs["feature_label_root"]) + 1 + 10))
@@ -372,10 +373,6 @@ def cosmo_constraints(batch,specs,settings=default_settings):
 			logdriver.info("Computing the {0}x{0} feature covariance matrix, Nreal={1}, NLSST={2}...".format(covariance_pca.shape[1],specs["realizations_for_covariance"],settings.covariance_to_lsst))
 			feature_covariance = covariance_pca.head(specs["realizations_for_covariance"]).cov() / settings.covariance_to_lsst
 
-			#Fit for the cosmological parameters
-			logdriver.info("Fitting for cosmological parameters ({0})...".format(",".join(fisher.parameter_names)))
-			parameter_fit = fisher.fit(data_pca.head(specs["realizations_for_data"]).mean(),feature_covariance)
-
 			#Compute the parameter covariance matrix correcting for the inverse covariance bias
 			logdriver.info("Computing {0}x{0} parameter covariance matrix, Nbins={1}...".format(len(pnames),covariance_pca.shape[1]))
 			parameter_covariance = fisher.parameter_covariance(feature_covariance,correct=specs["realizations_for_covariance"])
@@ -387,16 +384,55 @@ def cosmo_constraints(batch,specs,settings=default_settings):
 			#Format the row to insert
 			row = pd.Series(parameter_covariance.values.flatten(),index=pcov_columns)
 
-			#Insert best parameter fit
-			for p in parameter_fit.index:
-				row[p+"_fit"] = parameter_fit[p]
-
 			#Metadata
 			row["bins"] = covariance_pca.shape[1]
 			row["feature_label"] = feature_label
 
-			#Insert the row
-			db.insert(pd.DataFrame(row).T,specs["output_table_name"])
+			#####################################
+			#Fit for the cosmological parameters#
+			#####################################
+
+			realizations_for_data = specs["realizations_for_data"]
+			mock_data_realizations = specs["mock_data_realizations"]
+
+			#Maybe repeat the procedure for multiple mock observations
[…]

### 2016-03-18 code/library/driver_mpi.py
fix bug

@@ -397,7 +397,7 @@ def cosmo_constraints(batch,specs,settings=default_settings):
 
 			#Maybe repeat the procedure for multiple mock observations
 			if mock_data_realizations>1:
-				for nm in range(len(mock_data_realizations)):
+				for nm in range(mock_data_realizations):
 
 					#Build data vector
 					logdriver.info("Building data vector averaging over {0} realizations (mock observation {1} of {2})...".format(realizations_for_data,nm+1,mock_data_realizations))

### 2016-03-18 code/library/driver_mpi.py
added suffix to photoz table

@@ -92,6 +92,9 @@ def measure_main(measurer_kwargs,default_db_name):
 
 	}
 
+	#Suffix for table names with photoz
+	photoz_table_suffix = options.get("Noise","photoz_suffix")
+
 	#Merge keyword arguments dictionaries
 	driver_measurer_kwargs = dict(driver_kwargs,**measurer_kwargs)
 
@@ -105,14 +108,14 @@ def measure_main(measurer_kwargs,default_db_name):
 		if cosmo_id==batch.fiducial_cosmo_id:
 			
 			if (driver_kwargs["photoz_bias"] is not None) or (driver_kwargs["photoz_sigma"] is not None):
-				catalog2table = {"Shear":"features_fiducial_photoz","ShearEmuIC":"features_fiducial_EmuIC_photoz"}
+				catalog2table = {"Shear":"features_fiducial_{0}".format(photoz_table_suffix),"ShearEmuIC":"features_fiducial_EmuIC_{0}".format(photoz_table_suffix)}
 			else:
 				catalog2table = {"Shear":"features_fiducial","ShearEmuIC":"features_fiducial_EmuIC"}
 
 		else:
 
 			if (driver_kwargs["photoz_bias"] is not None) or (driver_kwargs["photoz_sigma"] is not None):
-				catalog2table = {"Shear":"features_photoz"}
+				catalog2table = {"Shear":"features_{0}".format(photoz_table_suffix)}
 			else:
 				catalog2table = {"Shear":"features"}
 
@@ -397,6 +400,7 @@ def cosmo_constraints(batch,specs,settings=default_settings):
 
 			#Maybe repeat the procedure for multiple mock observations
 			if mock_data_realizations>1:
+				
 				for nm in range(len(mock_data_realizations)):
 
 					#Build data vector

### 2016-03-18 code/library/driver_mpi.py
allow to pass None to photoz, allow to deserialize photoz calculation function

@@ -1,7 +1,7 @@
 import os
 import argparse,logging
 import itertools
-from distutils import config
+import json
 
 import numpy as np
 import pandas as pd
@@ -55,13 +55,10 @@ def measure(batch,cosmo_id,model_n,catalog2table,db_name,add_shape_noise,photoz_
 
 def measure_main(measurer_kwargs,default_db_name):
 
-	#INI option parser
-	options = config.ConfigParser()
-
 	#Parse command line arguments
 	parser = argparse.ArgumentParser()
 	parser.add_argument("-e","--environment",dest="environment",help="Environment options file")
-	parser.add_argument("-c","--config",dest="config",default="measure.ini",help="Configuration file")
+	parser.add_argument("-c","--config",dest="config",default="measure.json",help="Configuration file (JSON format)")
 	parser.add_argument("-d","--database",dest="database",default=default_db_name,help="Database name to populate")
 	parser.add_argument("id",nargs="*")
 	cmd_args = parser.parse_args()
@@ -71,8 +68,9 @@ def measure_main(measurer_kwargs,default_db_name):
 	#Handle on the current batch
 	batch = LSSTSimulationBatch(EnvironmentSettings.read(cmd_args.environment))
 
-	#Read the options
-	options.read(cmd_args.config)
+	#Read the JSON options
+	with open(cmd_args.config,"r") as fp:
+		options = json.load(fp)
 
 	#Output database name
 	database_name = cmd_args.database
@@ -85,15 +83,15 @@ def measure_main(measurer_kwargs,default_db_name):
 	driver_kwargs = {
 
 	"db_name" : database_name,
-	"add_shape_noise" : options.getboolean("Noise","add_shape_noise"),
-	"photoz_bias" : options.get("Noise","photoz_bias"),
-	"photoz_sigma" : options.get("Noise","photoz_sigma"),
+	"add_shape_noise" : options["add_shape_noise"],
+	"photoz_bias" : options["photoz_bias"],
+	"photoz_sigma" : options["photoz_sigma"],
 	"pool" : None
 
 	}
 
 	#Suffix for table names with photoz
-	photoz_table_suffix = options.get("Noise","photoz_suffix")
+	photoz_table_suffix = options["photoz_suffix"]
 
 	#Merge keyword arguments dictionaries
 	driver_measurer_kwargs = dict(driver_kwargs,**measurer_kwargs)

### 2016-03-18 code/library/driver_mpi.py
fix bug (ini vs json)

@@ -75,7 +75,7 @@ def measure_main(measurer_kwargs,default_db_name):
 	#Output database name
 	database_name = cmd_args.database
 	
-	if options.getboolean("Noise","add_shape_noise"):
+	if options["add_shape_noise"]:
 		database_name += "_noise" 
 	
 	database_name += ".sqlite"

### 2016-03-19 code/library/driver_mpi.py
adding distutils import fixes json memory bug

@@ -2,6 +2,7 @@ import os
 import argparse,logging
 import itertools
 import json
+from distutils import config
 
 import numpy as np
 import pandas as pd

### 2016-03-21 photoz_paper/paper.tex
generate first photoz bias figure
layed down paper structure

@@
 
-\title{Cosmology with photometric surveys: the effect of redshift errors on tomographic parameter constraints}
+\title{Cosmology with photometric surveys: the effect of redshift errors on Weak Lensing tomographic parameter constraints}
 
@@
 
-\keywords{Weak Gravitational Lensing --- Simulations --- Methods: numerical, statistical}
+\keywords{Weak Gravitational Lensing --- Simulations --- Systematic effects: photometry --- Methods: numerical, statistical}
 \pacs{98.80.-k, 95.36.+x, 95.30.Sf, 98.62.Sb}
@@
 
-\citep{DodelsonSchneider13}
+\citep{Huterer2006}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%% METHODS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Methods}
+
+\subsection{Cosmic shear simulations}
+
+\subsection{Forward modeling of systematics}
+
+\subsection{Parameter inference}
+
+%%%%%%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Results}
+
+%%%%%%%%%%%%%%%%%%%%%%% DISCUSSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Discussion}
+
+%%%%%%%%%%%%%%%%%%%%%%% CONCLUSIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Conclusions}
 

### 2016-03-21 photoz_paper/Figures/generate.py
update Figure1

@@ -43,35 +43,43 @@ def photoz_bias(cmd_args,db_name="data/fisher/constraints_photoz.sqlite",paramet
 	############
 
 	with FisherDatabase(db_name) as db:
-		pfit = db.query_parameter_fit(feature_label,table_name="shape_noise",parameters=parameters)
-		p1,p2 = [ pfit[parameters[n]+"_fit"].values for n in [0,1] ]
-		ax.scatter(p1,p2,s=pfit["bins"],color="black",label="No photo-z")
+		pfit = db.query_parameter_fit(feature_label,table_name="shape_noise_mocks",parameters=parameters)
+		p1f,p2f = [ pfit[parameters[n]+"_fit"].values for n in [0,1] ]
 
-	##############
-	#With photo-z#
-	##############
+	##########################
+	#With photo-z: optimistic#
+	##########################
 
 	with FisherDatabase(db_name) as db:
-		pfit = db.query_parameter_fit(feature_label,table_name="shape_noise_photoz",parameters=parameters)
+		pfit = db.query_parameter_fit(feature_label,table_name="shape_noise_mocks_photoz",parameters=parameters)
 		p1,p2 = [ pfit[parameters[n]+"_fit"].values for n in [0,1] ]
-		ax.scatter(p1,p2,s=pfit["bins"],color="red",label="With photo-z")
+		ax.scatter(p1-p1f,p2-p2f,color="red",label="With photo-z (optimistic)")
+
+	###########################
+	#With photo-z: pessimistic#
+	###########################
+
+	with FisherDatabase(db_name) as db:
+		pfit = db.query_parameter_fit(feature_label,table_name="shape_noise_mocks_photoz_pessimistic",parameters=parameters)
+		p1,p2 = [ pfit[parameters[n]+"_fit"].values for n in [0,1] ]
+		ax.scatter(p1-p1f,p2-p2f,color="blue",label="With photo-z (pessimistic)")
 
 	#Get axes bounds
-	xlim = ax.get_xlim()
-	ylim = ax.get_ylim()
+	xlim = np.abs(np.array(ax.get_xlim())).max()
+	ylim = np.abs(np.array(ax.get_ylim())).max()
 
 	#Show the fiducial value
[…]

### 2016-03-21 code/library/driver_mpi.py
generate specs files automatically

@@ -122,6 +122,57 @@ def measure_main(measurer_kwargs,default_db_name):
 		measure(batch=batch,cosmo_id=cosmo_id,model_n=int(n),catalog2table=catalog2table,**driver_measurer_kwargs)
 
 
+#Propagate the specifications through the run with photoz errors
+def photo_specs(specs,in2out_table):
+
+	if isinstance(specs,dict):
+		specs = [specs]
+	out_specs = list()
+
+	#Cycle through features
+	for s in specs:
+		
+		#Update table names
+		for in_table in in2out_table:
+			for feature in s["features"]:
+				s[feature]["data_table"] = in_table
+			s["output_table_name"] = in2out_table[in_table]
+
+		#Append to specs list
+		out_specs.append(json.loads(json.dumps(s)))
+
+	#Return to user
+	return out_specs
+
+#Create a list of single redshift features out of a tomographic one
+def split_redshifts(specs,redshift_index=range(5)):
+
+	#List of splittings
+	splitted_specs = list()
+
+	#Cycle over features and redshift bin
+	for zi in redshift_index:
+		
+		#Deep copy of the original dictionary
+		specs_redshift = dict()
+		for key in ["dbname","table_name","feature_label_root","feature_label_format","features","realizations_for_covariance","realizations_for_data","pca_components"]:
+			specs_redshift[key] = specs[key]
+
+		#Append redshift label to name
+		specs_redshift["feature_label_root"] += "_z{0}".format(zi)
+		
+		#Update features with redshift filter
+		for feature in specs["features"]:
+			specs_redshift[feature] = dict((("feature_filter",specs[feature]["feature_filter"]),("realization_filter",specs[feature]["realization_filter"])))
+			specs_redshift[feature]["redshift_filter"] = " AND ".join(["{0}={1}".format(l,zi) for l in getattr(settings,feature).redshift_labels])
+	
+		#Append to list
+		splitted_specs.append(specs_redshift)
+
+	#Return to user
+	return splitted_specs
+
+
 ################################################
 #######Cosmological constraints driver##########
 ################################################

### 2016-03-21 code/library/driver_mpi.py
fix bug

@@ -134,12 +134,13 @@ def photo_specs(specs,in2out_table):
 		
 		#Update table names
 		for in_table in in2out_table:
+			
 			for feature in s["features"]:
 				s[feature]["data_table"] = in_table
 			s["output_table_name"] = in2out_table[in_table]
 
-		#Append to specs list
-		out_specs.append(json.loads(json.dumps(s)))
+			#Append to specs list
+			out_specs.append(json.loads(json.dumps(s)))
 
 	#Return to user
 	return out_specs

### 2016-03-21 code/library/driver_mpi.py
fix bug

@@ -131,6 +131,9 @@ def photo_specs(specs,in2out_table):
 
 	#Cycle through features
 	for s in specs:
+
+		#Append to specs list
+		out_specs.append(json.loads(json.dumps(s)))
 		
 		#Update table names
 		for in_table in in2out_table:

### 2016-03-22 photoz_paper/paper.tex
update Figure1
started writing methods section

@@
 \newcommand{\h}[1]{\hat{#1}}
+
+\newcommand{\ttt}[1]{\texttt{#1}}
+
 \newcommand\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
@@
 
-\title{Cosmology with photometric surveys: the effect of redshift errors on Weak Lensing tomographic parameter constraints}
+\title{Cosmology with photometric surveys: constraints with redshift tomography of non--Gaussian statistics}
 
@@
 \begin{abstract}
-
+Weak Gravitational Lensing is becoming a popular technique to constrain cosmological parameters, such as the Dark Energy equation of state $w$.
+When analyzing galaxy surveys, redshift information has proven to be a valuable addition to angular shear correlations.
+We forecast parameter constraints on the triplet $(\Omega_m,w,\sigma_8)$ for a LSST like galaxy photometric survey, using tomography of the shear-shear power spectrum, convergence peak counts and higher convergence moments.
+We evaluate the effect of uncorrected photometric redshift systematics on parameter constraints.
+We show that different statistics lead to different bias directions in parameter space, leaving a window open for self--calibration.
 \end{abstract}
@@
 %
-
-\citep{Huterer2006}
+This work is organized as follows: we give an outline of the shear simulations we use in this work, followed by descriptions of the convergence reconstruction procedure and forward modeling of galaxy shape and redshift systematics.
+We then give an overview of the parameter inferences technique we used to forecast constraints on cosmology.
+We then discuss the main results of this work and present our conclusions as well as prospects for future work.
 
@@
 \subsection{Cosmic shear simulations}
+\label{sec:shearsim}
+We review the procedure used for generating mock shear catalogs.
+We consider a fiducial flat $\Lambda$CDM universe with $(h,\Omega_m,\Omega_\Lambda,\Omega_b,w,\sigma_8,n_s)=(0.72,0.26,0.74,0.046,-1,0.8,0.96)$.
+We examine different variations of the $\bb{p}=(\Omega_m,w,\sigma_8)$ triplet and run one $N$--body simulation for each choice of $\bb{p}$, using the public code \ttt{Gadget2} \citep{Gadget2}.
+The simulations have a comoving box size of $L_b=260\,{\rm Mpc}/h$ and contain $512^3$ dark matter particles, which correspond to a mass resolution of $M_p\approx 10^{10}M_{\rm sun}$ per particle.
+The three dimensional outputs of the $N$--body simulations are sliced in sequences of two dimensional lenses $120 \,{\rm Mpc}$ thick, which are lined up perpendicular to the line of sight between the observer on Earth and a source at redshift $z_s$.
+We make use of the multi--lens--plane algorithm \citep{RayTracingJain,RayTracingHartlap} to trace the deflections of light rays originating at $z=0$ through the system of lenses until $z$.
+To accomplish this task, we make use of the \ttt{LensTools} \citep{LensTools-ASCL,LensTools-paper} implementation of the multi--lens--plane algorithm.
+An observed galaxy position $\pmb{\theta}$ on the sky today corresponds to a real galaxy angular position $\pmb{\beta}(\pmb{\theta},z_s)$, which can be calculated using the \ttt{LensTools} pipeline by solving the lensing ODE up to redshift $z_s$.
+The Jacobian of $\pmb{\beta}(\pmb{\theta},z_s)$ is a $2\times 2$ matrix that contains information about the cosmic shear field at $\pmb{\theta}$ integrated along the line of sight.
+%
+\begin{equation}
+\label{meth:sheareqn}
+\frac{\partial\beta_i(\pmb{\theta},z_s)}{\partial \theta_j} = 
+\begin{pmatrix}
+1-\kappa(\pmb{\theta})-\gamma^1(\pmb{\theta}) & -\gamma^2(\pmb{\theta}) \\
+-\gamma^2(\pmb{\theta}) & 1-\kappa(\pmb{\theta})+\gamma^1(\pmb{\theta})\\
+\end{pmatrix}
+\end{equation}  
+%
+We simulate $N_g = 10^6$ random galaxy positions $\{\pmb{\theta}\}$ distributed uniformly in a field of view of size $\Omega_{\rm FOV}=(3.5{\rm deg})^2$, which correspond to a galaxy angular density of $n_g=22\,\rm{arcmin}^{-2}$.
+The galaxy have a distribution in redshift which mimics the one expected in the LSST survey
+\begin{equation}
+n(z) = n_0\left(\frac{z}{z_0}\right)^2\exp\left(-\frac{z}{z_0}\right)
+\end{equation}  
+%
+with $z_0=0.3$ and $n_0$ a normalization constant fixed so that $n(z)$ integrates to the total number of galaxies $N_g$.
+For each galaxy we compute the cosmic shear at $\pmb{\theta}$ using equation (\ref{meth:sheareqn}), producing a shear catalog $\{\pmb{\gamma}\}$.
+Different random realizations of a shear catalog $\{\pmb{\gamma}\}_r$ can be obtained rotating and periodically shifting the Large Scale Structure in the $N$--body snapshots according to the procedure explained in \citep{PetriVariance}.
+We produce $N_r=16000$ pseudo--independent realizations of the shear catalog $\{\pmb{\gamma}\}$.
+These shear realization cover the total survey area of LSST 10 times.
+We repeat the above procedure for 100 different combinations of the parameter triplet $\bb{p}$, sampled according to a Latin hypercube scheme.
+The sampling procedure is the same described in \citep{CFHTMink,CFHTPeaks}.
+For each of these simulations, the $N$--body initial conditions are generated using the same random seed.
+In addition to this simulations, we produce simulated shear catalogs for a fiducial $\Lambda$CDM universe with $\bb{p}_0=(0.26,-1,0.8)$.
+In this case the randomization procedure is based on 5 independent $N$--body simulations, and the same number of pseudo--independent catalog realizations is produced.
 
 \subsection{Forward modeling of systematics}
+We give an overview of the shear systematics included in this work.
+The measured galaxy ellipticity $\pmb{\epsilon}$ is an estimate of the cosmic shear $\pmb{\gamma}$ due to Large Scale Structure if the non--lensed galaxy shape is a circle.
+If this assumption is relaxed, the measured galaxy ellipticity $\pmb{\epsilon}_{\rm m}$ can be modeled as a cosmic shear term plus a noise term \citep{wlreview}
+\begin{equation}
+\pmb{\epsilon}_{\rm m} = \pmb{\gamma} + \pmb{\epsilon}_{\rm n}
+\end{equation} 
+%
+where $\pmb{\epsilon}_{\rm n}$ is a random Gaussian variable with zero mean and redshift dependent variance $\sigma_n(z)=0.15+0.035z$.
+This is equivalent to say that the cosmic shear inferred from ellipticity observations $\pmb{\gamma}_{\rm m}$ can be written as the sum of the true cosmic shear plus a noise term $\pmb{\gamma}_{\rm n}$ with the same statistical properties as $\pmb{\epsilon}_{\rm n}$.
+We add independent random realizations of the shape noise $\pmb{\epsilon}_{\rm n}$ to each of the $N_r$ shear catalogs.
+Each shape noise realization is generated with a different random seed.
+The same random seeds are used to generate shape noise catalogs across simulations with different cosmological parameters $\bb{p}$.
+
+In addition to shape noise contributions to the observed galaxy ellipticity we consider photometric redshift errors as an additional contamination source in the simulated catalogs.
+In photometric surveys such as LSST, the source redshift $z_s$ is estimated measuring the source luminosity in a finite small set of optical frequency bands.
+Using this compressed luminosity information rather than the full spectrum introduces biases in redshift estimation.
+Forward modeling of the cosmic shear using the procedure described in \S~\ref{sec:shearsim}, as well as the shape noise contributions, assume a correct redshift distributions $n(z)$.
+An incorrect binning of observed galaxy redshifts according to the inferred photometric distribution $n_p(z_p)$ can propagate to redshift measurement errors all the way to cosmological parameter constraints when the latter take advantage of redshift tomography.
+One of the goals of this work is to evaluate the size of this effect, assuming photometric redshift errors (photo-$z$) are left uncorrected.
+We model effect of photo-$z$ errors as a constant bias term $b_{\rm ph}(z_s)$ plus a random Gaussian component with variance $\sigma_{\rm ph}(z_s)$
+\begin{equation}
+\label{meth:photoz-correction}
+z_p(z_s) = z_s + b_{\rm ph}(z_s) + \sigma_{\rm ph}(z_s)\mathcal{N}(0,1)   
+\end{equation}
+%
+where $\mathcal{N}(0,1)$ is the standard normal distribution.
+We bin the $N_g$ galaxies in our simulated catalogs in 5 redshift bins.
+The bin sizes are adjusted so that each of them contains the same number of galaxies.
+We generate mock observations by applying an independent random realization of the photo-$z$ correction (\ref{meth:photoz-correction}) to each catalog realization in the fiducial cosmology $\bb{p}_0$ and by re--binning the galaxies according to their photometric redshifts $z_p$.
+In the remainder of the paper we use the following notation: we indicate a shear realization $r$ in cosmology $\bb{p}$ with shape noise added as $\h{\pmb{\gamma}}_r(\pmb{\theta}_g,z_g;\bb{p})$, and we indicate a mock observation as $\h{\pmb{\gamma}}_{\rm obs}(\pmb{\theta}_g,z_g)$.
+
+\subsection{Convergence reconstruction}
 
 \subsection{Parameter inference}
+
+\subsection{Dimensionality reduction}
 

### 2016-03-23 photoz_paper/paper.tex
wrote statistical method paragraph

@@
 
+%%%%%%%%
+
 \subsection{Cosmic shear simulations}
@@
 %
+The quantities that appear in equation (\ref{meth:sheareqn}) are the convergence $\kappa$, which is the source magnification due to lensing, and the cosmic shear $\pmb{\gamma}$, which is a measurement of the source ellipticity due to lensing from Large Scale Structure, assuming the non lensed shape is a circle.
 We simulate $N_g = 10^6$ random galaxy positions $\{\pmb{\theta}\}$ distributed uniformly in a field of view of size $\Omega_{\rm FOV}=(3.5{\rm deg})^2$, which correspond to a galaxy angular density of $n_g=22\,\rm{arcmin}^{-2}$.
@@
 
+%%%%%%%%
+
 \subsection{Forward modeling of systematics}
@@
 This is equivalent to say that the cosmic shear inferred from ellipticity observations $\pmb{\gamma}_{\rm m}$ can be written as the sum of the true cosmic shear plus a noise term $\pmb{\gamma}_{\rm n}$ with the same statistical properties as $\pmb{\epsilon}_{\rm n}$.
-We add independent random realizations of the shape noise $\pmb{\epsilon}_{\rm n}$ to each of the $N_r$ shear catalogs.
+We add independent random realizations of the shape noise $\pmb{\gamma}_{\rm n}$ to each of the $N_r$ shear catalogs.
 Each shape noise realization is generated with a different random seed.
-The same random seeds are used to generate shape noise catalogs across simulations with different cosmological parameters $\bb{p}$.
+The same random seeds are used to generate shape noise catalogs across simulations with different cosmological parameters $\{\bb{p}_i\}$.
+
+%ADD Simulation specifications
 
@@
 Forward modeling of the cosmic shear using the procedure described in \S~\ref{sec:shearsim}, as well as the shape noise contributions, assume a correct redshift distributions $n(z)$.
-An incorrect binning of observed galaxy redshifts according to the inferred photometric distribution $n_p(z_p)$ can propagate to redshift measurement errors all the way to cosmological parameter constraints when the latter take advantage of redshift tomography.
+An incorrect binning of observed galaxy redshifts according to the measured photometric distribution $n_p(z_p)$ can propagate the redshift measurement errors all the way to cosmological parameter constraints if the latter take advantage of redshift tomography.
 One of the goals of this work is to evaluate the size of this effect, assuming photometric redshift errors (photo-$z$) are left uncorrected.
@@
 where $\mathcal{N}(0,1)$ is the standard normal distribution.
-We bin the $N_g$ galaxies in our simulated catalogs in 5 redshift bins.
+We bin the $N_g$ galaxies in our simulated catalogs in 5 redshift bins $\bar{z}_b$, $b=1...5$.
+Several models have been proposed in the literature for the photometric bias $b_{\rm ph}(z_s)$ (see for example \citep{Huterer2006}) and variance $\sigma_{\rm ph}(z_s)$ (see for example \citep{LSSTSciBook}).
+We make use of the photo-$z$ bias and variance values contained in the LSST Science Book \citep{LSSTSciBook}.
 The bin sizes are adjusted so that each of them contains the same number of galaxies.
@@
 
+%%%%%%%%
+
 \subsection{Convergence reconstruction}
+In this paragraph we describe the procedure we used to construct convergence maps $\kappa$ from the simulated shear catalogs $\pmb{\gamma}$.
+We consider a two dimensional square pixel grid of area $\theta_{\rm FOV}^2$ and with 512 pixel per side.
+This correspond to a linear pixel resolution of $0.5 \rm{arcmin}$.
+We assign a shear value $\pmb{\gamma}(\pmb{\theta}_p,\bar{z}_b)$ to each pixel $\pmb{\theta}_p$ according to the following procedure
+\begin{equation}
+\pmb{\gamma}(\pmb{\theta}_p,\bar{z}_b) = \frac{\sum_{g=1}^{N_g}\pmb{\gamma}(\pmb{\theta}_g,z_g)W(\pmb{\theta}_g,\pmb{\theta}_p;z_g,\bar{z}_b)}{\sum_{g=1}^{N_g}W(\pmb{\theta}_g,\pmb{\theta}_p;z_g,\bar{z}_b)}
+\end{equation}   
+%
+We chose a top--hat window function
+\begin{equation}
+W(\pmb{\theta}_g,\pmb{\theta}_p;z_g,\bar{z}_b) = 
+\begin{cases}
+1 \,\,\,\,{\rm if}\,\,\,\, \pmb{\theta}_g\in\pmb{\theta}_p,z_g\in\bar{z}_b \\
+0 \,\,\,\,{\rm otherwise}
+\end{cases}
+\end{equation} 
+%
+The convergence $\kappa(\pmb{\theta}_p)$ can be reconstructed from the $E$--mode of the shear field, which is evaluated from the Fourier Transform of the pixelized shear $\pmb{\gamma}(\pmb{\theta}_p,\bar{z}_b)$
+\begin{equation}
+\label{meth:psdefinition}
+\tilde\kappa(\pmb{\ell},\bar{z}_b) = \left(\frac{\tilde{\gamma}^1(\pmb{\ell},\bar{z}_b)(\ell_x^2-\ell_y^2)+2\ell_1\ell_2\tilde{\gamma}^2(\pmb{\ell},\bar{z}_b)}{\ell_x^2+\ell_y^2}\right) e^{-\frac{\ell^2\theta_G^2}{2}}
+\end{equation}
+%
+We chose the Gaussian filter smoothing scale $\theta_G=0.5\,{\rm arcmin}$ to correspond to the linear pixel resolution.
+Inverting the Fourier Transform yields the pixelized map $\kappa(\pmb{\theta}_p,\bar{z}_b)$.
+We apply this procedure to both the shear realizations $\h{\pmb{\gamma}}_r(\pmb{\theta}_g,z_g;\bb{p})$ and the mock observations $\h{\pmb{\gamma}}_{\rm obs}(\pmb{\theta}_g,z_g)$, yielding convergence realizations $\h{\kappa}_r(\pmb{\theta}_p,\bar{z}_b;\bb{p})$ and mock convergence observations $\h{\kappa}_{\rm obs}(\pmb{\theta}_p,\bar{z}_b)$.
+
+We measure a variety of summary statistics from the pixelized convergence maps, which will then be used to forecast parameter constraints and biases.
+We consider three kinds of summary statistics, namely the $\kappa$ tomographic power spectrum $P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})$, the tomographic peak counts $n_{\rm pk}(\nu,\bar{z}_b)$ and a set of $\kappa$ moments $\pmb{\mu}(\bar{z}_b)$.
+The tomographic power spectrum is defined as
+\begin{equation}
+{\rm Re}\left(\langle\tilde{\kappa}(\pmb{\ell},\bar{z}_b)\tilde{\kappa}(\pmb{\ell}',\bar{z}_{b'})\rangle\right) = (2\pi)^2\delta_D(\pmb{\ell}+\pmb{\ell}')P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})
+\end{equation}
+%
+Because the $\kappa$ field is statistically isotropical, the expectation value $\langle\rangle$, for each realization $r$, is taken over all the modes $\pmb{\ell}$ which have the same magnitude $\ell=\vert\pmb{\ell}\vert$.
+The peak count statistic $n_{\rm pk}(\nu,\bar{z}_b)$ is defined as the number of the $\kappa$ local maxima of a certain height $\kappa_{\rm max}=\nu\sigma_0$, where $\sigma_0$ is the $\kappa$ standard deviation over pixels.
+The $\kappa$ moments $\pmb{\mu}(\bar{z}_b)$ are defined as follows
+%
+\begin{equation}
+\label{meth:momdef}
+\begin{matrix}
+\pmb{\mu} = (\pmb{\mu}_2,\pmb{\mu}_3,\pmb{\mu}_4) \\ \\
+\pmb{\mu}_2 = (\langle\kappa^2\rangle,\langle\vert\nabla\kappa\vert^2\rangle) \\ \\
+\pmb{\mu}_3 = (\langle\kappa^3\rangle,\langle\kappa\vert\nabla\kappa\vert^2\rangle,\langle\kappa^2\nabla^2\kappa\rangle) \\ \\
+\pmb{\mu}_4 = (\langle\kappa^4\rangle_c,\langle\kappa^2\vert\nabla\kappa\vert^2\rangle_c,\langle\kappa^3\nabla^2\kappa\rangle_c,\langle\vert\nabla\kappa\vert^4\rangle_c)
+\end{matrix}
+\end{equation}
+%
+In equation (\ref{meth:momdef}) the gradients $\nabla$ are evaluated using finite differences between $\kappa$ values at neighboring pixels and the expectation values $\langle\rangle$ for each realization $r$ are taken over the $512^2$ pixels in the map.
+The subscript $c$ indicates that we take only the connected parts of the quartic $\kappa$ moments.
+In the definition of the peak counts and convergence moments we omitted the redshift index $\bar{z}_b$ for notational simplicity, and also because both peak counts and moments do not contain cross redshift information unlike the power spectrum defined in equation (\ref{meth:psdefinition}).
+In the next paragraph we describe the statistical methods we use to infer cosmological parameter estimates $\bbh{p}$ from mock observations $\h{\kappa}_{\rm obs}(\pmb{\theta}_p,\bar{z}_b)$ using the summary statistics $P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})$, $n_{\rm pk}(\nu,\bar{z}_b)$, $\pmb{\mu}(\bar{z}_b)$.
+
+%%%%%%%%
 
 \subsection{Parameter inference}
+We adopt a Bayesian framework to forecast parameter constraints.
+We indicate as $\bb{d}$ a summary statistic vector (which can be any of $P^{\kappa\kappa},n_{\rm pk},\pmb{\mu}$ or a combination of the former).
+We label $\bb{d}(\bb{p})$ the sample mean of $\bb{d}$ over the $N_r=16000$ simulated realizations in cosmology $\bb{p}$ and we label $\bbh{d}_r$ the summary statistic measured in realization $r$ of the fiducial cosmology $\bb{p}_0$.
+Both $\bb{d}(\bb{p}),\bbh{d}_r$ are measured taking galaxy shape noise into account.
+We further label $\bbh{d}_{\rm obs}$ the summary statistic measured in a mock observation in which $\kappa$ has been measured taking photo-$z$ errors into account.
+$\bbh{d}_{\rm obs}$ is measured averaging a random sample of $N_{\rm FOV}=1600$ realizations of the fiducial cosmology with photo-$z$ errors added.
+This number has been chosen to mimic the survey are of LSST $\Omega_{\rm LSST}=N_{\rm FOV}\theta_{\rm FOV}^2$.
+Assuming no prior knowledge of the parameters $\bb{p}$, we can write the parameter likelihood $\mathcal{L}$ given the observation $\bbh{d}_{\rm obs}$ using the Bayes theorem
+%
+\begin{equation}
+\label{meth:paramlikelihood}
+-2\log\mathcal{L}(\bb{p}\vert \bbh{d}_{\rm obs}) = (\bbh{d}_{\rm obs} - \bb{d}(\bb{p}))^T\bb{C}^{-1}(\bbh{d}_{\rm obs} - \bb{d}(\bb{p}))
+\end{equation}  
+%
+The parameter likelihood (\ref{meth:paramlikelihood}) can be evaluated at every point $\bb{p}$ in parameter space by interpolating $\bb{d}(\bb{p})$ between simulation points $\{\bb{p}_i\}$ using a Radial Basis Function (RBF) interpolation (see \citep{CFHTMink,LensTools-paper}).
+$\bb{C}$ is the $\bb{d}$ covariance matrix and is assumed to be $\bb{p}$--independent.
+In practice we replace $\bb{C}$ with its estimated value $\bbh{C}$ from $N_r=16000$ realizations of the summary statistics $\bbh{d}_r$ in the fiducial cosmology $\bb{p}_0$ without photo-$z$ errors
+%
+\begin{equation}
+\bbh{d}_{\rm mean} = \frac{1}{N_r}\sum_{r=1}^{N_r}\bbh{d}_r 
+\end{equation}
+%
+\begin{equation}
+\bbh{C} = \frac{1}{N_r-1}\sum_{r=1}^{N_r} (\bbh{d}_r-\bbh{d}_{\rm mean})(\bbh{d}_r-\bbh{d}_{\rm mean})^T
+\end{equation} 
+%
+Cosmological parameter values $\bbh{p}$ can be inferred from equation (\ref{meth:paramlikelihood}) by looking at the peak of the likelihood.
+Parameter errors $\Delta\bbh{p}$ can be inferred from the likelihood confidence contours.
+Approximate estimates of $\bbh{p},\Delta \bbh{p}$ can be obtained approximating the model statistic $\bb{d}(\bb{p})$ dependency on parameters as linear in $\bb{p}$ provided $\bb{p}$ is not too far from the fiducial model $\bb{p}_0$
+\begin{equation}
+\label{meth:linapprox}
+\bb{d}(\bb{p}) = \bb{d}(\bb{p}_0) + \bb{M}(\bb{p}-\bb{p}_0) + O(\vert\bb{p}-\bb{p}_0\vert^2)
+\end{equation} 
+%
+Where we defined $(\bb{M})_{i\alpha}=(\partial d_i(\bb{p})/\partial p_\alpha)_{\bb{p}_0}$ as the statistic first derivative with respect to cosmology.
+This approximation allows for a fast estimate of $\bbh{p}$ in terms of $\bbh{d}_{\rm obs}$
+\begin{equation}
+\bbh{p} = (\bb{M}^T\bbh{\Psi}\bb{M})^{-1}\bb{M}^T\bbh{\Psi}(\bbh{d}_{\rm obs}-\bb{d}(\bb{p}_0))
+\end{equation}
+%
+Here we indicated $\bbh{\Psi}=\bbh{C}^{-1}$ as the summary statistic precision matrix.
+With the linear approximation (\ref{meth:linapprox}) the parameter likelihood (\ref{meth:paramlikelihood}) is a multivariate Gaussian in $\bb{p}$ and its width $\bbh{\Sigma}$ can be estimated as
+\begin{equation}
+(\bbh{\Sigma})_{\alpha\beta} = -\left(\frac{\partial^2 \log \mathcal{L}(\bb{p})}{\partial p_\alpha \partial p_\beta}\right)^{-1}_{\bb{p}_0} = ((\bb{M}^T\bbh{\Psi}\bb{M})^{-1})_{\alpha\beta}
+\end{equation}
+%
+The $1\sigma$ square parameter errors $\Delta \bbh{p}^2$ are the diagonal entries of $\bbh{\Sigma}$. This method of forecasting parameters takes the name of Fisher Matrix formalism. 
+%%%%%%%%
 

### 2016-03-25 photoz_paper/paper.tex
wrote pca section, started making results figures

@@
 The quantities that appear in equation (\ref{meth:sheareqn}) are the convergence $\kappa$, which is the source magnification due to lensing, and the cosmic shear $\pmb{\gamma}$, which is a measurement of the source ellipticity due to lensing from Large Scale Structure, assuming the non lensed shape is a circle.
-We simulate $N_g = 10^6$ random galaxy positions $\{\pmb{\theta}\}$ distributed uniformly in a field of view of size $\Omega_{\rm FOV}=(3.5{\rm deg})^2$, which correspond to a galaxy angular density of $n_g=22\,\rm{arcmin}^{-2}$.
+We simulate $N_g = 10^6$ random galaxy positions $\{\pmb{\theta}_g\}$ distributed uniformly in a field of view of size $\theta_{\rm FOV}^2=(3.5{\rm deg})^2$, which correspond to a galaxy angular density of $n_g=22\,\rm{arcmin}^{-2}$.
 The galaxy have a distribution in redshift which mimics the one expected in the LSST survey
@@
 with $z_0=0.3$ and $n_0$ a normalization constant fixed so that $n(z)$ integrates to the total number of galaxies $N_g$.
-For each galaxy we compute the cosmic shear at $\pmb{\theta}$ using equation (\ref{meth:sheareqn}), producing a shear catalog $\{\pmb{\gamma}\}$.
-Different random realizations of a shear catalog $\{\pmb{\gamma}\}_r$ can be obtained rotating and periodically shifting the Large Scale Structure in the $N$--body snapshots according to the procedure explained in \citep{PetriVariance}.
-We produce $N_r=16000$ pseudo--independent realizations of the shear catalog $\{\pmb{\gamma}\}$.
+For each galaxy we compute the cosmic shear at $\pmb{\theta}_g$ using equation (\ref{meth:sheareqn}), producing a shear catalog $\{\pmb{\gamma}_g\}$.
+Different random realizations of a shear catalog $\{\pmb{\gamma}_g\}_r$ can be obtained rotating and periodically shifting the Large Scale Structure in the $N$--body snapshots according to the procedure explained in \citep{PetriVariance}.
+We produce $N_r=16000$ pseudo--independent realizations of the shear catalog $\{\pmb{\gamma}_g\}$.
 These shear realization cover the total survey area of LSST 10 times.
-We repeat the above procedure for 100 different combinations of the parameter triplet $\bb{p}$, sampled according to a Latin hypercube scheme.
+We repeat the above procedure for $P=100$ different combinations of the parameter triplet $\bb{p}$, sampled according to a Latin hypercube scheme.
 The sampling procedure is the same described in \citep{CFHTMink,CFHTPeaks}.
+
+%ADD Simulation specifications
+
 For each of these simulations, the $N$--body initial conditions are generated using the same random seed.
@@
 
-%ADD Simulation specifications
-
 In addition to shape noise contributions to the observed galaxy ellipticity we consider photometric redshift errors as an additional contamination source in the simulated catalogs.
@@
 The bin sizes are adjusted so that each of them contains the same number of galaxies.
+The galaxy distribution we assumed, along with the binning choice is shown in Figure \ref{fig:galdistr}
+
+\begin{figure}
+\includegraphics[scale=0.3]{Figures/galdistr.eps}
+\caption{Galaxy distribution assumed throughout this work, along with the choice of the redshift bins $\bar{z}_b$.}
+\label{fig:galdistr}
+\end{figure}
+
 We generate mock observations by applying an independent random realization of the photo-$z$ correction (\ref{meth:photoz-correction}) to each catalog realization in the fiducial cosmology $\bb{p}_0$ and by re--binning the galaxies according to their photometric redshifts $z_p$.
@@
 The peak count statistic $n_{\rm pk}(\nu,\bar{z}_b)$ is defined as the number of the $\kappa$ local maxima of a certain height $\kappa_{\rm max}=\nu\sigma_0$, where $\sigma_0$ is the $\kappa$ standard deviation over pixels.
-The $\kappa$ moments $\pmb{\mu}(\bar{z}_b)$ are defined as follows
+The $\kappa$ moments $\pmb{\mu}(\bar{z}_b)$ are defined as follows (see \citep{Matsubara10,Munshi12,MinkPetri})
 %
@@
 In equation (\ref{meth:momdef}) the gradients $\nabla$ are evaluated using finite differences between $\kappa$ values at neighboring pixels and the expectation values $\langle\rangle$ for each realization $r$ are taken over the $512^2$ pixels in the map.
-The subscript $c$ indicates that we take only the connected parts of the quartic $\kappa$ moments.
+The subscript $c$ indicates that we consider only the connected parts of the quartic $\kappa$ moments.
 In the definition of the peak counts and convergence moments we omitted the redshift index $\bar{z}_b$ for notational simplicity, and also because both peak counts and moments do not contain cross redshift information unlike the power spectrum defined in equation (\ref{meth:psdefinition}).
@@
 %
-Cosmological parameter values $\bbh{p}$ can be inferred from equation (\ref{meth:paramlikelihood}) by looking at the peak of the likelihood.
+Cosmological parameter values $\bbh{p}$ can be inferred from equation (\ref{meth:paramlikelihood}) by looking at the location at which the likelihood $\mathcal{L}(\bb{p}\vert\bbh{d}_{\rm obs})$ is maximum.
 Parameter errors $\Delta\bbh{p}$ can be inferred from the likelihood confidence contours.
@@
 Where we defined $(\bb{M})_{i\alpha}=(\partial d_i(\bb{p})/\partial p_\alpha)_{\bb{p}_0}$ as the statistic first derivative with respect to cosmology.
-This approximation allows for a fast estimate of $\bbh{p}$ in terms of $\bbh{d}_{\rm obs}$
+We evaluate $\bb{M}$ with finite differences on the smooth RBF interpolation of the summary statistic $\bb{d}(\bb{p})$.
+This linear approximation allows for a fast estimate of $\bbh{p}$ in terms of $\bbh{d}_{\rm obs}$
 \begin{equation}
-\bbh{p} = (\bb{M}^T\bbh{\Psi}\bb{M})^{-1}\bb{M}^T\bbh{\Psi}(\bbh{d}_{\rm obs}-\bb{d}(\bb{p}_0))
+\label{meth:parestimate}
+\bbh{p} = \bb{p}_0 + (\bb{M}^T\bbh{\Psi}\bb{M})^{-1}\bb{M}^T\bbh{\Psi}(\bbh{d}_{\rm obs}-\bb{d}(\bb{p}_0))
 \end{equation}
@@
 \begin{equation}
+\label{meth:parcovestimator}
 (\bbh{\Sigma})_{\alpha\beta} = -\left(\frac{\partial^2 \log \mathcal{L}(\bb{p})}{\partial p_\alpha \partial p_\beta}\right)^{-1}_{\bb{p}_0} = ((\bb{M}^T\bbh{\Psi}\bb{M})^{-1})_{\alpha\beta}
@@
 %
-The $1\sigma$ square parameter errors $\Delta \bbh{p}^2$ are the diagonal entries of $\bbh{\Sigma}$. This method of forecasting parameters takes the name of Fisher Matrix formalism. 
+The $1\sigma$ square parameter errors $\Delta \bbh{p}^2$ are the diagonal entries of $\bbh{\Sigma}$.
+This method of forecasting parameters takes the name of Fisher Matrix formalism (see \citep{astroMLText} for a possible reference).
+When the dimension $N_b$ of the summary statistics space is large, numerical issues can arise in the estimation of the parameter error bars if the covariance matrix $\bbh{C}$ is measured from simulations.
+When $N_r$ independent realizations are used to estimate $\bbh{C}$, its inverse $\bbh{\Psi}$ is biased by a constant factor (see \citep{Hartlap07,Taylor12,Taylor14}) that can be taken into account.
+When the bias correction is applied, we can calculate the expectation value of the covariance estimator (\ref{meth:parcovestimator}) (see again\citep{Taylor14})
+\begin{equation}
+\label{meth:covdegradation}
+\langle\bbh{\Sigma}\rangle = \left(\frac{N_r-N_b+N_p-1}{N_r-N_b-2}\right)\bb{\Sigma}
+\end{equation}   
+%
+where $\bb{\Sigma}$ is the asymptotic covariance one obtains with an infinite number of realizations and $N_p$ is the number of parameters we are estimating, in this case 3.
+The scatter of the parameter estimates (\ref{meth:parestimate}) on the other hand scales as
+\begin{equation}
+\label{meth:estdegradation}
+\langle{\rm Cov}(\bbh{p})\rangle = \left(\frac{N_r-2}{N_r-N_b+N_p-2}\right)\bb{\Sigma}
+\end{equation}
+%
+Although equations (\ref{meth:covdegradation}) and (\ref{meth:estdegradation}) agree in the limit $N_r\rightarrow\infty$, they can be different when a finite number of realizations is used.
+More in detail, the degradation factor in the parameter covariance estimate in (\ref{meth:covdegradation}) is of order $1+(1+N_p)/N_r$, while the actual scatter of the estimates $\bbh{p}$ is of order $1+(N_b-N_p)/N_r$.
+These numbers can very different if $N_b$ is big.
+This means that the parameter error bar estimate (\ref{meth:covdegradation}) is too conservative if $N_b/N_r$ is of order unity.
+This could be likely the case in the analysis we are carrying because of the inclusion of tomography information.
+In order to avoid these error degradation issues, we apply dimensional reduction techniques to the summary statistics we are considering.
+These techniques are explained in the next paragraph.
+
 %%%%%%%%
@@
 \subsection{Dimensionality reduction}
-
+We apply Principal Component Analysis techniques (see \citep{astroMLText} for example) to reduce the dimensionality of our summary statistics while preserving the cosmological information content.
+Consider the model statistic $\bb{d}(\bb{p})$, and think of it in terms of a $P\times N_b$ matrix $d_{pi}$.
+Consider the whitened model matrix
+\begin{equation}
+\Delta_{pi} = P\frac{d_{pi}}{\sum_{q=1}^Pd_{qi}} - 1
+\end{equation} 
+%
+We perform a Singular Value Decomposition (SVD) of $\Delta$ 
+\begin{equation}
+\bb\Delta = \bb{L}\bb{\Lambda} \bb{R}
+\end{equation}
+%
+where $L$ is $P\times Q$, $\bb{\Lambda}={\rm diag}(\Lambda_1,...,\Lambda_Q)$ and $\bb{R}$ is $Q\times N_b$ and $Q={\min}(P,N_b)$.
+$R_{ni}$ is the $i$-th component of the $n$-th basis vector in statistics space.
+The singular value $\Lambda_n$ is the variance of the whitened summary statistic along the $n$-th basis vector.
+We assume that only summary statistic projections on the first $N_c$ basis vectors contain relevant cosmological information, and $N_c<N_b$ is a number that has to be determined from the simulations.
+Let $\bb{R}(N_c)$ be a matrix made of the first $N_c$ rows of $\bb{R}$ (we assume that the singular values $\Lambda_i$ are sorted).
+We define the PCA projection of a summary statistic $\bbh{d}$ on $N_c$ principal components as
+\begin{equation}
+\h{d}_n(N_c) = \sum_{i=1}^{N_b}(\bb{R}(N_c))_{ni}\left(P\frac{\h{d}_i}{\sum_{p=1}^P d_{pi}}-1\right) 
+\end{equation} 
+%
+In this way we hope to capture the cosmological information contained in $\bbh{d}$ by projecting it on the $N_c<N_b$ principal components that vary the most with cosmology parameters.
+In the next section we outline the main results of this work.
 %%%%%%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Results}
+
+\begin{figure*}
+\includegraphics[scale=0.3]{Figures/w_power_spectrum_pca.eps}
+\includegraphics[scale=0.3]{Figures/w_peaks_pca.eps}
+\includegraphics[scale=0.3]{Figures/w_moments_pca.eps}
+\caption{Constraints on $w$ as a function of $N_c$}
+\label{fig:pcacomponents}
+\end{figure*}
+
+\begin{figure}
+\includegraphics[scale=0.3]{Figures/photoz_bias.eps}
+\caption{Bias due to photo-$z$ errors}
+\label{fig:photozbias}
+\end{figure}
 

### 2016-03-25 photoz_paper/Figures/generate.py

@@ -1,10 +1,12 @@
 #!/usr/bin/env python
 
-import sys,argparse
+import sys,os,argparse
 sys.modules["mpi4py"] = None
 
 import numpy as np
 import matplotlib.pyplot as plt
+
+from lenstools.catalog.shear import Catalog
 
 from library.featureDB import FisherDatabase
 
@@ -32,37 +34,110 @@ par2value = {
 }
 
 ###################################################################################################
+###################################################################################################
 
-def photoz_bias(cmd_args,db_name="data/fisher/constraints_photoz.sqlite",parameters=["Om","w"],feature_label="power_spectrum_pca",fontsize=22):
+def galdistr(cmd_args,fontsize=22):
+
+	#Set up plot
+	fig,ax = plt.subplots()
+
+	#Read in galaxy redshifts
+	colors = ["blue","green","red","purple","yellow"]
+	position_files = [os.path.join("data","positions_bin{0}.fits".format(n)) for n in range(1,6)]
+	for n,f in enumerate(position_files):
+		z = Catalog.read(f)["z"]
+
+		#Make the histogram
+		ng,zb = np.histogram(z,bins=np.arange(z.min(),z.max(),0.02))
+		ax.plot(0.5*(zb[1:]+zb[:-1]),ng,color=colors[n],label=r"$z\in[{0:.2f},{1:.2f}]$".format(z.min(),z.max()))
+		ax.fill_between(0.5*(zb[1:]+zb[:-1]),np.zeros_like(ng),ng,color=colors[n],alpha=0.3)
+
+	#Labels
+	ax.set_xlabel(r"$z$",fontsize=fontsize)
+	ax.set_ylabel(r"$N_g$",fontsize=fontsize)
+	ax.legend()
+
+	#Save figure
+	fig.savefig("galdistr."+cmd_args.type)
+
+###################################################################################################
+###################################################################################################
+
+def pca_components(cmd_args,db_name="data/fisher/constraints.sqlite",feature_label="power_spectrum_pca",parameter="w",fontsize=22):
+
+	#Use automatic plot routine
+	with FisherDatabase(db_name) as db:
+		fig,axes = db.plot_by_feature([feature_label],table_name="pcov_noise",parameter="w")
+
+	#Labels
+	axes[0].set_ylabel(r"$\Delta$"+par2label[parameter],fontsize=fontsize)
+
+	#Save figure
+	fig.savefig("{0}_{1}.".format(parameter,feature_label)+cmd_args.type)
+
[…]

### 2016-03-25 code/library/featureDB.py
modified fonts/labels

@@ -516,27 +516,32 @@ class FisherDatabase(Database):
 		return fig,axes
 
 	#Plot shortcut by feature
-	def plot_by_feature(self,features,table_name,parameter):
+	def plot_by_feature(self,features,table_name,parameter,title=True):
 		fig,axes = plt.subplots(1,len(features),figsize=(8*len(features),8))
+
+		try:
+			len(axes)
+		except TypeError:
+			axes = [axes]
 		
 		#Plot single redshift
 		for nfeat,feature in enumerate(features):
 			for n in range(5):
 				b,p = self.query_parameter_simple(feature+"_z{0}".format(n),table_name,parameter)
 				axes[nfeat].plot(b,np.sqrt(p),label=r"$z\in[{0:.2f},{1:.2f}]$".format(*self.z_bins[n]))
-			axes[nfeat].set_title(feature)
+			axes[nfeat].set_title(r"${\rm " + feature.replace("_pca","").replace("_","\,\,") + r"}$",fontsize=22)
 
 		#Plot alltogether
 		for nfeat,feature in enumerate(features):
 			b,p = self.query_parameter_simple(feature,table_name,parameter)
-			axes[nfeat].plot(b,np.sqrt(p),label=r"$z$"+ " tomography")
+			axes[nfeat].plot(b,np.sqrt(p),label=r"$z$"+ r" ${\rm tomography}$")
 
 		#Axes labels
 		for ax in axes:
-			ax.set_xlabel("PCA components",fontsize=18)
-			ax.set_ylabel(r"$\Delta$" + parameter)
+			ax.set_xlabel(r"$N_c$",fontsize=22)
+			ax.set_ylabel(r"$\Delta$" + parameter,fontsize=22)
 			ax.set_yscale("log")
-			ax.legend(prop={"size":10})
+			ax.legend(prop={"size":16})
 
 		#Tight layout
 		fig.tight_layout()

### 2016-03-28 code/library/driver_mpi.py
fix split_redshift

@@ -159,15 +159,18 @@ def split_redshifts(specs,redshift_index=range(5)):
 		
 		#Deep copy of the original dictionary
 		specs_redshift = dict()
-		for key in ["dbname","table_name","feature_label_root","feature_label_format","features","realizations_for_covariance","realizations_for_data","pca_components"]:
-			specs_redshift[key] = specs[key]
+		for key in ["output_dbname","output_table_name","feature_label_root","feature_label_format","features","realizations_for_covariance","realizations_for_data","pca_components","mock_data_realizations"]:
+			try:
+				specs_redshift[key] = specs[key]
+			except:
+				pass
 
 		#Append redshift label to name
 		specs_redshift["feature_label_root"] += "_z{0}".format(zi)
 		
 		#Update features with redshift filter
 		for feature in specs["features"]:
-			specs_redshift[feature] = dict((("feature_filter",specs[feature]["feature_filter"]),("realization_filter",specs[feature]["realization_filter"])))
+			specs_redshift[feature] = dict((("features_dbname",specs[feature]["features_dbname"]),("data_table",specs[feature]["data_table"]),("feature_filter",specs[feature]["feature_filter"]),("realization_filter",specs[feature]["realization_filter"])))
 			specs_redshift[feature]["redshift_filter"] = " AND ".join(["{0}={1}".format(l,zi) for l in getattr(settings,feature).redshift_labels])
 	
 		#Append to list

### 2016-03-28 code/library/driver_mpi.py
fix split_redshift

@@ -171,7 +171,7 @@ def split_redshifts(specs,redshift_index=range(5)):
 		#Update features with redshift filter
 		for feature in specs["features"]:
 			specs_redshift[feature] = dict((("features_dbname",specs[feature]["features_dbname"]),("data_table",specs[feature]["data_table"]),("feature_filter",specs[feature]["feature_filter"]),("realization_filter",specs[feature]["realization_filter"])))
-			specs_redshift[feature]["redshift_filter"] = " AND ".join(["{0}={1}".format(l,zi) for l in getattr(settings,feature).redshift_labels])
+			specs_redshift[feature]["redshift_filter"] = " AND ".join(["{0}={1}".format(l,zi) for l in getattr(default_settings,feature).redshift_labels])
 	
 		#Append to list
 		splitted_specs.append(specs_redshift)

### 2016-03-28 photoz_paper/paper.tex
create new figures

@@
 The sampling procedure is the same described in \citep{CFHTMink,CFHTPeaks}.
+The parameter space sampling we adopted for our simulations is shown in Figure \ref{fig:simdesign}
 
-%ADD Simulation specifications
-
-For each of these simulations, the $N$--body initial conditions are generated using the same random seed.
+\begin{figure*}
+\includegraphics[scale=0.4]{Figures/design.eps}
+\caption{Parameter space sampling}
+\label{fig:simdesign}
+\end{figure*}
+%
+For each of the parameter choices in Figure \ref{fig:simdesign}, the $N$--body initial conditions are generated using the same random seed.
 In addition to this simulations, we produce simulated shear catalogs for a fiducial $\Lambda$CDM universe with $\bb{p}_0=(0.26,-1,0.8)$.
@@
 Several models have been proposed in the literature for the photometric bias $b_{\rm ph}(z_s)$ (see for example \citep{Huterer2006}) and variance $\sigma_{\rm ph}(z_s)$ (see for example \citep{LSSTSciBook}).
-We make use of the photo-$z$ bias and variance values contained in the LSST Science Book \citep{LSSTSciBook}.
+We make use of the photo-$z$ bias and variance values contained in the LSST Science Book \citep{LSSTSciBook}, which we show in Figure \ref{fig:lsstscibook}.
 The bin sizes are adjusted so that each of them contains the same number of galaxies.
@@
 \label{fig:galdistr}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.3]{Figures/scibook.eps}
+\caption{LSST Science Book}
+\label{fig:lsstscibook}
 \end{figure}
@@
 
+\begin{figure}
+\includegraphics[scale=0.3]{Figures/constraints.eps}
+\caption{Constraints in $(\Omega_m,w)$ space}
+\label{fig:constraintsOm-w}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%% DISCUSSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-03-28 photoz_paper/Figures/generate.py

@@ -7,6 +7,8 @@ import numpy as np
 import matplotlib.pyplot as plt
 
 from lenstools.catalog.shear import Catalog
+from lenstools.statistics.constraints import FisherAnalysis
+from lenstools.simulations.design import Design
 
 from library.featureDB import FisherDatabase
 
@@ -32,6 +34,28 @@ par2value = {
 "sigma8" : 0.8
 
 }
+
+###################################################################################################
+###################################################################################################
+
+def design(cmd_args,fontsize=22):
+
+	#Set up plot
+	fig,ax = plt.subplots(1,2,figsize=(16,8))
+
+	#Read in the simulation design
+	design = Design.read("md/design.pkl")
+	parameters = [("Om","w"),("Om","sigma8")]
+
+	#Plot the points
+	for n,(p1,p2) in enumerate(parameters):
+		ax[n].scatter(design[p1],design[p2],marker="x")
+		ax[n].scatter(par2value[p1],par2value[p2],marker="x",color="red",s=50)
+		ax[n].set_xlabel(par2label[p1],fontsize=fontsize)
+		ax[n].set_ylabel(par2label[p2],fontsize=fontsize)
+
+	#Save figure
+	fig.savefig("design."+cmd_args.type)
 
 ###################################################################################################
 ###################################################################################################
@@ -63,7 +87,31 @@ def galdistr(cmd_args,fontsize=22):
 ###################################################################################################
 ###################################################################################################
 
-def pca_components(cmd_args,db_name="data/fisher/constraints.sqlite",feature_label="power_spectrum_pca",parameter="w",fontsize=22):
+def scibook_photo(cmd_args,fontsize=22):
+
+	#Set up plot
+	fig,ax = plt.subplots()
+
+	#Read in bias and sigma
+	z,b = np.loadtxt("data/photoz/SciBook_bias_gold.out",unpack=True)
+	z,s = np.loadtxt("data/photoz/SciBook_sigma_gold.out",unpack=True)
+
+	#Plot
+	ax.plot(z,b,label=r"$b(z_s)$",color="black")
[…]

### 2016-03-30 photoz_paper/paper.tex
completed first draft

@@
 We forecast parameter constraints on the triplet $(\Omega_m,w,\sigma_8)$ for a LSST like galaxy photometric survey, using tomography of the shear-shear power spectrum, convergence peak counts and higher convergence moments.
+We find that the addition of peak and counts to the power spectrum can significantly improve the constraints on the $(\Omega_m,w)$ doublet.
 We evaluate the effect of uncorrected photometric redshift systematics on parameter constraints.
-We show that different statistics lead to different bias directions in parameter space, leaving a window open for self--calibration.
+We find that different statistics lead to different bias directions in parameter space, leaving a window open for self--calibration.
 \end{abstract}
@@
 %
-This work is organized as follows: we give an outline of the shear simulations we use in this work, followed by descriptions of the convergence reconstruction procedure and forward modeling of galaxy shape and redshift systematics.
-We then give an overview of the parameter inferences technique we used to forecast constraints on cosmology.
+Weak Gravitational Lensing is a promising technique to probe the Large Scale Structure of the universe in which the tracers are unbiased \citep{wlreview}.
+This technique has the potential of improving significantly the constraints on the Dark Energy equation of state $w$ because it is most sensitive to the matter density fluctuations at the non--linear stage.
+Cosmology inferences from Weak Lensing observations have been produced for past (CFHTLenS \citep{cfht1}) and current (DES \citep{DES}) surveys, and are being planned for future experiments as well (LSST \citep{LSST}, WFIRST \citep{WFIRST}, Euclid \citep{Euclid}).
+Because of the non-linear nature of the density fluctuations probed by Weak Lensing, cosmological information might leak from quadratic statistics (such as two point functions and power spectra) into more complicated non-Gaussian statistics, for which forward modeling from cosmological parameters requires numerical simulations of cosmic shear fields.
+An extensive list of these non-Gaussian statistics, and their cosmological information content, have been investigated extensively in the literature.
+We investigate the constraining power of a subset of these non-Gaussian statistics combined with redshift tomography in a LSST-like survey.
+We also investigate the effects of uncorrected photometric redshift systematics on parameter constraints when using redshift tomography.
+This work is organized as follows: we give an outline of the shear simulations we use in this work, followed by descriptions of the convergence reconstruction procedure and forward modeling of galaxy shape and photometric redshift systematics.
+We then give an overview of the parameter inferences techniques we used to forecast constraints on cosmology.
 We then discuss the main results of this work and present our conclusions as well as prospects for future work.
@@
 \begin{equation}
+\label{meth:galdistr}
 n(z) = n_0\left(\frac{z}{z_0}\right)^2\exp\left(-\frac{z}{z_0}\right)
@@
 \includegraphics[scale=0.4]{Figures/design.eps}
-\caption{Parameter space sampling}
+\caption{Parameter space sampling chosen for our simulations.
+We show both the sampling in the $(\Omega_m,w)$ (left) and $(\Omega_m,\sigma_8)$ (right) slices of the parameter space.
+The fiducial cosmology has been marked in red.}
 \label{fig:simdesign}
@@
 \includegraphics[scale=0.3]{Figures/galdistr.eps}
-\caption{Galaxy distribution assumed throughout this work, along with the choice of the redshift bins $\bar{z}_b$.}
+\caption{Galaxy distribution assumed throughout this work (see equation (\ref{meth:galdistr})), along with the choice of the redshift bins $\bar{z}_b$.
+Our galaxy sample consists of $N_g=10^6$ galaxies.
+The figure shows the number of galaxies $N_g(z)$ at each redshift $z$.}
 \label{fig:galdistr}
@@
 \includegraphics[scale=0.3]{Figures/scibook.eps}
-\caption{LSST Science Book}
+\caption{Photo-$z$ bias $b_{\rm ph}(z_s)$ (black) and standard deviation $\sigma_{\rm ph}(z_s)$ (red) as a function of the source redshift $z_s$ for two different models, optimistic (solid lines) and pessimistic (dashed lines), obtained from the LSST Science Book \citep{LSSTSciBook}.}
 \label{fig:lsstscibook}
@@
 \label{meth:psdefinition}
-\tilde\kappa(\pmb{\ell},\bar{z}_b) = \left(\frac{\tilde{\gamma}^1(\pmb{\ell},\bar{z}_b)(\ell_x^2-\ell_y^2)+2\ell_1\ell_2\tilde{\gamma}^2(\pmb{\ell},\bar{z}_b)}{\ell_x^2+\ell_y^2}\right) e^{-\frac{\ell^2\theta_G^2}{2}}
+\tilde\kappa(\pmb{\ell},\bar{z}_b) = \left(\frac{\tilde{\gamma}^1(\pmb{\ell},\bar{z}_b)(\ell_x^2-\ell_y^2)+2\ell_x\ell_y\tilde{\gamma}^2(\pmb{\ell},\bar{z}_b)}{\ell_x^2+\ell_y^2}\right) e^{-\frac{\ell^2\theta_G^2}{2}}
 \end{equation}
@@
 \begin{equation}
-{\rm Re}\left(\langle\tilde{\kappa}(\pmb{\ell},\bar{z}_b)\tilde{\kappa}(\pmb{\ell}',\bar{z}_{b'})\rangle\right) = (2\pi)^2\delta_D(\pmb{\ell}+\pmb{\ell}')P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})
+\langle\tilde{\kappa}(\pmb{\ell},\bar{z}_b)\tilde{\kappa}(\pmb{\ell}',\bar{z}_{b'})\rangle = (2\pi)^2\delta_D(\pmb{\ell}+\pmb{\ell}')P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})
 \end{equation}
@@
 \begin{equation}
+\label{meth:pcaprojection}
 \h{d}_n(N_c) = \sum_{i=1}^{N_b}(\bb{R}(N_c))_{ni}\left(P\frac{\h{d}_i}{\sum_{p=1}^P d_{pi}}-1\right) 
@@
 \section{Results}
+In this section we illustrate the main results of this work.
+Figure \ref{fig:pcacomponents} shows the robustness of the dimensionality reduction technique we adopted.
+on the three summary statistics considered, namely the convergence power spectrum $P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})$, peak counts $n_{\rm pk}(\nu,\bar{z}_b)$ and moments $\pmb{\mu}(\bar{z}_b)$.
+To measure the power spectrum we chose 15 uniformly spaced multipole bins between $(\ell_{\rm min},\ell_{\rm max})=(200,2000)$, for a total of $N_b=15\times 15=225$ measurement bands, including cross redshift information.
+We bin the convergence peak counts in 30 uniformly spaced $\nu$ bins between $(\nu_{\rm min},\nu_{\rm max})=(-2,7)$, for a total of $N_b=30\times5=150$ measurement bands, including redshift information.
+The total size of the moments summary statistic vector is $N_b=9\times 5=45$, including redshift information.
+The forecast error bars on $w$ are calculated according to equation (\ref{meth:parcovestimator}), where the covariance matrix $\bbh{C}$ and its inverse $\bbh{\Psi}$ have been estimated with $N_r=16000$ realizations of each summary statistic in the fiducial cosmology.
+Figure \ref{fig:constraintsOm-w} shows the $1\sigma$ confidence contours on the $(\Omega_m,w)$ doublet calculated with equation (\ref{meth:parcovestimator}) after the PCA dimensionality reduction performed according to equation (\ref{meth:pcaprojection}), for a variety of choices $({\rm statistic},N_c)$.
+We also show the improvements on the confidence contours when combining different summary statistics after the corresponding dimensionality reductions have been performed.
+Figure \ref{fig:photozbias} shows the effect of ignoring photo-$z$ errors on parameter constraints.
+To evaluate this effect we construct different mock observations, with and without photo-$z$ effects, and compare the results of the parameter fit according to equation (\ref{meth:parestimate}).
+Using our simulation suite, we construct 20 mock observations: the summary statistic in each observation is calculated by taking the mean of a random sample of $N_{\rm FOV}$ realizations of the summary statistic in the fiducial cosmology (randomly chosen among the ensemble of $N_r=16000$ that are available in the ensemble).
+The estimated covariance matrix $\bbh{C}$ is scaled by a factor $N_{\rm FOV}$ to take into account the construction process of the mock observations.
+This procedure allows to forecast the results an LSST-like survey would obtain.
 
@@
 \includegraphics[scale=0.3]{Figures/w_moments_pca.eps}
-\caption{Constraints on $w$ as a function of $N_c$}
+\caption{$1\sigma$ errors on $w$ as a function of the number of the principal components $N_c$, using the power spectrum (top left), peak counts (top right) and moments (bottom).
+The thin colored lines refer to single redshift summary statistics, while the thick black line shows the case in which the joint redshift information is included.}
 \label{fig:pcacomponents}
@@
 \begin{figure}
-\includegraphics[scale=0.3]{Figures/photoz_bias.eps}
-\caption{Bias due to photo-$z$ errors}
-\label{fig:photozbias}
+\includegraphics[scale=0.3]{Figures/constraints.eps}
+\caption{$1\sigma$ confidence contours on the $(\Omega_m,w)$ parameter space obtained using equation (\ref{meth:parcovestimator}).
+The covariance matrix $\bbh{C}$ and its inverse $\bbh{\Psi}$ have been obtained using $16000$ summary statistics realizations, and has been scaled by a factor $N_{\rm FOV}=1600$ to mimic the constraining power of an LSST-like survey.}
+\label{fig:constraintsOm-w}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[scale=0.3]{Figures/constraints.eps}
-\caption{Constraints in $(\Omega_m,w)$ space}
-\label{fig:constraintsOm-w}
+\includegraphics[scale=0.3]{Figures/photoz_bias.eps}
+\caption{Distribution of parameter estimates in the $(\Omega_m,w)$ parameter space using the power spectrum (black), peak counts (black) and moments (blue) to fit 20 LSST-like mock observations.
+The parameter deviations $(\delta\Omega_m,\delta w)$ are obtained comparing parameter estimates according to equation (\ref{meth:parestimate}) with and without photo-$z$ errors.
+Results for both optimistic (dots) and pessimistic (crosses) are shown.
+The colored squares and the ellipses correspond to respectively to the mean and $1\sigma$ level of the $(\delta\Omega_m,\delta w)$ distribution in the pessimistic systematics case, assuming this distribution is Gaussian.}
+\label{fig:photozbias}
 \end{figure}
@@
 \section{Discussion}
+In this section we discuss our findings.
+Figure \ref{fig:pcacomponents} shows that our dimensionality reduction technique is robust.
+For all the summary statistics we consider, we notice that a plateau in the $w$ error is reached for a sufficient high number of principal components $N_c$.
+We also see that for single redshift statistics, this plateau is reached for $\sim 5$ components for the power spectrum and the moments, and $\sim 10$ components for the peak counts.
+The number of components to consider increases when including redshift information, and can reach $\sim 30$ for the power spectrum and moments and $\sim 40$ for the peak counts.
+We can also see that most of the cosmological information is concentrated in the last redshift bin, with tomography improving the constraints by a factor of few for the power spectrum and peak counts.
+
+In Figure \ref{fig:constraintsOm-w} we can see that peak counts and moments can significantly improve the constraints on $(\Omega_m,w)$ when combined with the power spectrum.
+Combining the peaks or the moments to the power spectrum improves the $w$ constraint by a factor of 1.7 while considering the three statistics together the error improves by an additional $30\%$.
+This shows that peaks and moments contain cosmological information that is not contained in the power spectrum, because a similar improvement cannot be obtained by increasing the number of PCA components in the power spectrum dimensionality reduction procedure.
+
+Figure \ref{fig:photozbias} quantifies the effect of uncorrected photo-$z$ errors on $(\Omega_m,w)$ constraints.
+Because the random nature of the observations, parameter values $\bbh{p}$ estimated from equation (\ref{meth:parestimate}) are affected by statistical fluctuations.
+In Figure \ref{fig:photozbias} we show 20 random draws from the probability distribution of $\delta \bbh{p}=\bbh{p}_{\rm photo-z}-\bbh{p}_{\rm no-photo-z}$.
+We can conclude that the $\bbh{p}$ estimator is biased if $\langle\delta\bbh{p}\rangle\neq 0$.
+Figure \ref{fig:photozbias} clearly show that photo-$z$ errors cause parameter biases at more than $1\sigma$ significance level when using the power spectrum and the moments, while no bias is observed for the peak count statistic within the constraining accuracy.
+We also observe that photo-$z$ errors bias the constraints in different directions, leaving open possibilities for bias self--calibration techniques.
 
@@
 \section{Conclusions}
+In this work we study cosmological parameter constraints forecasts for an LSST-like galaxy survey using the convergence power spectrum and a range of non--Gaussian statistics.
+We make use of redshift tomography to improve the constraints from their single redshift counterparts.
+We also investigate the effects of uncorrected photo-$z$ systematic effects on the inferred cosmology.
+We find that:
+\begin{itemize}
+	\item Principal Component analysis is a robust technique to keep the dimensionality of the parameter space under control and avoid the numerical pitfalls explained in \citep{Taylor12,DodelsonSchneider13,Taylor14} and more recently \citep{PetriVariance}.
+In particular we find that only a few components are necessary to characterize the cosmological information content in single redshift statistics, while more components are necessary when tomography is included.
+	\item Peak counts and moments can significantly improve $(\Omega_m,w)$ parameter constraints when used in combination with the power spectrum.
+	\item Uncorrected photo-$z$ systematics can bias parameter constraints, but the direction of the bias is different for each summary statistic, leaving open windows for self-calibration
+\end{itemize}
 

### 2016-03-30 code/library/featureDB.py

@@ -523,6 +523,11 @@ class FisherDatabase(Database):
 			len(axes)
 		except TypeError:
 			axes = [axes]
+
+		#Plot alltogether
+		for nfeat,feature in enumerate(features):
+			b,p = self.query_parameter_simple(feature,table_name,parameter)
+			axes[nfeat].plot(b,np.sqrt(p),linewidth=3.5,label=r"$z$"+ r" ${\rm tomography}$")
 		
 		#Plot single redshift
 		for nfeat,feature in enumerate(features):
@@ -530,11 +535,6 @@ class FisherDatabase(Database):
 				b,p = self.query_parameter_simple(feature+"_z{0}".format(n),table_name,parameter)
 				axes[nfeat].plot(b,np.sqrt(p),label=r"$z\in[{0:.2f},{1:.2f}]$".format(*self.z_bins[n]))
 			axes[nfeat].set_title(r"${\rm " + feature.replace("_pca","").replace("_","\,\,") + r"}$",fontsize=22)
-
-		#Plot alltogether
-		for nfeat,feature in enumerate(features):
-			b,p = self.query_parameter_simple(feature,table_name,parameter)
-			axes[nfeat].plot(b,np.sqrt(p),label=r"$z$"+ r" ${\rm tomography}$")
 
 		#Axes labels
 		for ax in axes:

### 2016-03-30 photoz_paper/Figures/generate.py

@@ -78,7 +78,7 @@ def galdistr(cmd_args,fontsize=22):
 
 	#Labels
 	ax.set_xlabel(r"$z$",fontsize=fontsize)
-	ax.set_ylabel(r"$N_g$",fontsize=fontsize)
+	ax.set_ylabel(r"$N_g(z)$",fontsize=fontsize)
 	ax.legend()
 
 	#Save figure
@@ -97,8 +97,16 @@ def scibook_photo(cmd_args,fontsize=22):
 	z,s = np.loadtxt("data/photoz/SciBook_sigma_gold.out",unpack=True)
 
 	#Plot
-	ax.plot(z,b,label=r"$b(z_s)$",color="black")
-	ax.plot(z,s,label=r"$\sigma(z_s)$",color="red")
+	ax.plot(z,b,label=r"$b_{\rm ph}(z_s)$ ${\rm optimistic}$",color="black")
+	ax.plot(z,s,label=r"$\sigma_{\rm ph}(z_s)$ ${\rm optimistic}$",color="red")
+
+	#Read in bias and sigma
+	z,b = np.loadtxt("data/photoz/weightcombo_bias_gold.out",unpack=True)
+	z,s = np.loadtxt("data/photoz/weightcombo_sigma_gold.out",unpack=True)
+
+	#Plot
+	ax.plot(z,b,label=r"$b_{\rm ph}(z_s)$ ${\rm pessimistic}$",color="black",linestyle="--")
+	ax.plot(z,s,label=r"$\sigma_{\rm ph}(z_s)$ ${\rm pessimistic}$",color="red",linestyle="--")
 
 	#Labels
 	ax.set_xlabel(r"$z_s$",fontsize=fontsize)
@@ -245,8 +253,8 @@ def photoz_bias(cmd_args,db_name="data/fisher/constraints_photoz.sqlite",paramet
 	ax.set_ylim(-ylim,ylim)
 
 	#Legends
-	ax.set_xlabel(r"${\rm bias}$"+ "$($" + par2label[parameters[0]] + "$)$",fontsize=fontsize)
-	ax.set_ylabel(r"${\rm bias}$"+ "$($" + par2label[parameters[1]] + "$)$",fontsize=fontsize)
+	ax.set_xlabel(r"$\delta$" + par2label[parameters[0]],fontsize=fontsize)
+	ax.set_ylabel(r"$\delta$" + par2label[parameters[1]],fontsize=fontsize)
 	ax.legend(loc="upper left")
 
 	#Save figure

### 2016-04-05 photoz_paper/paper.tex
fix typo
implemented Zoltan edits 1

@@
 
-\title{Cosmology with photometric surveys: constraints with redshift tomography of non--Gaussian statistics}
+\title{Cosmology with Weak Lensing photometric surveys: constraints with redshift tomography of non--Gaussian statistics}
 
@@
 Because of the non-linear nature of the density fluctuations probed by Weak Lensing, cosmological information might leak from quadratic statistics (such as two point functions and power spectra) into more complicated non-Gaussian statistics, for which forward modeling from cosmological parameters requires numerical simulations of cosmic shear fields.
-An extensive list of these non-Gaussian statistics, and their cosmological information content, have been investigated extensively in the literature.
-We investigate the constraining power of a subset of these non-Gaussian statistics combined with redshift tomography in a LSST-like survey.
+Different examples of these non-Gaussian statistics, and their cosmological information content, have been investigated extensively in the literature (see \citep{MinkJan,PeaksJan,NG-Marian,NG-Jain1,NG-Jain2,NG-Jain3,NG-Refregier,NG-Dietrich} for a non comprehensive list).
+The constraining power of Weak Lensing power spectra with the addition of redshift tomography information have been extensively investigated in the literature (see \citep{SongKnox,FangHaiman07,Huterer2006}).
+In this work we concentrate on the constraining power of a subset of these non-Gaussian statistics combined with redshift tomography in a LSST-like survey.
+Previous work on redshift tomography with Weak Lensing Minkowski functionals is also present in the literature \citep{MinkJan}.
 We also investigate the effects of uncorrected photometric redshift systematics on parameter constraints when using redshift tomography.
@@
 We simulate $N_g = 10^6$ random galaxy positions $\{\pmb{\theta}_g\}$ distributed uniformly in a field of view of size $\theta_{\rm FOV}^2=(3.5{\rm deg})^2$, which correspond to a galaxy angular density of $n_g=22\,\rm{arcmin}^{-2}$.
-The galaxy have a distribution in redshift which mimics the one expected in the LSST survey
+The galaxies have a distribution in redshift which mimics the one expected in the LSST survey
 \begin{equation}
@@
 with $z_0=0.3$ and $n_0$ a normalization constant fixed so that $n(z)$ integrates to the total number of galaxies $N_g$.
+The galaxies have a maximum redshift $z_{\rm max}=3$.
 For each galaxy we compute the cosmic shear at $\pmb{\theta}_g$ using equation (\ref{meth:sheareqn}), producing a shear catalog $\{\pmb{\gamma}_g\}$.
@@
 \begin{figure*}
-\includegraphics[scale=0.4]{Figures/design.eps}
+\includegraphics[scale=0.35]{Figures/design.eps}
 \caption{Parameter space sampling chosen for our simulations.
-We show both the sampling in the $(\Omega_m,w)$ (left) and $(\Omega_m,\sigma_8)$ (right) slices of the parameter space.
+We show both the sampling in the $(\Omega_m,w)$ (left), $(\Omega_m,\sigma_8)$ (center) and $(\sigma_8,w)$ (right) slices of the parameter space.
 The fiducial cosmology has been marked in red.}
@@
 For each of the parameter choices in Figure \ref{fig:simdesign}, the $N$--body initial conditions are generated using the same random seed.
-In addition to this simulations, we produce simulated shear catalogs for a fiducial $\Lambda$CDM universe with $\bb{p}_0=(0.26,-1,0.8)$.
-In this case the randomization procedure is based on 5 independent $N$--body simulations, and the same number of pseudo--independent catalog realizations is produced.
+In addition to these simulations, we produce simulated shear catalogs for a fiducial $\Lambda$CDM universe with $\bb{p}_0=(0.26,-1,0.8)$.
+In this case the randomization procedure is based on 5 independent $N$--body simulations, and the same number $N_r=16000$ of pseudo--independent catalog realizations is produced.
+This additional simulation set serves two purposes: it provides an independent dataset from which to measure covariance matrices and it provides a way to construct mock observations that are independent on the simulations on which the cosmological forward model is trained.
+For the fiducial dataset we chose to base the shear randomization procedure on 5 independent $N$--body simulations to ensure the independence of the $N_r$ realizations for the purpose of estimating covariance matrices.
+\citep{PetriVariance} recently showed that, even with only one $N$--body simulation a few $10^4$ independent realizations can be produced.
 
@@
 We give an overview of the shear systematics included in this work.
+
 The measured galaxy ellipticity $\pmb{\epsilon}$ is an estimate of the cosmic shear $\pmb{\gamma}$ due to Large Scale Structure if the non--lensed galaxy shape is a circle.
@@
 One of the goals of this work is to evaluate the size of this effect, assuming photometric redshift errors (photo-$z$) are left uncorrected.
+
 We model effect of photo-$z$ errors as a constant bias term $b_{\rm ph}(z_s)$ plus a random Gaussian component with variance $\sigma_{\rm ph}(z_s)$
@@
 \begin{figure}
-\includegraphics[scale=0.3]{Figures/galdistr.eps}
+\includegraphics[scale=0.3]{Figures/galdistr.pdf}
 \caption{Galaxy distribution assumed throughout this work (see equation (\ref{meth:galdistr})), along with the choice of the redshift bins $\bar{z}_b$.
@@
 The subscript $c$ indicates that we consider only the connected parts of the quartic $\kappa$ moments.
-In the definition of the peak counts and convergence moments we omitted the redshift index $\bar{z}_b$ for notational simplicity, and also because both peak counts and moments do not contain cross redshift information unlike the power spectrum defined in equation (\ref{meth:psdefinition}).
+In the definition of the peak counts and convergence moments we omitted the redshift index $\bar{z}_b$ for notational simplicity.
 In the next paragraph we describe the statistical methods we use to infer cosmological parameter estimates $\bbh{p}$ from mock observations $\h{\kappa}_{\rm obs}(\pmb{\theta}_p,\bar{z}_b)$ using the summary statistics $P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})$, $n_{\rm pk}(\nu,\bar{z}_b)$, $\pmb{\mu}(\bar{z}_b)$.
@@
 The $1\sigma$ square parameter errors $\Delta \bbh{p}^2$ are the diagonal entries of $\bbh{\Sigma}$.
-This method of forecasting parameters takes the name of Fisher Matrix formalism (see \citep{astroMLText} for a possible reference).
+The parameter covariance estimator (\ref{meth:parcovestimator}) is the same that one gets adopting a Fisher Matrix formalism for parameter forecasts (see \citep{astroMLText} for a possible reference).
+
 When the dimension $N_b$ of the summary statistics space is large, numerical issues can arise in the estimation of the parameter error bars if the covariance matrix $\bbh{C}$ is measured from simulations.
@@
 on the three summary statistics considered, namely the convergence power spectrum $P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})$, peak counts $n_{\rm pk}(\nu,\bar{z}_b)$ and moments $\pmb{\mu}(\bar{z}_b)$.
-To measure the power spectrum we chose 15 uniformly spaced multipole bins between $(\ell_{\rm min},\ell_{\rm max})=(200,2000)$, for a total of $N_b=15\times 15=225$ measurement bands, including cross redshift information.
+To measure the power spectrum we chose 15 uniformly spaced multipole bands between $(\ell_{\rm min},\ell_{\rm max})=(200,2000)$.
+Because, of the combinations $(\bar{z}_b,\bar{z}_{b'})$, only 15 of them (5 diagonal + 10 off-diagonal) are independent, this leads to a total of $N_b=15\times 15=225$ power spectrum measurement bands, including cross redshift information.
 We bin the convergence peak counts in 30 uniformly spaced $\nu$ bins between $(\nu_{\rm min},\nu_{\rm max})=(-2,7)$, for a total of $N_b=30\times5=150$ measurement bands, including redshift information.
 The total size of the moments summary statistic vector is $N_b=9\times 5=45$, including redshift information.
+
 The forecast error bars on $w$ are calculated according to equation (\ref{meth:parcovestimator}), where the covariance matrix $\bbh{C}$ and its inverse $\bbh{\Psi}$ have been estimated with $N_r=16000$ realizations of each summary statistic in the fiducial cosmology.
@@
 We also show the improvements on the confidence contours when combining different summary statistics after the corresponding dimensionality reductions have been performed.
+
 Figure \ref{fig:photozbias} shows the effect of ignoring photo-$z$ errors on parameter constraints.
@@
 \includegraphics[scale=0.3]{Figures/w_moments_pca.eps}
-\caption{$1\sigma$ errors on $w$ as a function of the number of the principal components $N_c$, using the power spectrum (top left), peak counts (top right) and moments (bottom).
+\caption{$1\sigma$ errors on $w$, marginalized over $(\Omega_m,\sigma_8)$, as a function of the number of the principal components $N_c$, using the power spectrum (top left), peak counts (top right) and moments (bottom).
 The thin colored lines refer to single redshift summary statistics, while the thick black line shows the case in which the joint redshift information is included.}
@@
 \includegraphics[scale=0.3]{Figures/constraints.eps}
-\caption{$1\sigma$ confidence contours on the $(\Omega_m,w)$ parameter space obtained using equation (\ref{meth:parcovestimator}).
+\caption{$1\sigma$ confidence contours on the $(\Omega_m,w)$ parameter space, marginalized over $\sigma_8$, obtained using equation (\ref{meth:parcovestimator}).
 The covariance matrix $\bbh{C}$ and its inverse $\bbh{\Psi}$ have been obtained using $16000$ summary statistics realizations, and has been scaled by a factor $N_{\rm FOV}=1600$ to mimic the constraining power of an LSST-like survey.}
@@
 \includegraphics[scale=0.3]{Figures/photoz_bias.eps}
-\caption{Distribution of parameter estimates in the $(\Omega_m,w)$ parameter space using the power spectrum (black), peak counts (black) and moments (blue) to fit 20 LSST-like mock observations.
+\caption{Distribution of parameter estimates in the $(\Omega_m,w)$ parameter space using the power spectrum (red), peak counts (green) and moments (blue) to fit 20 LSST-like mock observations.
 The parameter deviations $(\delta\Omega_m,\delta w)$ are obtained comparing parameter estimates according to equation (\ref{meth:parestimate}) with and without photo-$z$ errors.

### 2016-04-05 code/library/featureDB.py

@@ -541,7 +541,7 @@ class FisherDatabase(Database):
 			ax.set_xlabel(r"$N_c$",fontsize=22)
 			ax.set_ylabel(r"$\Delta$" + parameter,fontsize=22)
 			ax.set_yscale("log")
-			ax.legend(prop={"size":16})
+			ax.legend(prop={"size":25})
 
 		#Tight layout
 		fig.tight_layout()

### 2016-04-05 photoz_paper/Figures/generate.py

@@ -41,11 +41,11 @@ par2value = {
 def design(cmd_args,fontsize=22):
 
 	#Set up plot
-	fig,ax = plt.subplots(1,2,figsize=(16,8))
+	fig,ax = plt.subplots(1,3,figsize=(24,8))
 
 	#Read in the simulation design
 	design = Design.read("md/design.pkl")
-	parameters = [("Om","w"),("Om","sigma8")]
+	parameters = [("Om","w"),("Om","sigma8"),("sigma8","w")]
 
 	#Plot the points
 	for n,(p1,p2) in enumerate(parameters):
@@ -107,6 +107,9 @@ def scibook_photo(cmd_args,fontsize=22):
 	#Plot
 	ax.plot(z,b,label=r"$b_{\rm ph}(z_s)$ ${\rm pessimistic}$",color="black",linestyle="--")
 	ax.plot(z,s,label=r"$\sigma_{\rm ph}(z_s)$ ${\rm pessimistic}$",color="red",linestyle="--")
+
+	ax.plot(z,0.003*(1+z),label=r"$b_{\rm ph}(z_s)=0.003(1+z_s)$",color="blue",linestyle="-",linewidth=3)
+	ax.plot(z,0.02*(1+z),label=r"$\sigma_{\rm ph}(z_s)=0.02(1+z_s)$",color="blue",linestyle="--",linewidth=3)
 
 	#Labels
 	ax.set_xlabel(r"$z_s$",fontsize=fontsize)
@@ -200,7 +203,7 @@ def parameter_constraints(cmd_args,db_name="data/fisher/constraints_combine.sqli
 ###################################################################################################
 ###################################################################################################
 
-def photoz_bias(cmd_args,db_name="data/fisher/constraints_photoz.sqlite",parameters=["Om","w"],feature_labels=["power_spectrum_pca","peaks_pca","moments_pca"],colors=["black","red","blue"],fontsize=22):
+def photoz_bias(cmd_args,db_name="data/fisher/constraints_photoz.sqlite",parameters=["Om","w"],feature_labels=["power_spectrum_pca","peaks_pca","moments_pca"],colors=["red","green","blue"],fontsize=22):
 	
 	#Init figure
 	fig,ax = plt.subplots()
@@ -245,8 +248,8 @@ def photoz_bias(cmd_args,db_name="data/fisher/constraints_photoz.sqlite",paramet
[…]

### 2016-04-05 photoz_paper/paper.tex
modified bias figure

@@
 Several models have been proposed in the literature for the photometric bias $b_{\rm ph}(z_s)$ (see for example \citep{Huterer2006}) and variance $\sigma_{\rm ph}(z_s)$ (see for example \citep{LSSTSciBook}).
-We make use of the photo-$z$ bias and variance values contained in the LSST Science Book \citep{LSSTSciBook}, which we show in Figure \ref{fig:lsstscibook}.
-The bin sizes are adjusted so that each of them contains the same number of galaxies.
-The galaxy distribution we assumed, along with the binning choice is shown in Figure \ref{fig:galdistr}
+We chose the photo-$z$ bias and variance functions in equation (\ref{meth:photoz-correction}) to be the science requirements contained in the LSST Science Book \citep{LSSTSciBook}, namely $b(z_s)=0.003(1+z_s)$ and $\sigma(z_s)=0.02(1+z_s)$.
 
@@
 \label{fig:galdistr}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.3]{Figures/scibook.eps}
-\caption{Photo-$z$ bias $b_{\rm ph}(z_s)$ (black) and standard deviation $\sigma_{\rm ph}(z_s)$ (red) as a function of the source redshift $z_s$ for two different models, optimistic (solid lines) and pessimistic (dashed lines), obtained from the LSST Science Book \citep{LSSTSciBook}.}
-\label{fig:lsstscibook}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[scale=0.3]{Figures/constraints.eps}
+\includegraphics[scale=0.3]{Figures/constraints_Om-w.eps}
 \caption{$1\sigma$ confidence contours on the $(\Omega_m,w)$ parameter space, marginalized over $\sigma_8$, obtained using equation (\ref{meth:parcovestimator}).
@@
 \begin{figure}
-\includegraphics[scale=0.3]{Figures/photoz_bias.eps}
+\includegraphics[scale=0.3]{Figures/photoz_bias_Om-w.eps}
 \caption{Distribution of parameter estimates in the $(\Omega_m,w)$ parameter space using the power spectrum (red), peak counts (green) and moments (blue) to fit 20 LSST-like mock observations.

### 2016-04-05 photoz_paper/Figures/generate.py

@@ -122,6 +122,34 @@ def scibook_photo(cmd_args,fontsize=22):
 ###################################################################################################
 ###################################################################################################
 
+def constraints_no_pca(cmd_args,db_name="data/fisher/constraints_combine.sqlite",features=["power_spectrum","peaks","moments"],colors=["red","green","blue"],parameter="w",fontsize=22):
+
+	#Set up plot
+	fig,ax = plt.subplots()
+
+	#Plot each feature 
+	with FisherDatabase(db_name) as db:
+		
+		#Query parameter variance
+		var_db = db.query('SELECT "{0}-{0}",feature_label FROM pcov_noise_no_pca'.format(parameter))
+
+		#Cycle over features 
+		for nf,f in enumerate(features):
+			var_feature = var_db[var_db["feature_label"].str.contains(f)]["{0}-{0}".format(parameter)].values
+			ax.plot(np.sqrt(var_feature),color=colors[nf],label=f)
+
+	#Axes labels
+	ax.set_xticks(range(len(var_feature)))
+	ax.set_xticklabels([r"$z_{0}$".format(n+1) for n in range(len(var_feature))],fontsize=fontsize)
+	ax.set_ylabel(r"$\Delta$"+par2label[parameter],fontsize=fontsize)
+	ax.legend()
+
+	#Save the figure
+	fig.savefig("{0}_no_pca.{1}".format(parameter,cmd_args.type))
+
+###################################################################################################
+###################################################################################################
+
 def pca_components(cmd_args,db_name="data/fisher/constraints_combine.sqlite",feature_label="power_spectrum_pca",parameter="w",fontsize=22):
 
 	#Use automatic plot routine
@@ -146,26 +174,24 @@ def pca_components_moments(cmd_args):
 ###################################################################################################
 ###################################################################################################
 
-features_to_show = {
+feature_properties = {
 
[…]

### 2016-04-06 photoz_paper/paper.tex
finished implementing Zoltan suggestions

@@
 We forecast parameter constraints on the triplet $(\Omega_m,w,\sigma_8)$ for a LSST like galaxy photometric survey, using tomography of the shear-shear power spectrum, convergence peak counts and higher convergence moments.
-We find that the addition of peak and counts to the power spectrum can significantly improve the constraints on the $(\Omega_m,w)$ doublet.
+We find that most the cosmological information is contained in the highest redshift galaxies, with redshift tomography further improving the $w$ constraints by only a few $10\%$.
+We also find that the addition of peak and counts to the power spectrum can significantly improve the constraints on the $(\Omega_m,w)$ doublet.
 We evaluate the effect of uncorrected photometric redshift systematics on parameter constraints.
@@
 %
-where $\pmb{\epsilon}_{\rm n}$ is a random Gaussian variable with zero mean and redshift dependent variance $\sigma_n(z)=0.15+0.035z$.
+where $\pmb{\epsilon}_{\rm n}$ is a random Gaussian variable with zero mean and redshift dependent variance $\sigma_n(z_s)=0.15+0.035z_s$.
 This is equivalent to say that the cosmic shear inferred from ellipticity observations $\pmb{\gamma}_{\rm m}$ can be written as the sum of the true cosmic shear plus a noise term $\pmb{\gamma}_{\rm n}$ with the same statistical properties as $\pmb{\epsilon}_{\rm n}$.
@@
 \section{Results}
+
+\begin{figure*}
+\includegraphics[scale=0.3]{Figures/w_power_spectrum_pca.eps}
+\includegraphics[scale=0.3]{Figures/w_peaks_pca.eps}
+\includegraphics[scale=0.3]{Figures/w_moments_pca.eps}
+\caption{$1\sigma$ errors on $w$, marginalized over $(\Omega_m,\sigma_8)$, as a function of the number of the principal components $N_c$, using the power spectrum (top left), peak counts (top right) and moments (bottom).
+The thin colored lines refer to single redshift summary statistics, while the thick black line shows the case in which the joint redshift information is included.}
+\label{fig:pcacomponents}
+\end{figure*}
+
 In this section we illustrate the main results of this work.
@@
 The forecast error bars on $w$ are calculated according to equation (\ref{meth:parcovestimator}), where the covariance matrix $\bbh{C}$ and its inverse $\bbh{\Psi}$ have been estimated with $N_r=16000$ realizations of each summary statistic in the fiducial cosmology.
+
+Figure \ref{fig:nopca} shows a comparison between the $w$ constraints obtained using single redshift bins, with and without PCA dimensionality reduction, and compares these single redshift constraints with the ones obtained using redshift tomography.
+
+\begin{figure*}
+\includegraphics[scale=0.3]{Figures/w_power_spectrum_no_pca.pdf}
+\includegraphics[scale=0.3]{Figures/w_peaks_no_pca.pdf}
+\includegraphics[scale=0.3]{Figures/w_moments_no_pca.pdf}
+\caption{Comparison between single redshift $w$ constraints (marginalized over $(\Omega_m,\sigma_8)$) obtained without PCA (gray shaded bars) and with PCA (colored bars) as a function of the redshift bin $\bar{z}_b$.
+The rightmost black bar shows the same constraint, but obtained with redshift tomography and using the maximum number of PCA components seen in Figure \ref{fig:pcacomponents}.
+We show constrained obtained with the power spectrum (top right), peak counts (top left) and moments (bottom).}
+\label{fig:nopca}
+\end{figure*}
+
 Figure \ref{fig:constraintsOm-w} shows the $1\sigma$ confidence contours on the $(\Omega_m,w)$ doublet calculated with equation (\ref{meth:parcovestimator}) after the PCA dimensionality reduction performed according to equation (\ref{meth:pcaprojection}), for a variety of choices $({\rm statistic},N_c)$.
@@
 This procedure allows to forecast the results an LSST-like survey would obtain.
-
-\begin{figure*}
-\includegraphics[scale=0.3]{Figures/w_power_spectrum_pca.eps}
-\includegraphics[scale=0.3]{Figures/w_peaks_pca.eps}
-\includegraphics[scale=0.3]{Figures/w_moments_pca.eps}
-\caption{$1\sigma$ errors on $w$, marginalized over $(\Omega_m,\sigma_8)$, as a function of the number of the principal components $N_c$, using the power spectrum (top left), peak counts (top right) and moments (bottom).
-The thin colored lines refer to single redshift summary statistics, while the thick black line shows the case in which the joint redshift information is included.}
-\label{fig:pcacomponents}
-\end{figure*}
 
@@
 The parameter deviations $(\delta\Omega_m,\delta w)$ are obtained comparing parameter estimates according to equation (\ref{meth:parestimate}) with and without photo-$z$ errors.
-Results for both optimistic (dots) and pessimistic (crosses) are shown.
 The colored squares and the ellipses correspond to respectively to the mean and $1\sigma$ level of the $(\delta\Omega_m,\delta w)$ distribution in the pessimistic systematics case, assuming this distribution is Gaussian.}
@@
 We also see that for single redshift statistics, this plateau is reached for $\sim 5$ components for the power spectrum and the moments, and $\sim 10$ components for the peak counts.
+Moreover, Figure \ref{fig:nopca} shows that, at least for the four highest redshift bins $\{\bar{z}_b: b\geq 2\}$, most of the cosmological information contained in the full (pre-PCA) summary statistic vector can be captured with a limited number of principal components $N_c<N_b$.
+
 The number of components to consider increases when including redshift information, and can reach $\sim 30$ for the power spectrum and moments and $\sim 40$ for the peak counts.
-We can also see that most of the cosmological information is concentrated in the last redshift bin, with tomography improving the constraints by a factor of few for the power spectrum and peak counts.
+Figure \ref{fig:nopca} clearly that most of the cosmological information is concentrated in the last redshift bin.
+The use of redshift tomography only tightens the constraints by a few $10\%$.
 
@@
 Combining the peaks or the moments to the power spectrum improves the $w$ constraint by a factor of 1.7 while considering the three statistics together the error improves by an additional $30\%$.
-This shows that peaks and moments contain cosmological information that is not contained in the power spectrum, because a similar improvement cannot be obtained by increasing the number of PCA components in the power spectrum dimensionality reduction procedure.
+This shows that peaks and moments contain cosmological information that is not contained in the power spectrum, because a similar improvement cannot be obtained by simply increasing the number of PCA components in the power spectrum dimensionality reduction procedure.
 
@@
 In particular we find that only a few components are necessary to characterize the cosmological information content in single redshift statistics, while more components are necessary when tomography is included.
+Nevertheless we find that the number of required components $N_c$ is significantly smaller than the full summary statistic space dimensionality before performing PCA.
+	\item Most of the cosmological information is contained in high redshift galaxies, with tomography improving $w$ constraints by only a few $10\%$.   
 	\item Peak counts and moments can significantly improve $(\Omega_m,w)$ parameter constraints when used in combination with the power spectrum.
-	\item Uncorrected photo-$z$ systematics can bias parameter constraints, but the direction of the bias is different for each summary statistic, leaving open windows for self-calibration
+	\item Uncorrected photo-$z$ systematics can bias parameter constraints obtained from the power spectrum and the moments, but in different parameter directions, leaving open windows for self-calibration
 \end{itemize}

### 2016-04-06 photoz_paper/Figures/generate.py

@@ -122,10 +122,17 @@ def scibook_photo(cmd_args,fontsize=22):
 ###################################################################################################
 ###################################################################################################
 
-def constraints_no_pca(cmd_args,db_name="data/fisher/constraints_combine.sqlite",features=["power_spectrum","peaks","moments"],colors=["red","green","blue"],parameter="w",fontsize=22):
+def constraints_no_pca(cmd_args,db_name="data/fisher/constraints_combine.sqlite",feature="power_spectrum",base_color="black",pca_components=[5,10],colors=["red","blue","green"],parameter="w",ylim=None,fontsize=22):
 
 	#Set up plot
 	fig,ax = plt.subplots()
+
+	#Axes bounds
+	if ylim is not None:
+		ax.set_ylim(*ylim)
+
+	#Construct title
+	title = r"${\rm " + feature.replace("_","\,\,") + r"}$"
 
 	#Plot each feature 
 	with FisherDatabase(db_name) as db:
@@ -133,19 +140,43 @@ def constraints_no_pca(cmd_args,db_name="data/fisher/constraints_combine.sqlite"
 		#Query parameter variance
 		var_db = db.query('SELECT "{0}-{0}",feature_label FROM pcov_noise_no_pca'.format(parameter))
 
-		#Cycle over features 
-		for nf,f in enumerate(features):
-			var_feature = var_db[var_db["feature_label"].str.contains(f)]["{0}-{0}".format(parameter)].values
-			ax.plot(np.sqrt(var_feature),color=colors[nf],label=f)
+		#Plot feature without PCA
+		var_feature = var_db[var_db["feature_label"].str.contains(feature)]["{0}-{0}".format(parameter)].values
+		ax.bar(range(len(var_feature)),np.sqrt(var_feature),width=1,color=base_color,label=r"${\rm No}$ ${\rm PCA}$",alpha=0.3)
+
+		#Plot features with PCA
+		for n,nc in enumerate(pca_components):
+			var_db = db.query('SELECT "{0}-{0}",feature_label FROM pcov_noise WHERE bins={1}'.format(parameter,nc))
+			var_feature = var_db[var_db["feature_label"].str.contains(feature+"_pca_z")]["{0}-{0}".format(parameter)].values
[…]

### 2016-04-07 code/management/compress.py
more flexibility in compress/unpack scripts to handle planes/catalogs/snapshots, etc...

@@ -1,12 +1,13 @@
 #!/usr/bin/env python-mpi
 import os
+import argparse
 
 from lenstools.utils import MPIWhirlPool
 from lenstools.pipeline.simulation import SimulationBatch
 
 #Get the resource to compress
-def shear(model,batch):
-	full_path =  model.collections[0].getCatalog("Shear").storage_subdir
+def shear(model,batch,search_string):
+	full_path =  model[search_string].storage
 	rel_path = os.path.relpath(full_path,batch.environment.storage)
 	return rel_path
 
@@ -16,12 +17,20 @@ try:
 except:
 	pool = None
 
-#Current simulation batch 
-batch = SimulationBatch.current()
-models = batch.models
-archive_names = ["archive/{0}.tar.gz".format(m.cosmo_id) for m in models]
+#Parse command line arguments
+parser = argparse.ArgumentParser()
+parser.add_argument("-e","--environment",dest="env_file",action="store",type=str,default="environment.ini",help="environment option file")
+parser.add_argument("-a","--archive",dest="archive",action="store",type=str,default="archive/{0}.tar.gz",help="archive name format")
+parser.add_argument("-s","--search",dest="search",action="store",type=str,default="c0C0",help="search string that when dialed points to the resource")
 
-batch.archive(archive_names,pool=pool,resource=shear,chunk_size=1,batch=batch)
+cmd_args = parser.parse_args()
+
+#Current simulation batch 
+batch = SimulationBatch.current(cmd_args.env_file)
+models = batch.models
+archive_names = [cmd_args.archive.format(m.cosmo_id) for m in models]
+
+batch.archive(archive_names,pool=pool,resource=shear,chunk_size=1,batch=batch,search_string=cmd_args.search)
 
 
 pool.comm.Barrier()

### 2016-04-08 photoz_paper/Figures/generate.py
update figure 4

@@ -142,6 +142,7 @@ def constraints_no_pca(cmd_args,db_name="data/fisher/constraints_combine.sqlite"
 
 		#Plot feature without PCA
 		var_feature = var_db[var_db["feature_label"].str.contains(feature)]["{0}-{0}".format(parameter)].values
+		var_highest_z = var_feature[-1]
 		ax.bar(range(len(var_feature)),np.sqrt(var_feature),width=1,color=base_color,label=r"${\rm No}$ ${\rm PCA}$",alpha=0.3)
 
 		#Plot features with PCA
@@ -154,6 +155,9 @@ def constraints_no_pca(cmd_args,db_name="data/fisher/constraints_combine.sqlite"
 		var_db = db.query('SELECT "{0}-{0}",bins,feature_label FROM pcov_noise'.format(parameter))
 		var_feature_tomo,nc,label = var_db.query("feature_label=='{0}'".format(feature+"_pca")).tail(1).values.flat
 		ax.bar(5,np.sqrt(var_feature_tomo),width=2,color=base_color)
+
+		#Put a percent value on the last bar of the graph
+		ax.text(5.5,np.sqrt(var_highest_z),r"$-{0}\%$".format(int(100*(np.sqrt(var_highest_z/var_feature_tomo)-1))),fontsize=fontsize)
 
 	#Axes labels
 	xticks = np.arange(len(var_feature)+1)+0.5
@@ -327,18 +331,19 @@ method = dict()
 
 method["1"] = design
 method["2"] = galdistr
-method["3"] = scibook_photo
 
-method["4a"] = pca_components_power_spectrum
-method["4b"] = pca_components_peaks
-method["4c"] = pca_components_moments
+method["3a"] = pca_components_power_spectrum
+method["3b"] = pca_components_peaks
+method["3c"] = pca_components_moments
 
-method["5a"] = constraints_no_pca_power
-method["5b"] = constraints_no_pca_peaks
-method["5c"] = constraints_no_pca_moments
+method["4a"] = constraints_no_pca_power
+method["4b"] = constraints_no_pca_peaks
+method["4c"] = constraints_no_pca_moments
 
-method["6"] = parameter_constraints
-method["7"] = photoz_bias
+method["5"] = parameter_constraints
+method["6"] = photoz_bias
+
+method["x"] = scibook_photo
 
 #Main
 def main():

### 2016-04-15 photoz_paper/paper.tex
update figure 4
incorporated Morgan edits

@@
 \begin{abstract}
-Weak Gravitational Lensing is becoming a popular technique to constrain cosmological parameters, such as the Dark Energy equation of state $w$.
+Weak gravitational lensing is becoming a mature technique to constrain cosmological parameters, such as the dark energy equation of state $w$.
 When analyzing galaxy surveys, redshift information has proven to be a valuable addition to angular shear correlations.
 We forecast parameter constraints on the triplet $(\Omega_m,w,\sigma_8)$ for a LSST like galaxy photometric survey, using tomography of the shear-shear power spectrum, convergence peak counts and higher convergence moments.
-We find that most the cosmological information is contained in the highest redshift galaxies, with redshift tomography further improving the $w$ constraints by only a few $10\%$.
-We also find that the addition of peak and counts to the power spectrum can significantly improve the constraints on the $(\Omega_m,w)$ doublet.
+We find that the addition of peak counts and moments to the power spectrum can significantly improve the constraints on the $(\Omega_m,w)$ doublet.
+We also find that most the cosmological information is contained in the highest redshift galaxies, with redshift tomography further improving the $w$ constraints by only 15\% to 30\%.
 We evaluate the effect of uncorrected photometric redshift systematics on parameter constraints.
@@
 
-\keywords{Weak Gravitational Lensing --- Simulations --- Systematic effects: photometry --- Methods: numerical, statistical}
+\keywords{Weak gravitational lensing --- Simulations --- Systematic effects: photometry --- Methods: numerical, statistical}
 \pacs{98.80.-k, 95.36.+x, 95.30.Sf, 98.62.Sb}
@@
 %
-Weak Gravitational Lensing is a promising technique to probe the Large Scale Structure of the universe in which the tracers are unbiased \citep{wlreview}.
-This technique has the potential of improving significantly the constraints on the Dark Energy equation of state $w$ because it is most sensitive to the matter density fluctuations at the non--linear stage.
+Weak gravitational lensing is a promising technique to probe the large scale structure of the universe in which the tracers are unbiased \citep{wlreview}.
+This technique has the potential of improving significantly the constraints on the dark energy equation of state $w$ because it is most sensitive to the matter density fluctuations at the non--linear stage.
 Cosmology inferences from Weak Lensing observations have been produced for past (CFHTLenS \citep{cfht1}) and current (DES \citep{DES}) surveys, and are being planned for future experiments as well (LSST \citep{LSST}, WFIRST \citep{WFIRST}, Euclid \citep{Euclid}).
@@
 \label{sec:shearsim}
-We review the procedure used for generating mock shear catalogs.
+We review the procedure used for generating simulated shear catalogs.
 We consider a fiducial flat $\Lambda$CDM universe with $(h,\Omega_m,\Omega_\Lambda,\Omega_b,w,\sigma_8,n_s)=(0.72,0.26,0.74,0.046,-1,0.8,0.96)$.
@@
 To accomplish this task, we make use of the \ttt{LensTools} \citep{LensTools-ASCL,LensTools-paper} implementation of the multi--lens--plane algorithm.
-An observed galaxy position $\pmb{\theta}$ on the sky today corresponds to a real galaxy angular position $\pmb{\beta}(\pmb{\theta},z_s)$, which can be calculated using the \ttt{LensTools} pipeline by solving the lensing ODE up to redshift $z_s$.
+An observed galaxy position $\pmb{\theta}$ on the sky today corresponds to a real galaxy angular position $\pmb{\beta}(\pmb{\theta},z_s)$, which can be calculated using the \ttt{LensTools} pipeline by solving the lensing ordinary differential equations up to redshift $z_s$.
 The Jacobian of $\pmb{\beta}(\pmb{\theta},z_s)$ is a $2\times 2$ matrix that contains information about the cosmic shear field at $\pmb{\theta}$ integrated along the line of sight.
@@
 %
-The quantities that appear in equation (\ref{meth:sheareqn}) are the convergence $\kappa$, which is the source magnification due to lensing, and the cosmic shear $\pmb{\gamma}$, which is a measurement of the source ellipticity due to lensing from Large Scale Structure, assuming the non lensed shape is a circle.
+The quantities that appear in equation (\ref{meth:sheareqn}) are the convergence $\kappa$, which is the source magnification due to lensing, and the cosmic shear $\pmb{\gamma}$, which is a measurement of the source ellipticity due to lensing from large scale structure, assuming the non lensed shape is a circle.
 We simulate $N_g = 10^6$ random galaxy positions $\{\pmb{\theta}_g\}$ distributed uniformly in a field of view of size $\theta_{\rm FOV}^2=(3.5{\rm deg})^2$, which correspond to a galaxy angular density of $n_g=22\,\rm{arcmin}^{-2}$.
@@
 For each galaxy we compute the cosmic shear at $\pmb{\theta}_g$ using equation (\ref{meth:sheareqn}), producing a shear catalog $\{\pmb{\gamma}_g\}$.
-Different random realizations of a shear catalog $\{\pmb{\gamma}_g\}_r$ can be obtained rotating and periodically shifting the Large Scale Structure in the $N$--body snapshots according to the procedure explained in \citep{PetriVariance}.
+Different random realizations of a shear catalog $\{\pmb{\gamma}_g\}_r$ can be obtained rotating and periodically shifting the large scale structure in the $N$--body snapshots according to the procedure explained in \citep{PetriVariance}.
 We produce $N_r=16000$ pseudo--independent realizations of the shear catalog $\{\pmb{\gamma}_g\}$.
@@
 In this case the randomization procedure is based on 5 independent $N$--body simulations, and the same number $N_r=16000$ of pseudo--independent catalog realizations is produced.
-This additional simulation set serves two purposes: it provides an independent dataset from which to measure covariance matrices and it provides a way to construct mock observations that are independent on the simulations on which the cosmological forward model is trained.
+This additional simulation set serves two purposes: it provides an independent dataset from which to measure covariance matrices and it provides a way to construct simulated observations that are independent of the simulations on which the cosmological forward model is trained.
 For the fiducial dataset we chose to base the shear randomization procedure on 5 independent $N$--body simulations to ensure the independence of the $N_r$ realizations for the purpose of estimating covariance matrices.
@@
 
-The measured galaxy ellipticity $\pmb{\epsilon}$ is an estimate of the cosmic shear $\pmb{\gamma}$ due to Large Scale Structure if the non--lensed galaxy shape is a circle.
-If this assumption is relaxed, the measured galaxy ellipticity $\pmb{\epsilon}_{\rm m}$ can be modeled as a cosmic shear term plus a noise term \citep{wlreview}
+The measured galaxy ellipticity $\pmb{\epsilon}$ is an estimate of the cosmic shear $\pmb{\gamma}$ due to large scale structure if the non--lensed galaxy shape is a circle.
+Because the galaxies have intrinsic non circular shapes, the measured galaxy ellipticity $\pmb{\epsilon}_{\rm m}$ is the sum of a cosmic shear term and the intrinsic ellipticity (galaxy shape noise) \citep{wlreview}
 \begin{equation}
@@
 
+The study of photometric redshift errors is an active subject of research, and includes investigation of techniques such as spectroscopic calibration, catastrophic errors and cross-correlation techniques that we do not explore in this work (see for example \citep{HuTomo} for a more throughout discussion).
 We model effect of photo-$z$ errors as a constant bias term $b_{\rm ph}(z_s)$ plus a random Gaussian component with variance $\sigma_{\rm ph}(z_s)$
@@
 
-We generate mock observations by applying an independent random realization of the photo-$z$ correction (\ref{meth:photoz-correction}) to each catalog realization in the fiducial cosmology $\bb{p}_0$ and by re--binning the galaxies according to their photometric redshifts $z_p$.
-In the remainder of the paper we use the following notation: we indicate a shear realization $r$ in cosmology $\bb{p}$ with shape noise added as $\h{\pmb{\gamma}}_r(\pmb{\theta}_g,z_g;\bb{p})$, and we indicate a mock observation as $\h{\pmb{\gamma}}_{\rm obs}(\pmb{\theta}_g,z_g)$.
+We generate simulated observations by applying an independent random realization of the photo-$z$ correction (\ref{meth:photoz-correction}) to each catalog realization in the fiducial cosmology $\bb{p}_0$ and by re--binning the galaxies according to their photometric redshifts $z_p$.
+In the remainder of the paper we use the following notation: we indicate a shear realization $r$ in cosmology $\bb{p}$ with shape noise added as $\h{\pmb{\gamma}}_r(\pmb{\theta}_g,z_g;\bb{p})$, and we indicate a simulated observation as $\h{\pmb{\gamma}}_{\rm obs}(\pmb{\theta}_g,z_g)$.
 
@@
 \subsection{Convergence reconstruction}
-In this paragraph we describe the procedure we used to construct convergence maps $\kappa$ from the simulated shear catalogs $\pmb{\gamma}$.
+In this section we describe the procedure we use to construct convergence maps $\kappa$ from the simulated shear catalogs $\pmb{\gamma}$.
 We consider a two dimensional square pixel grid of area $\theta_{\rm FOV}^2$ and with 512 pixel per side.
@@
 Inverting the Fourier Transform yields the pixelized map $\kappa(\pmb{\theta}_p,\bar{z}_b)$.
-We apply this procedure to both the shear realizations $\h{\pmb{\gamma}}_r(\pmb{\theta}_g,z_g;\bb{p})$ and the mock observations $\h{\pmb{\gamma}}_{\rm obs}(\pmb{\theta}_g,z_g)$, yielding convergence realizations $\h{\kappa}_r(\pmb{\theta}_p,\bar{z}_b;\bb{p})$ and mock convergence observations $\h{\kappa}_{\rm obs}(\pmb{\theta}_p,\bar{z}_b)$.
+We apply this procedure to both the shear realizations $\h{\pmb{\gamma}}_r(\pmb{\theta}_g,z_g;\bb{p})$ and the simulated observations $\h{\pmb{\gamma}}_{\rm obs}(\pmb{\theta}_g,z_g)$, yielding convergence realizations $\h{\kappa}_r(\pmb{\theta}_p,\bar{z}_b;\bb{p})$ and simulated convergence observations $\h{\kappa}_{\rm obs}(\pmb{\theta}_p,\bar{z}_b)$.
 
@@
 In the definition of the peak counts and convergence moments we omitted the redshift index $\bar{z}_b$ for notational simplicity.
-In the next paragraph we describe the statistical methods we use to infer cosmological parameter estimates $\bbh{p}$ from mock observations $\h{\kappa}_{\rm obs}(\pmb{\theta}_p,\bar{z}_b)$ using the summary statistics $P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})$, $n_{\rm pk}(\nu,\bar{z}_b)$, $\pmb{\mu}(\bar{z}_b)$.
+In the next paragraph we describe the statistical methods we use to infer cosmological parameter estimates $\bbh{p}$ from simulated observations $\h{\kappa}_{\rm obs}(\pmb{\theta}_p,\bar{z}_b)$ using the summary statistics $P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})$, $n_{\rm pk}(\nu,\bar{z}_b)$, $\pmb{\mu}(\bar{z}_b)$.
 
@@
 Both $\bb{d}(\bb{p}),\bbh{d}_r$ are measured taking galaxy shape noise into account.
-We further label $\bbh{d}_{\rm obs}$ the summary statistic measured in a mock observation in which $\kappa$ has been measured taking photo-$z$ errors into account.
+We further label $\bbh{d}_{\rm obs}$ the summary statistic measured in a simulated observation in which $\kappa$ has been measured taking photo-$z$ errors into account.
 $\bbh{d}_{\rm obs}$ is measured averaging a random sample of $N_{\rm FOV}=1600$ realizations of the fiducial cosmology with photo-$z$ errors added.
@@
 %
-The $1\sigma$ square parameter errors $\Delta \bbh{p}^2$ are the diagonal entries of $\bbh{\Sigma}$.
-The parameter covariance estimator (\ref{meth:parcovestimator}) is the same that one gets adopting a Fisher Matrix formalism for parameter forecasts (see \citep{astroMLText} for a possible reference).
+The square of the $1\sigma$ parameter errors $\Delta \bbh{p}^2$ are the diagonal entries of $\bbh{\Sigma}$.
+The parameter covariance estimator (\ref{meth:parcovestimator}) is the same that one gets adopting a Fisher Matrix formalism for parameter forecasts (see \citep{astroMLText}).
 
@@
 where $\bb{\Sigma}$ is the asymptotic covariance one obtains with an infinite number of realizations and $N_p$ is the number of parameters we are estimating, in this case 3.
-The scatter of the parameter estimates (\ref{meth:parestimate}) on the other hand scales as
+The scatter of the parameter estimates (\ref{meth:parestimate}) on the other hand scales as \citep{Taylor14}
 \begin{equation}
@@
 This means that the parameter error bar estimate (\ref{meth:covdegradation}) is too conservative if $N_b/N_r$ is of order unity.
-This could be likely the case in the analysis we are carrying because of the inclusion of tomography information.
+This could be likely the case in our analysis because of the inclusion of tomography information.
 In order to avoid these error degradation issues, we apply dimensional reduction techniques to the summary statistics we are considering.
@@
 
-In this section we illustrate the main results of this work.
+In this section we present the main results of this work.
 Figure \ref{fig:pcacomponents} shows the robustness of the dimensionality reduction technique we adopted.
@@
 To measure the power spectrum we chose 15 uniformly spaced multipole bands between $(\ell_{\rm min},\ell_{\rm max})=(200,2000)$.
-Because, of the combinations $(\bar{z}_b,\bar{z}_{b'})$, only 15 of them (5 diagonal + 10 off-diagonal) are independent, this leads to a total of $N_b=15\times 15=225$ power spectrum measurement bands, including cross redshift information.
+There are only 15 $(\bar{z}_b,\bar{z}_{b'})$ independent combinations (5 diagonal + 10 off-diagonal), which leads to a total of $N_b=15\times 15=225$ power spectrum measurement bands, including cross redshift information.
 We bin the convergence peak counts in 30 uniformly spaced $\nu$ bins between $(\nu_{\rm min},\nu_{\rm max})=(-2,7)$, for a total of $N_b=30\times5=150$ measurement bands, including redshift information.
@@
 Figure \ref{fig:photozbias} shows the effect of ignoring photo-$z$ errors on parameter constraints.
-To evaluate this effect we construct different mock observations, with and without photo-$z$ effects, and compare the results of the parameter fit according to equation (\ref{meth:parestimate}).
-Using our simulation suite, we construct 20 mock observations: the summary statistic in each observation is calculated by taking the mean of a random sample of $N_{\rm FOV}$ realizations of the summary statistic in the fiducial cosmology (randomly chosen among the ensemble of $N_r=16000$ that are available in the ensemble).
-The estimated covariance matrix $\bbh{C}$ is scaled by a factor $N_{\rm FOV}$ to take into account the construction process of the mock observations.
+To evaluate this effect we construct different simulated observations, with and without photo-$z$ effects, and compare the results of the parameter fit according to equation (\ref{meth:parestimate}).
+Using our simulation suite, we construct 20 simulated observations: the summary statistic in each observation is calculated by taking the mean of a random sample of $N_{\rm FOV}$ realizations of the summary statistic in the fiducial cosmology (randomly chosen among the ensemble of $N_r=16000$ that are available in the ensemble).
+The estimated covariance matrix $\bbh{C}$ is scaled by a factor $N_{\rm FOV}$ to take into account the construction process of the simulated observations.
 This procedure allows to forecast the results an LSST-like survey would obtain.
@@
 \includegraphics[scale=0.3]{Figures/photoz_bias_Om-w.eps}
-\caption{Distribution of parameter estimates in the $(\Omega_m,w)$ parameter space using the power spectrum (red), peak counts (green) and moments (blue) to fit 20 LSST-like mock observations.
+\caption{Distribution of parameter estimates in the $(\Omega_m,w)$ parameter space using the power spectrum (red), peak counts (green) and moments (blue) to fit 20 LSST-like simulated observations.
 The parameter deviations $(\delta\Omega_m,\delta w)$ are obtained comparing parameter estimates according to equation (\ref{meth:parestimate}) with and without photo-$z$ errors.
-The colored squares and the ellipses correspond to respectively to the mean and $1\sigma$ level of the $(\delta\Omega_m,\delta w)$ distribution in the pessimistic systematics case, assuming this distribution is Gaussian.}
+The colored squares and the ellipses correspond to respectively to the mean and $1\sigma$ level of the $(\delta\Omega_m,\delta w)$ distribution, assuming the latter is Gaussian.}
 \label{fig:photozbias}
@@
 Figure \ref{fig:nopca} clearly that most of the cosmological information is concentrated in the last redshift bin.
-The use of redshift tomography only tightens the constraints by a few $10\%$.
+The use of redshift tomography tightens the constraints by approximately 33\% for the power spectrum, 16\% for the peaks and 25\% for the moments.
 

### 2016-04-15 photoz_paper/Figures/generate.py

@@ -157,7 +157,7 @@ def constraints_no_pca(cmd_args,db_name="data/fisher/constraints_combine.sqlite"
 		ax.bar(5,np.sqrt(var_feature_tomo),width=2,color=base_color)
 
 		#Put a percent value on the last bar of the graph
-		ax.text(5.5,np.sqrt(var_highest_z),r"$-{0}\%$".format(int(100*(np.sqrt(var_highest_z/var_feature_tomo)-1))),fontsize=fontsize)
+		#ax.text(5.5,np.sqrt(var_highest_z),r"$-{0}\%$".format(int(100*(np.sqrt(var_highest_z/var_feature_tomo)-1))),fontsize=fontsize)
 
 	#Axes labels
 	xticks = np.arange(len(var_feature)+1)+0.5

### 2016-04-15 photoz_paper/Figures/generate.py
generate biasVsigma figure

@@ -324,6 +324,86 @@ def photoz_bias(cmd_args,db_name="data/fisher/constraints_photoz.sqlite",paramet
 
 ###################################################################################################
 ###################################################################################################
+
+def bias_vs_sigma(cmd_args,db_name="data/fisher/constraints_photoz.sqlite",parameters=["Om","w"],features_to_show=["ps70","pk70","mu40"],fontsize=22):
+
+	#Init figure
+	fig,ax = plt.subplots()
+	ellipses = list()
+	labels = list()
+
+	#Cycle over features
+	for f in features_to_show:
+
+		#Feature properties
+		feature_label = feature_properties[f]["name"]
+		nbins = feature_properties[f]["pca_components"]
+		color = feature_properties[f]["color"]
+		plot_label = feature_properties[f]["label"]
+		marker = feature_properties[f]["marker"]
+
+		############
+		#No photo-z#
+		############
+
+		with FisherDatabase(db_name) as db:
+			pfit = db.query_parameter_fit(feature_label,table_name="mocks_without_photoz",parameters=parameters).query("bins=={0}".format(nbins))
+			p1f,p2f = [ pfit[parameters[n]+"_fit"].values for n in [0,1] ]
+
+		###########################
+		#With photo-z: (bias only)#
+		###########################
+
+		with FisherDatabase(db_name) as db:
+			pfit = db.query_parameter_fit(feature_label,table_name="mocks_photoz_requirement_bias",parameters=parameters).query("bins=={0}".format(nbins))
+			p1,p2 = [ pfit[parameters[n]+"_fit"].values for n in [0,1] ]
+			ax.scatter((p1-p1f).mean(),(p2-p2f).mean(),color=color,marker="s",s=60)
+
+			#Draw an error ellipse around the mean bias
+			center = ((p1-p1f).mean(),(p2-p2f).mean())
+			pcov = np.cov([p1-p1f,p2-p2f]) 
+			ellipses.append(FisherAnalysis.ellipse(center,pcov,p_value=0.677,fill=False,edgecolor=color,linestyle="-"))
+			labels.append(feature_properties[f]["label"] + r"$({\rm bias})$")
+			ax.add_artist(ellipses[-1])
+
+		############################
+		#With photo-z: (sigma only)#
+		############################
+
+		with FisherDatabase(db_name) as db:
[…]

### 2016-04-18 photoz_paper/paper.tex
added table with constraints

@@
 We find that the addition of peak counts and moments to the power spectrum can significantly improve the constraints on the $(\Omega_m,w)$ doublet.
-We also find that most the cosmological information is contained in the highest redshift galaxies, with redshift tomography further improving the $w$ constraints by only 15\% to 30\%.
+We also find that most the cosmological information on $w$ is contained in the highest redshift galaxies, with redshift tomography further improving the constraints by only 15\% to 30\%.
+The improvement obtained with redshift tomography is much bigger when considering the constraints on $(\Omega_m,w)$ using the convergence power spectrum.
 We evaluate the effect of uncorrected photometric redshift systematics on parameter constraints.
@@
 We also show the improvements on the confidence contours when combining different summary statistics after the corresponding dimensionality reductions have been performed.
+The forecast constraints on the $(\Omega_m,w,\sigma_8)$ parameter space for a variety of summary statistics are summarized in Table \ref{tbl:constraints}.
 
@@
 \end{figure}
+
+\begin{table*}
+\begin{tabular}{c|c|c|c|c|}
+\toprule
+                        \textbf{Statistic} & $\Delta \Omega_m$ & $\Delta w$ & $\Delta \sigma_8$ & $\sqrt[3]{\rm Volume}$ $(\Omega_m,w,\sigma_8)$ \\ \hline \hline
+\midrule
+     Power spectrum ($\bar{z}_5$) &            0.0222 &     0.0286 &            0.0298 &                                       0.0087 \\
+      Power spectrum (tomography) &            0.0038 &     0.0213 &            0.0060 &                                       0.0042 \\
+              Peaks ($\bar{z}_5$) &            0.0049 &     0.0316 &            0.0050 &                                       0.0046 \\
+               Peaks (tomography) &            0.0042 &     0.0271 &            0.0043 &                                       0.0050 \\
+            Moments ($\bar{z}_5$) &            0.0027 &     0.0276 &            0.0026 &                                       0.0034 \\
+             Moments (tomography) &            0.0020 &     0.0214 &            0.0020 &                                       0.0028 \\ \hline \hline
+           Power spectrum + peaks &            0.0021 &     0.0153 &            0.0026 &                                       0.0030 \\ 
+         Power spectrum + moments &            0.0016 &     0.0150 &            0.0019 &                                       0.0025 \\
+ Power spectrum + peaks + moments &            0.0015 &     0.0121 &            0.0018 &                                       0.0023 \\ \hline
+\bottomrule
+\end{tabular}
+\caption{Constraints on the $(\Omega_m,w,\sigma_8)$ parameter triplet using different summary statistics and redshift information.
+Each column $(\Delta \Omega_m,\Delta w,\Delta \sigma_8)$ contains the 1 $\sigma$ constraints on a particular parameter, marginalized over the other two.
+The last volume contains the volume of the $\sigma$ ellipsoid in $(\Omega_m,w,\sigma_8)$ space, calculated as $\sqrt{\det \bbh{\Sigma}}$.}
+\label{tbl:constraints}
+\end{table*}
 
@@
 Figure \ref{fig:nopca} clearly that most of the cosmological information is concentrated in the last redshift bin.
-The use of redshift tomography tightens the constraints by approximately 33\% for the power spectrum, 16\% for the peaks and 25\% for the moments.
+The use of redshift tomography tightens the $w$ constraints by approximately 33\% for the power spectrum, 16\% for the peaks and 25\% for the moments.
+Redshift tomography seems to play a vital role when constraining the $(\Omega_m,\sigma_8)$ doublet using the convergence power spectrum.
 
@@
 Nevertheless we find that the number of required components $N_c$ is significantly smaller than the full summary statistic space dimensionality before performing PCA.
-	\item Most of the cosmological information is contained in high redshift galaxies, with tomography improving $w$ constraints by only a few $10\%$.   
+	\item Most of the cosmological information on $w$ is contained in high redshift galaxies, with tomography improving constraints by only a few $10\%$.
+The advantage using tomography is much bigger when constraining $(\Omega_m,\sigma_8)$ using the convergence power spectrum.
 	\item Peak counts and moments can significantly improve $(\Omega_m,w)$ parameter constraints when used in combination with the power spectrum.

### 2016-04-18 photoz_paper/Figures/generate.py

@@ -3,7 +3,10 @@
 import sys,os,argparse
 sys.modules["mpi4py"] = None
 
+import itertools
+
 import numpy as np
+import pandas as pd
 import matplotlib.pyplot as plt
 
 from lenstools.catalog.shear import Catalog
@@ -402,6 +405,68 @@ def bias_vs_sigma(cmd_args,db_name="data/fisher/constraints_photoz.sqlite",param
 	#Save figure
 	fig.savefig("bias_vs_sigma_{0}.{1}".format("-".join(parameters),cmd_args.type))
 
+
+###################################################################################################
+###################################################################################################
+
+rows = {
+
+"ps5" : {"name" : "power_spectrum_pca_z4" , "table_name" : "pcov_noise" ,"bins" : 14 , "label" : r"Power spectrum ($\bar{z}_5$)"},
+"ps-tomo" : {"name" : "power_spectrum_pca" , "table_name" : "pcov_noise" , "bins" : 70 , "label" : "Power spectrum (tomography)"},
+"peaks5" : {"name" : "peaks_pca_z4" , "table_name" : "pcov_noise" , "bins" : 27 , "label" : r"Peaks ($\bar{z}_5$)"},
+"peaks-tomo" : {"name" : "peaks_pca" , "table_name" : "pcov_noise" , "bins" : 70 , "label" : "Peaks (tomography)"},
+"moments5" : {"name" : "moments_pca_z4" , "table_name" : "pcov_noise" , "bins" : 9 , "label" : r"Moments ($\bar{z}_5$)"},
+"moments-tomo" : {"name" : "moments_pca" , "table_name" : "pcov_noise" , "bins" : 40 , "label" : "Moments (tomography)"},
+
+"ps+pk" : {"name" : "power_spectrum+peaks" , "table_name" : "pcov_noise_combine" , "bins" : 70 , "label" : "Power spectrum + peaks"},
+"ps+mu" : {"name" : "power_spectrum+moments" , "table_name" : "pcov_noise_combine" , "bins" : 60 , "label" : "Power spectrum + moments"},
+"ps+pk+mu" : {"name" : "power_spectrum+peaks+moments" , "table_name" : "pcov_noise_combine" , "bins" : 100 , "label" : "Power spectrum + peaks + moments"} 
+
+}
+
+columns = {
+	
[…]

### 2016-04-18 photoz_paper/paper.tex
fix typo

@@
 We also find that most the cosmological information on $w$ is contained in the highest redshift galaxies, with redshift tomography further improving the constraints by only 15\% to 30\%.
-The improvement obtained with redshift tomography is much bigger when considering the constraints on $(\Omega_m,w)$ using the convergence power spectrum.
+The improvement obtained with redshift tomography is much bigger when considering the constraints on $(\Omega_m,\sigma_8)$ using the convergence power spectrum.
 We evaluate the effect of uncorrected photometric redshift systematics on parameter constraints.

### 2016-04-19 code/library/featureDB.py
fix bug when no  fiducial model present

@@ -560,7 +560,12 @@ class LSSTSimulationBatch(SimulationBatch):
 
 		super(LSSTSimulationBatch,self).__init__(*args,**kwargs)
 		self._models = self.models
-		self._fiducial = [ m for m in self._models if (m.cosmology.Om0==0.26 and m.cosmology.w0==-1 and m.cosmology.sigma8==0.8) ][0]
+		
+		try:
+			self._fiducial = [ m for m in self._models if (m.cosmology.Om0==0.26 and m.cosmology.w0==-1 and m.cosmology.sigma8==0.8) ][0]
+		except IndexError:
+			self._fiducial = None
+			
 		self._non_fiducial = [ m for m in self.models if (m.cosmology.Om0!=0.26 or m.cosmology.w0!=-1 or m.cosmology.sigma8!=0.8) ]
 
 	@property
@@ -569,6 +574,8 @@ class LSSTSimulationBatch(SimulationBatch):
 
 	@property 
 	def fiducial_cosmo_id(self):
+		if self.fiducial is None:
+			return None
 		return self.fiducial.cosmo_id
 
 	@property

### 2016-04-19 code/constraints/nicaea_constraints.py
first implementation of tomographic constraints using Nicaea

@@ -1,0 +1,108 @@
+#!/usr/bin/env python
+from __future__ import division
+import sys
+sys.modules["mpi4py"] = None
+
+import itertools
+import numpy as np
+import astropy.units as u
+import pandas as pd
+
+from lenstools.statistics.ensemble import Ensemble
+from lenstools.statistics.constraints import FisherAnalysis
+from lenstools.simulations.nicaea import Nicaea
+
+################################
+#######Tunable options##########
+################################
+
+options = {
+
+#Multipoles
+"multipoles" : np.linspace(150.,2000.,15) ,
+
+#Redshift distribution parameters
+"zbins" : [(0.0052829915857917076, 0.46370802037163456), 
+(0.46370802037163456, 0.68921284184762954),
+(0.68921284184762954, 0.93608623056054063),
+(0.93608623056054063, 1.2872107430836479),
+(1.2872107430836479, 2.9998163872653354)] ,
+
+"alpha_p" : 2,
+"beta_p" : 1,
+"z0" : 0.3,
+
+#Cosmological parameters
+"fiducial" : {"Om0" : 0.26, "w0" : -1. , "sigma8" : 0.8},
+"derivative_percentage" : 0.01 ,
+
+#Shape noise
+"add_shape_noise" : True,
+"ngal" : 22.*(u.arcmin**-2),
+
+#Sky fraction
+"fsky" : 0.47
+
+}
+
+
+##################################################################################################################################
+
+#Build FisherAnalysis instance from predicted power spectrum with NICAEA
+def predict_power(options):
+
+	#From options
+	multipoles = options["multipoles"]
+	zbins = options["zbins"]
+	alpha_p = options["alpha_p"]
+	beta_p = options["beta_p"]
+	z0 = options["z0"]
+	fiducial = options["fiducial"]
+	derivative_percentage = options["derivative_percentage"]
+
+	#Pack the zbins and distribution parameters into lists 
+	distribution = ["ludo"]*len(zbins)
+	distribution_parameters = [ [zmin,zmax,alpha_p,beta_p,z0] for (zmin,zmax) in zbins]
+
+	#Variations of cosmological parameters
+	cosmo_parameters = dict((k,[fiducial[k]]*(len(fiducial)+1)) for k in fiducial)
+	for n,k in enumerate(fiducial):
[…]

### 2016-04-19 code/constraints/nicaea_constraints.py
single redshift constraints with Nicaea

@@ -35,6 +35,7 @@ options = {
 #Cosmological parameters
 "fiducial" : {"Om0" : 0.26, "w0" : -1. , "sigma8" : 0.8},
 "derivative_percentage" : 0.01 ,
+"parameters_rename" : {"Om0" : "Om" , "w0" : "w" , "sigma8" : "sigma8"} ,
 
 #Shape noise
 "add_shape_noise" : True,
@@ -97,12 +98,37 @@ def predict_power(options):
 	predicted_power.add_name("power_kk")
 	fisher = FisherAnalysis.from_features(predicted_power,cosmo_parameters)
 
-	#Calculate the Pkk covariance matrix assuming it is diagonal
-	fsky = options["fsky"]
-	diagonal_covariance_matrix = pd.Series(np.zeros(fisher["power_kk"].shape[1]),index=fisher[["power_kk"]].columns)
-	for n,l in enumerate(multipoles):
-		columns_to_fill = [ ("power_kk","l{0}-z{1}-z{2}".format(n,z1,z2)) for (z1,z2) in redshift_indices ] 
-		diagonal_covariance_matrix[columns_to_fill] = (fisher[columns_to_fill].iloc[fisher._fiducial])**2 / (fsky*(l+0.5))
-
 	#Return
-	return fisher,diagonal_covariance_matrix
+	return fisher
+
+
+#Calculate the single redshift constraints
+def singleZ_constraints(fisher,options):
+
+	#Multipole spacing
+	dl_bin = options["multipoles"][1] - options["multipoles"][0]
+
+	#Rows
+	rows = list()
+
+	#Cycle over redshift bins
+	for nz,zb in enumerate(options["zbins"]):
+
+		#Select the appropriate columns from the FisherAnalysis instance
+		fisher_singleZ = fisher.features({ "power_kk" : [ "l{0}-z{1}-z{1}".format(nl,nz) for nl in range(len(options["multipoles"])) ] })
+
+		#Estimate the covariance matrix and errorbars
+		singleZ_covariance = (fisher_singleZ["power_kk"].iloc[fisher._fiducial]**2) / (options["fsky"]*dl_bin*(0.5+options["multipoles"]))
+		parameter_covariance = fisher_singleZ.parameter_covariance(singleZ_covariance)
+
+		#Rename the columns for convenience
+		new_column_names = [ options["parameters_rename"][k] for k in parameter_covariance.columns ]
+
[…]

### 2016-04-20 photoz_paper/Figures/generate.py
generate figure nicaea vs simulations

@@ -188,6 +188,42 @@ def constraints_no_pca_moments(cmd_args):
 ###################################################################################################
 ###################################################################################################
 
+#Comparison with NICAEA
+def sims_vs_nicaea(cmd_args,db_name="data/fisher/constraints_combine.sqlite",feature="power_spectrum",parameter="w",ylim=None,fontsize=22):
+
+	#Set up plot
+	fig,ax = plt.subplots()
+
+	#Axes bounds
+	if ylim is not None:
+		ax.set_ylim(*ylim)
+
+	#Plot the power spectrum 
+	with FisherDatabase(db_name) as db:
+		
+		#Query parameter variance obtained with the simulations
+		var_db = db.query('SELECT "{0}-{0}",feature_label FROM pcov_noise_no_pca'.format(parameter))
+		var_feature = var_db[var_db["feature_label"].str.contains(feature)]["{0}-{0}".format(parameter)].values
+		ax.bar(range(len(var_feature)),np.sqrt(var_feature),width=1,color="black",label=r"${\rm Simulations}$",alpha=0.3)
+
+		#Query parameter variance obtained with NICAEA
+		var_db = db.query('SELECT "{0}-{0}",feature_label FROM pcov_noise_nicaea'.format(parameter))
+		var_feature = var_db[var_db["feature_label"].str.contains(feature)]["{0}-{0}".format(parameter)].values
+		ax.bar(range(len(var_feature)),np.sqrt(var_feature),width=1,fill=False,edgecolor="red",label=r"${\rm NICAEA}$")
+
+	#Axes labels
+	xticks = np.arange(len(var_feature))+0.5
+	ax.set_xticks(xticks)
+	ax.set_xticklabels([r"$\bar{z}_" + str(n+1) + r"$" for n in range(len(var_feature))],fontsize=fontsize)
+	ax.set_ylabel(r"$\Delta$"+par2label[parameter],fontsize=fontsize)
+	ax.legend(prop={"size":25})
+
+	#Save the figure
+	fig.savefig("sims_vs_nicaea_{0}.{1}".format(parameter,cmd_args.type))
+
+###################################################################################################
+###################################################################################################
+
 def pca_components(cmd_args,db_name="data/fisher/constraints_combine.sqlite",feature_label="power_spectrum_pca",parameter="w",fontsize=22):
 
 	#Use automatic plot routine
[…]

### 2016-04-20 photoz_paper/Figures/generate.py
update sims vs nicaea figure

@@ -206,15 +206,25 @@ def sims_vs_nicaea(cmd_args,db_name="data/fisher/constraints_combine.sqlite",fea
 		var_feature = var_db[var_db["feature_label"].str.contains(feature)]["{0}-{0}".format(parameter)].values
 		ax.bar(range(len(var_feature)),np.sqrt(var_feature),width=1,color="black",label=r"${\rm Simulations}$",alpha=0.3)
 
+		#Overlay the results obtained with PCA
+		var_db = db.query('SELECT "{0}-{0}",feature_label FROM pcov_noise WHERE bins=10'.format(parameter))
+		var_feature = var_db[var_db["feature_label"].str.contains(feature+"_pca_z")]["{0}-{0}".format(parameter)].values
+		ax.bar(range(len(var_feature)),np.sqrt(var_feature),width=1,fill=False,edgecolor="green",label=r"${\rm Simulations(PCA)}$")
+
+		var_db = db.query('SELECT "{0}-{0}",feature_label FROM pcov_noise WHERE bins=70'.format(parameter))
+		var_feature = var_db[var_db["feature_label"].str.contains(feature+"_pca")]["{0}-{0}".format(parameter)].values
+		ax.bar(5,np.sqrt(var_feature),width=1,fill=False,edgecolor="green")
+
 		#Query parameter variance obtained with NICAEA
 		var_db = db.query('SELECT "{0}-{0}",feature_label FROM pcov_noise_nicaea'.format(parameter))
 		var_feature = var_db[var_db["feature_label"].str.contains(feature)]["{0}-{0}".format(parameter)].values
 		ax.bar(range(len(var_feature)),np.sqrt(var_feature),width=1,fill=False,edgecolor="red",label=r"${\rm NICAEA}$")
 
+
 	#Axes labels
 	xticks = np.arange(len(var_feature))+0.5
 	ax.set_xticks(xticks)
-	ax.set_xticklabels([r"$\bar{z}_" + str(n+1) + r"$" for n in range(len(var_feature))],fontsize=fontsize)
+	ax.set_xticklabels([r"$\bar{z}_" + str(n+1) + r"$" for n in range(len(var_feature)-1)] + [r"${\rm Tomo}$"],fontsize=fontsize)
 	ax.set_ylabel(r"$\Delta$"+par2label[parameter],fontsize=fontsize)
 	ax.legend(prop={"size":25})
 

### 2016-04-20 photoz_paper/paper.tex
updated abstract

--- 2016-04-18 photoz_paper/paper.tex
@@
 
-\title{Cosmology with Weak Lensing photometric surveys: constraints with redshift tomography of non--Gaussian statistics}
+\title{Cosmology with weak lensing photometric surveys: constraints with redshift tomography of non--Gaussian statistics}
 
@@
 \begin{abstract}
-Weak gravitational lensing is becoming a mature technique to constrain cosmological parameters, such as the dark energy equation of state $w$.
+Weak gravitational lensing is becoming a mature technique to constrain cosmological parameters, and future surveys will be able to constrain the dark energy equation of state $w$.
 When analyzing galaxy surveys, redshift information has proven to be a valuable addition to angular shear correlations.
-We forecast parameter constraints on the triplet $(\Omega_m,w,\sigma_8)$ for a LSST like galaxy photometric survey, using tomography of the shear-shear power spectrum, convergence peak counts and higher convergence moments.
+We forecast parameter constraints on the triplet $(\Omega_m,w,\sigma_8)$ for an LSST like galaxy photometric survey, using tomography of the shear-shear power spectrum, convergence peak counts and higher convergence moments.
 We find that the addition of peak counts and moments to the power spectrum can significantly improve the constraints on the $(\Omega_m,w)$ doublet.
-We also find that most the cosmological information on $w$ is contained in the highest redshift galaxies, with redshift tomography further improving the constraints by only 15\% to 30\%.
-The improvement obtained with redshift tomography is much bigger when considering the constraints on $(\Omega_m,w)$ using the convergence power spectrum.
+We also find that most of the cosmological information on $w$ is contained in the highest redshift galaxies, with redshift tomography further improving the constraints by only 15\% to 30\%.
+The improvement obtained with power spectrum tomography is larger for the doublet $(\Omega_m,\sigma_8)$, or which the 1$\sigma$ error bar shrinks by a factor of 5.
 We evaluate the effect of uncorrected photometric redshift systematics on parameter constraints.
-We find that different statistics lead to different bias directions in parameter space, leaving a window open for self--calibration.
+We find that different statistics lead to different bias directions in parameter space, suggesting the possibility of eliminating this bias via self--calibration.
 \end{abstract}

### 2016-04-20 photoz_paper/Figures/generate.py

@@ -206,6 +206,11 @@ def sims_vs_nicaea(cmd_args,db_name="data/fisher/constraints_combine.sqlite",fea
 		var_feature = var_db[var_db["feature_label"].str.contains(feature)]["{0}-{0}".format(parameter)].values
 		ax.bar(range(len(var_feature)),np.sqrt(var_feature),width=1,color="black",label=r"${\rm Simulations}$",alpha=0.3)
 
+		#Overlay the results obtained by zeroing out the multipole-multipole correlations
+		var_db = db.query('SELECT "{0}-{0}",bins,feature_label FROM pcov_noise_ps_block_diagonal'.format(parameter))
+		var_feature = var_db.sort_values("bins")["{0}-{0}".format(parameter)].values
+		ax.bar(range(len(var_feature)),np.sqrt(var_feature),width=1,fill=False,edgecolor="blue",label=r"${\rm Simulations}(C_{l_1\neq l_2}=0)$")
+
 		#Overlay the results obtained with PCA
 		var_db = db.query('SELECT "{0}-{0}",feature_label FROM pcov_noise WHERE bins=10'.format(parameter))
 		var_feature = var_db[var_db["feature_label"].str.contains(feature+"_pca_z")]["{0}-{0}".format(parameter)].values

### 2016-04-20 code/library/driver_mpi.py
possibility of making the covariance block diagonal

@@ -1,3 +1,5 @@
+from __future__ import division
+
 import os
 import argparse,logging
 import itertools
@@ -179,6 +181,22 @@ def split_redshifts(specs,redshift_index=range(5)):
 	#Return to user
 	return splitted_specs
 
+#Make the covariance matrix block diagonal
+def block_mask(Nb,block=15):
+
+	#Safety
+	if Nb%block!=0:
+		raise ValueError("The block size must divide the matrix size exactly")
+
+	step = Nb//block
+
+	#Create the mask
+	mask = np.zeros((Nb,)*2,dtype=np.int8)
+	for n in range(step):
+		mask[n*block:(n+1)*block,n*block:(n+1)*block] = 1
+
+	#Return
+	return mask
 
 ################################################
 #######Cosmological constraints driver##########
@@ -432,6 +450,12 @@ def cosmo_constraints(batch,specs,settings=default_settings):
 			#Compute the feature covariance matrix
 			logdriver.info("Computing the {0}x{0} feature covariance matrix, Nreal={1}, NLSST={2}...".format(covariance_pca.shape[1],specs["realizations_for_covariance"],settings.covariance_to_lsst))
 			feature_covariance = covariance_pca.head(specs["realizations_for_covariance"]).cov() / settings.covariance_to_lsst
+
+			#Reserve the possibility of zeroing out some of the off diagonal elements of the covariance (to make it block diagonal)
+			if "covariance_block_size" in specs:
+				logdriver.info("Making the feature covariance block-diagonal with {0}x{0} sized blocks".format(specs["covariance_block_size"]))
+				mask = block_mask(len(feature_covariance),specs["covariance_block_size"])
+				feature_covariance.values[mask==0] = 0
 
 			#Compute the parameter covariance matrix correcting for the inverse covariance bias
 			logdriver.info("Computing {0}x{0} parameter covariance matrix, Nbins={1}...".format(len(pnames),covariance_pca.shape[1]))

### 2016-04-21 code/library/featureDB.py
query_parameter_covariance returns a SquareMatrix

@@ -7,7 +7,7 @@ import sys,os,re
 from itertools import product
 
 from lenstools.catalog import ShearCatalog
-from lenstools.statistics.ensemble import Ensemble
+from lenstools.statistics.ensemble import Ensemble, SquareMatrix
 from lenstools.statistics.database import Database
 from lenstools.pipeline.simulation import SimulationBatch
 
@@ -425,7 +425,7 @@ class FisherDatabase(Database):
 
 		#Cast the row into a matrix
 		pcov = query_row.values.reshape((len(parameters),)*2)
-		return self._constructor_ensemble(pcov,index=parameters,columns=parameters)
+		return SquareMatrix(pcov,index=parameters,columns=parameters)
 
 	#Retrieve the variance of a single parameter for a single feature_label
 	def query_parameter_simple(self,feature_label,table_name="pcov",parameter="w"):

### 2016-04-22 photoz_paper/paper.tex
added figures/tables with CMB priors

@@
 In the next section we outline the main results of this work.
+
+%%%%%%%%
+
+\subsection{Priors from CMB experiments}
+In this paragraph we describe how we included prior knowledge of cosmological parameters from previous Cosmic Microwave Background (CMB) observations, such as Planck \citep{PlanckCosmo}.
+CMB experiments provide tight constraints on $(\Omega_m,\sigma_8)$, but they are not sensitive to dark energy parameters such as $w$.
+Nevertheless, prior knowledge of $\Omega_m$ and $\sigma_8$ could in principle help in breaking degeneracies between these parameters and $w$ in weak lensing observations.
+The CMB parameter prior probability function can be written as
+\begin{equation}
+-2\log\mathcal{L}_{\rm CMB}(\bb{p}) = (\bb{p} - \bb{p}_0)^T\bb{F}_{\rm CMB}(\bb{p} - \bb{p}_0)
+\end{equation}
+%
+where we assumed that the best fit parameters are the same $\bb{p}_0$ that appear in equation (\ref{meth:linapprox}). 
+Parameter constraints from the Planck CMB experiment are made available to the public via the parameter Markov Chains (MCMC) published on the Planck Legacy Archive \footnote{\url{http://pla.esac.esa.int/pla/}}.
+We can use these MCMC data to estimate the parameter covariance matrix $\bb{\Sigma}_{\rm CMB}$ on the parameter multiplet $(\Omega_m,\Omega_bh^2,\theta_{\rm MC},\tau,w,n_s,\sigma_8)$, marginalized over the Planck nuisance parameters.
+We then compute the parameter prior Fisher matrix $\bb{F}_{\rm CMB} = \bb{\Sigma}_{\rm CMB}^{-1}$.
+Fixing the values of all parameters but $(\Omega_m,w,\sigma_8)$ and applying the prior to the weak lensing parameter likelihood (\ref{meth:paramlikelihood}) is equivalent to taking the $(\Omega_m,w,\sigma_8)$ slice of $\bb{F}_{\rm CMB}$, which we call $\bb{F}_{\rm CMB}^{(\Omega_m,w,\sigma_8)}$, and computing the parameters constraints subject to the CMB prior as
+
+\begin{equation}
+\label{meth:parcovestimator_cmb}
+\bbh{\Sigma}_{\rm lens+CMB} = \left(\bb{M}^T\bbh{\Psi}\bb{M} + \bb{F}_{\rm CMB}^{(\Omega_m,w,\sigma_8)}\right)^{-1}
+\end{equation}
+%
+In the next section we describe the main results of this work.
+
 %%%%%%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Figure \ref{fig:nopca} shows a comparison between the $w$ constraints obtained using single redshift bins, with and without PCA dimensionality reduction, and compares these single redshift constraints with the ones obtained using redshift tomography.
+When we calculate parameter inferences using the convergence power spectrum $P^{\kappa\kappa}$, we can cross check the results obtained with our simulations with the ones obtained with the analytical code NICAEA \citep{Nicaea}.
+This code allows to predict the convergence power spectrum as a function of cosmological parameters $\bb{p}$, for an arbitrary galaxy redshift distribution $n(z)$.
+Parameter inferences can be obtained from the NICAEA predictions for $P^{\kappa\kappa}(\ell,z_i,z_j)$ (where $\{z_i\}$ are the centers of the redshift bins) using equation (\ref{meth:parcovestimator}).
+To proceed in the calculations we approximate the $P^{\kappa\kappa}$ covariance matrix with the one one would obtain in the limit in which the $\kappa(\pmb{\theta})$ field is Gaussian
+
+\begin{widetext}
+\begin{equation}
+\label{meth:gausspcov}
+\left\langle\delta\h{P}_\ell(z_1,z_2)\delta\h{P}_\ell(z_3,z_4)\right\rangle = \frac{P_\ell(z_1,z_3)P_\ell(z_2,z_4)+P_\ell(z_1,z_4)P_\ell(z_2,z_3)}{f_{\rm sky}\delta\ell_{\rm bin}(2\ell+1)}
+\end{equation} 
+\end{widetext}
+%
+where $P_\ell(z_1,z_2)$ is a shorthand for $P^{\kappa\kappa}(\ell,z_1,z_2)$, $\delta\h{P}_\ell(z_1,z_2)=\h{P}_\ell(z_1,z_2) - P_\ell(z_1,z_2)$ is the scatter in the $\h{P}$ estimator, $\delta\ell_{\rm bin}$ is the width of the linearly spaced multipole bands and $f_{\rm sky} = \theta^2_{\rm FOV}/4\pi$ is the sky coverage fraction of one field of view.
+In this approximation the cross variance terms between different multipoles are assumed to be zero.
 
@@
 The rightmost black bar shows the same constraint, but obtained with redshift tomography and using the maximum number of PCA components seen in Figure \ref{fig:pcacomponents}.
-We show constrained obtained with the power spectrum (top right), peak counts (top left) and moments (bottom).}
+We show constrained obtained with the power spectrum (top right), peak counts (top left) and moments (bottom).
+The black dashed lines in the top left panel refer to parameter constraints on $w$ obtained with the public code NICAEA \citep{Nicaea}, assuming a Gaussian covariance model for the power spectrum, as specified by equation (\ref{meth:gausspcov}).
+}
 \label{fig:nopca}
@@
 
-\begin{figure}
-\includegraphics[scale=0.3]{Figures/constraints_Om-w.eps}
+\begin{figure*}
+\includegraphics[scale=0.3]{Figures/constraints_Om-w_lensing.eps}
+\includegraphics[scale=0.3]{Figures/constraints_Om-w_lensing_cmb.eps}
 \caption{$1\sigma$ confidence contours on the $(\Omega_m,w)$ parameter space, marginalized over $\sigma_8$, obtained using equation (\ref{meth:parcovestimator}).
-The covariance matrix $\bbh{C}$ and its inverse $\bbh{\Psi}$ have been obtained using $16000$ summary statistics realizations, and has been scaled by a factor $N_{\rm FOV}=1600$ to mimic the constraining power of an LSST-like survey.}
+The covariance matrix $\bbh{C}$ and its inverse $\bbh{\Psi}$ have been obtained using $16000$ summary statistics realizations, and has been scaled by a factor $N_{\rm FOV}=1600$ to mimic the constraining power of an LSST-like survey.
+The thick line ellipses in the right panel refer to $(\Omega_m,w)$ obtained from the weak lensing statistics considered in this work, but subject to Planck priors as described in equation (\ref{meth:parcovestimator_cmb}).}
 \label{fig:constraintsOm-w}
-\end{figure}
+\end{figure*}
 
@@
 \toprule
-                        \textbf{Statistic} & $\Delta \Omega_m$ & $\Delta w$ & $\Delta \sigma_8$ & $\sqrt[3]{\rm Volume}$ $(\Omega_m,w,\sigma_8)$ \\ \hline \hline
+                        \textbf{Statistic} & $\Delta \Omega_m$ & $\Delta w$ & $\Delta \sigma_8$ & $10^4\sqrt[3]{\rm Volume}$ $(\Omega_m,w,\sigma_8)$ \\ \hline \hline
 \midrule
-     Power spectrum ($\bar{z}_5$) &            0.0222 &     0.0286 &            0.0298 &                                       0.0087 \\
-      Power spectrum (tomography) &            0.0038 &     0.0213 &            0.0060 &                                       0.0042 \\
-              Peaks ($\bar{z}_5$) &            0.0049 &     0.0316 &            0.0050 &                                       0.0046 \\
-               Peaks (tomography) &            0.0042 &     0.0271 &            0.0043 &                                       0.0050 \\
-            Moments ($\bar{z}_5$) &            0.0027 &     0.0276 &            0.0026 &                                       0.0034 \\
-             Moments (tomography) &            0.0020 &     0.0214 &            0.0020 &                                       0.0028 \\ \hline \hline
-           Power spectrum + peaks &            0.0021 &     0.0153 &            0.0026 &                                       0.0030 \\ 
-         Power spectrum + moments &            0.0016 &     0.0150 &            0.0019 &                                       0.0025 \\
- Power spectrum + peaks + moments &            0.0015 &     0.0121 &            0.0018 &                                       0.0023 \\ \hline
+     Power spectrum ($\bar{z}_5$) &            0.0222 &     0.0286 &            0.0298 &                                                 86 \\
+      Power spectrum (tomography) &            0.0038 &     0.0213 &            0.0060 &                                                 42 \\
+              Peaks ($\bar{z}_5$) &            0.0049 &     0.0316 &            0.0050 &                                                 46 \\
+               Peaks (tomography) &            0.0042 &     0.0271 &            0.0043 &                                                 49 \\
+            Moments ($\bar{z}_5$) &            0.0027 &     0.0276 &            0.0026 &                                                 33 \\
+             Moments (tomography) &            0.0020 &     0.0214 &            0.0020 &                                                 28 \\ \hline \hline
+           Power spectrum + peaks &            0.0021 &     0.0153 &            0.0026 &                                                 29 \\
+         Power spectrum + moments &            0.0016 &     0.0150 &            0.0019 &                                                 24 \\
+ Power spectrum + peaks + moments &            0.0015 &     0.0121 &            0.0018 &                                                 22 \\ \hline
 \bottomrule
@@
 \caption{Constraints on the $(\Omega_m,w,\sigma_8)$ parameter triplet using different summary statistics and redshift information.
-Each column $(\Delta \Omega_m,\Delta w,\Delta \sigma_8)$ contains the 1 $\sigma$ constraints on a particular parameter, marginalized over the other two.
+Each column $(\Delta \Omega_m,\Delta w,\Delta \sigma_8)$ contains the 1$\sigma$ constraints on a particular parameter, marginalized over the other two.
 The last volume contains the volume of the $\sigma$ ellipsoid in $(\Omega_m,w,\sigma_8)$ space, calculated as $\sqrt{\det \bbh{\Sigma}}$.}
 \label{tbl:constraints}
+\end{table*}
+
+\begin{table*}
+\begin{tabular}{c|c|c|c|c|}
+\toprule
+                        \textbf{Statistic} & $\Delta \Omega_m$ & $\Delta w$ & $\Delta \sigma_8$ & $10^4\sqrt[3]{\rm Volume}$ $(\Omega_m,w,\sigma_8)$ \\ \hline \hline
+\midrule
+     Power spectrum ($\bar{z}_5$) &            0.0076 &     0.0274 &            0.0084 &                                                 45 \\
+      Power spectrum (tomography) &            0.0028 &     0.0129 &            0.0035 &                                                 31 \\
+              Peaks ($\bar{z}_5$) &            0.0048 &     0.0237 &            0.0050 &                                                 38 \\
+               Peaks (tomography) &            0.0041 &     0.0204 &            0.0042 &                                                 41 \\
+            Moments ($\bar{z}_5$) &            0.0024 &     0.0172 &            0.0025 &                                                 27 \\
+             Moments (tomography) &            0.0019 &     0.0149 &            0.0020 &                                                 24 \\ \hline \hline
+           Power spectrum + peaks &            0.0021 &     0.0127 &            0.0025 &                                                 26 \\ 
+         Power spectrum + moments &            0.0015 &     0.0120 &            0.0018 &                                                 22 \\
+ Power spectrum + peaks + moments &            0.0015 &     0.0104 &            0.0018 &                                                 21 \\ \hline
+\bottomrule
+\end{tabular}
+\caption{Constraints on the $(\Omega_m,w,\sigma_8)$ parameter triplet using different summary statistics and redshift information, including Fisher priors from Planck according to equation (\ref{meth:parcovestimator_cmb}).
+Each column $(\Delta \Omega_m,\Delta w,\Delta \sigma_8)$ contains the 1$\sigma$ constraints on a particular parameter, marginalized over the other two.
+The last volume contains the volume of the $\sigma$ ellipsoid in $(\Omega_m,w,\sigma_8)$ space, calculated as $\sqrt{\det \bbh{\Sigma}}$.}
+\label{tbl:constraints-cmb}
 \end{table*}
@@
 
+We thank Colin Hill for useful discussions. The simulations in this work
+were performed at the NSF XSEDE facility, supported by grant number
+ACI-1053575, and at the New York Center for Computational Sciences, a
+cooperative effort between Brookhaven National Laboratory and Stony
+Brook University, supported in part by the State of New York. This
+work was supported in part by the U.S. Department of Energy under
+Contract Nos. DE-AC02-98CH10886 and DE-SC0012704, and by the NSF Grant
+No. AST-1210877 (to Z.H.) and by the Research Opportunities and
+Approaches to Data Science (ROADS) program at the Institute for Data
+Sciences and Engineering at Columbia University (to Z.H.).
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-04-22 photoz_paper/Figures/generate.py

@@ -1,4 +1,5 @@
 #!/usr/bin/env python
+from __future__ import division
 
 import sys,os,argparse
 sys.modules["mpi4py"] = None
@@ -10,6 +11,8 @@ import pandas as pd
 import matplotlib.pyplot as plt
 
 from lenstools.catalog.shear import Catalog
+
+from lenstools.statistics.ensemble import SquareMatrix
 from lenstools.statistics.constraints import FisherAnalysis
 from lenstools.simulations.design import Design
 
@@ -125,7 +128,7 @@ def scibook_photo(cmd_args,fontsize=22):
 ###################################################################################################
 ###################################################################################################
 
-def constraints_no_pca(cmd_args,db_name="data/fisher/constraints_combine.sqlite",feature="power_spectrum",base_color="black",pca_components=[5,10],colors=["red","blue","green"],parameter="w",ylim=None,fontsize=22):
+def constraints_no_pca(cmd_args,db_name="data/fisher/constraints_combine.sqlite",feature="power_spectrum",base_color="black",tomo_color="magenta",pca_components=[5,10],colors=["red","blue","green"],parameter="w",ylim=None,fontsize=22):
 
 	#Set up plot
 	fig,ax = plt.subplots()
@@ -157,16 +160,15 @@ def constraints_no_pca(cmd_args,db_name="data/fisher/constraints_combine.sqlite"
 		#Plot tomographic constraint with the maximum number of pca components
 		var_db = db.query('SELECT "{0}-{0}",bins,feature_label FROM pcov_noise'.format(parameter))
 		var_feature_tomo,nc,label = var_db.query("feature_label=='{0}'".format(feature+"_pca")).tail(1).values.flat
-		ax.bar(5,np.sqrt(var_feature_tomo),width=2,color=base_color)
+		ax.bar(5,np.sqrt(var_feature_tomo),width=1,fill=False,edgecolor=tomo_color,label=r"$(N_c={0})$".format(int(nc)))
 
 		#Put a percent value on the last bar of the graph
[…]

### 2016-04-25 photoz_paper/paper.tex
finished revised version with CMB priors

@@
 We forecast parameter constraints on the triplet $(\Omega_m,w,\sigma_8)$ for an LSST like galaxy photometric survey, using tomography of the shear-shear power spectrum, convergence peak counts and higher convergence moments.
-We find that the addition of peak counts and moments to the power spectrum can significantly improve the constraints on the $(\Omega_m,w)$ doublet.
-We also find that most of the cosmological information on $w$ is contained in the highest redshift galaxies, with redshift tomography further improving the constraints by only 15\% to 30\%.
-The improvement obtained with power spectrum tomography is larger for the doublet $(\Omega_m,\sigma_8)$, or which the 1$\sigma$ error bar shrinks by a factor of 5.
+We find that redshift tomography with the power spectrum shrinks the $1\sigma$ confidence interval area in $(\Omega_m,w)$ space by a factor of 8 with respect to the case of a single redshift bin.
+We also find that adding non-Gaussian information from the peak counts and higher moments of the convergence further shrinks the constrained area in $(\Omega_m,w)$ by a factor of respectively 3 and 4.
+When we add parameter priors from Planck to our analysis, we find that the improvements using tomography and non-Gaussian statistics are less important, spanning a factor of 3 at most using power spectrum tomography, but only improving by 30\% when adding the peak counts.
 We evaluate the effect of uncorrected photometric redshift systematics on parameter constraints.
@@
 %
-Weak gravitational lensing is a promising technique to probe the large scale structure of the universe in which the tracers are unbiased \citep{wlreview}.
-This technique has the potential of improving significantly the constraints on the dark energy equation of state $w$ because it is most sensitive to the matter density fluctuations at the non--linear stage.
-Cosmology inferences from Weak Lensing observations have been produced for past (CFHTLenS \citep{cfht1}) and current (DES \citep{DES}) surveys, and are being planned for future experiments as well (LSST \citep{LSST}, WFIRST \citep{WFIRST}, Euclid \citep{Euclid}).
-Because of the non-linear nature of the density fluctuations probed by Weak Lensing, cosmological information might leak from quadratic statistics (such as two point functions and power spectra) into more complicated non-Gaussian statistics, for which forward modeling from cosmological parameters requires numerical simulations of cosmic shear fields.
-Different examples of these non-Gaussian statistics, and their cosmological information content, have been investigated extensively in the literature (see \citep{MinkJan,PeaksJan,NG-Marian,NG-Jain1,NG-Jain2,NG-Jain3,NG-Refregier,NG-Dietrich} for a non comprehensive list).
-The constraining power of Weak Lensing power spectra with the addition of redshift tomography information have been extensively investigated in the literature (see \citep{SongKnox,FangHaiman07,Huterer2006}).
-In this work we concentrate on the constraining power of a subset of these non-Gaussian statistics combined with redshift tomography in a LSST-like survey.
-Previous work on redshift tomography with Weak Lensing Minkowski functionals is also present in the literature \citep{MinkJan}.
-We also investigate the effects of uncorrected photometric redshift systematics on parameter constraints when using redshift tomography.
-This work is organized as follows: we give an outline of the shear simulations we use in this work, followed by descriptions of the convergence reconstruction procedure and forward modeling of galaxy shape and photometric redshift systematics.
-We then give an overview of the parameter inferences techniques we used to forecast constraints on cosmology.
-We then discuss the main results of this work and present our conclusions as well as prospects for future work.
+Weak gravitational lensing is a promising technique to probe the large scale structure of the universe in which the tracers are intrinsically unbiased \citep{wlreview}.
+This technique has the potential of significantly improving the constraints on the dark energy equation of state parameter $w$ because it is most sensitive to the matter density fluctuations at the non--linear stage.
+Cosmology inferences from weak lensing observations have been produced for past (CFHTLenS \citep{cfht1}, COSMOS \citep{cosmos}) and current (DES \citep{DES}) surveys, and are being planned for future experiments as well (e.g.
+LSST \citep{LSST}, WFIRST \citep{WFIRST}, Euclid \citep{Euclid}).
+Because of the non-linear nature of the density fluctuations probed by weak lensing, cosmological information might leak from quadratic statistics (such as two-point functions and power spectra) into more complicated non-Gaussian statistics, for which forward modeling requires numerical simulations of cosmic shear fields.
+
+Several different examples of these non-Gaussian statistics, and their cosmological information content, have been studied in the past as well (see \citep{MinkJan,PeaksJan,NG-Marian,NG-Jain1,NG-Jain2,NG-Jain3,NG-Refregier,NG-Dietrich} for a non-comprehensive list).
+The constraining power of weak lensing power spectra with the addition of redshift tomography information have been extensively investigated in the literature (see e.g.
+\citep{SongKnox,FangHaiman07,Huterer2006}).
+In this work we concentrate on the constraining power of a subset of non-Gaussian statistics, combined with redshift tomography in an LSST-like survey.
+Previous work on redshift tomography with weak lensing Minkowski functionals is also present in the literature \citep{MinkJan}.
+
+Tomography relies on assigning accurate redshifts to galaxies.
+We therefore also investigate the effects of uncorrected photometric redshift systematics on parameter constraints when using redshift tomography.
+This work is organized as follows: in \S~\ref{sec:methods} we outline the shear simulations we use in this work, followed by descriptions of the convergence reconstruction procedure, forward modeling of galaxy shape and photometric redshift systematics, and the parameter-inference techniques we used to forecast constraints on cosmology.
+In \S~\ref{sec:results} we present our main results, which we discuss in \S~\ref{sec:discussion}.
+In \S~\ref{sec:conclusions} we present our conclusions as well as prospects for future work.
 
@@
 \section{Methods}
+\label{sec:methods}
 
@@
 We review the procedure used for generating simulated shear catalogs.
-We consider a fiducial flat $\Lambda$CDM universe with $(h,\Omega_m,\Omega_\Lambda,\Omega_b,w,\sigma_8,n_s)=(0.72,0.26,0.74,0.046,-1,0.8,0.96)$.
+We consider a fiducial flat $\Lambda$CDM universe with parameters $(h,\Omega_m,\Omega_\Lambda,\Omega_b,w,\sigma_8,n_s)=(0.72,0.26,0.74,0.046,-1,0.8,0.96)$ \citep{WMAP9,PlanckCosmo}.
 We examine different variations of the $\bb{p}=(\Omega_m,w,\sigma_8)$ triplet and run one $N$--body simulation for each choice of $\bb{p}$, using the public code \ttt{Gadget2} \citep{Gadget2}.
@@
 The three dimensional outputs of the $N$--body simulations are sliced in sequences of two dimensional lenses $120 \,{\rm Mpc}$ thick, which are lined up perpendicular to the line of sight between the observer on Earth and a source at redshift $z_s$.
-We make use of the multi--lens--plane algorithm \citep{RayTracingJain,RayTracingHartlap} to trace the deflections of light rays originating at $z=0$ through the system of lenses until $z$.
+We make use of the multi--lens--plane algorithm \citep{RayTracingJain,RayTracingHartlap} to trace the deflections of light rays originating at $z=0$ through the system of lenses out to redshift $z$.
 To accomplish this task, we make use of the \ttt{LensTools} \citep{LensTools-ASCL,LensTools-paper} implementation of the multi--lens--plane algorithm.
-An observed galaxy position $\pmb{\theta}$ on the sky today corresponds to a real galaxy angular position $\pmb{\beta}(\pmb{\theta},z_s)$, which can be calculated using the \ttt{LensTools} pipeline by solving the lensing ordinary differential equations up to redshift $z_s$.
+An observed galaxy position $\pmb{\theta}$ on the sky today corresponds to a real galaxy angular position $\pmb{\beta}(\pmb{\theta},z_s)$, which can be calculated using the \ttt{LensTools} pipeline by solving the ordinary differential lens equations up to redshift $z_s$.
 The Jacobian of $\pmb{\beta}(\pmb{\theta},z_s)$ is a $2\times 2$ matrix that contains information about the cosmic shear field at $\pmb{\theta}$ integrated along the line of sight.
@@
 %
-The quantities that appear in equation (\ref{meth:sheareqn}) are the convergence $\kappa$, which is the source magnification due to lensing, and the cosmic shear $\pmb{\gamma}$, which is a measurement of the source ellipticity due to lensing from large scale structure, assuming the non lensed shape is a circle.
-We simulate $N_g = 10^6$ random galaxy positions $\{\pmb{\theta}_g\}$ distributed uniformly in a field of view of size $\theta_{\rm FOV}^2=(3.5{\rm deg})^2$, which correspond to a galaxy angular density of $n_g=22\,\rm{arcmin}^{-2}$.
-The galaxies have a distribution in redshift which mimics the one expected in the LSST survey
+The quantities that appear in equation (\ref{meth:sheareqn}) are the convergence $\kappa$, which is the source magnification due to lensing, and the cosmic shear $\pmb{\gamma}$, which is a measurement of the source ellipticity due to lensing from large scale structure, assuming the non-lensed shape is a circle.
+
+We simulate $N_g = 10^6$ random galaxy positions $\{\pmb{\theta}_g\}$ distributed uniformly in a field of view of size $\theta_{\rm FOV}^2=(3.5{\rm deg})^2$, which correspond to a galaxy surface density of $n_g=22\,\rm{arcmin}^{-2}$.
+The galaxies have a distribution in redshift which mimics the one expected in the LSST survey,
 \begin{equation}
 \label{meth:galdistr}
-n(z) = n_0\left(\frac{z}{z_0}\right)^2\exp\left(-\frac{z}{z_0}\right)
+n(z) = n_0\left(\frac{z}{z_0}\right)^2\exp\left(-\frac{z}{z_0}\right) ,
 \end{equation}  
@@
 The galaxies have a maximum redshift $z_{\rm max}=3$.
-For each galaxy we compute the cosmic shear at $\pmb{\theta}_g$ using equation (\ref{meth:sheareqn}), producing a shear catalog $\{\pmb{\gamma}_g\}$.
+For each galaxy, we compute the cosmic shear at $\pmb{\theta}_g$ using equation (\ref{meth:sheareqn}), producing a shear catalog $\{\pmb{\gamma}_g\}$.
 Different random realizations of a shear catalog $\{\pmb{\gamma}_g\}_r$ can be obtained rotating and periodically shifting the large scale structure in the $N$--body snapshots according to the procedure explained in \citep{PetriVariance}.
 We produce $N_r=16000$ pseudo--independent realizations of the shear catalog $\{\pmb{\gamma}_g\}$.
-These shear realization cover the total survey area of LSST 10 times.
+These shear realizations all together cover 10 times the total survey area of LSST.
 We repeat the above procedure for $P=100$ different combinations of the parameter triplet $\bb{p}$, sampled according to a Latin hypercube scheme.
-The sampling procedure is the same described in \citep{CFHTMink,CFHTPeaks}.
-The parameter space sampling we adopted for our simulations is shown in Figure \ref{fig:simdesign}
+The sampling procedure is the same as described in \citep{CFHTMink,CFHTPeaks}.
+The parameter space sampling we adopted for our simulations is shown in Figure \ref{fig:simdesign}.
 
@@
 \caption{Parameter space sampling chosen for our simulations.
-We show both the sampling in the $(\Omega_m,w)$ (left), $(\Omega_m,\sigma_8)$ (center) and $(\sigma_8,w)$ (right) slices of the parameter space.
+We show the sampling in the $(\Omega_m,w)$ (left), $(\Omega_m,\sigma_8)$ (center) and $(\sigma_8,w)$ (right) projections of the parameter space.
 The fiducial cosmology has been marked in red.}
@@
 In this case the randomization procedure is based on 5 independent $N$--body simulations, and the same number $N_r=16000$ of pseudo--independent catalog realizations is produced.
-This additional simulation set serves two purposes: it provides an independent dataset from which to measure covariance matrices and it provides a way to construct simulated observations that are independent of the simulations on which the cosmological forward model is trained.
+This additional simulation set serves two purposes: it provides an independent dataset from which to measure covariance matrices, and it provides a way to construct simulated observations that are independent of the simulations on which the cosmological forward model is trained.
 For the fiducial dataset we chose to base the shear randomization procedure on 5 independent $N$--body simulations to ensure the independence of the $N_r$ realizations for the purpose of estimating covariance matrices.
+Ref.
 \citep{PetriVariance} recently showed that, even with only one $N$--body simulation a few $10^4$ independent realizations can be produced.
@@
 \subsection{Forward modeling of systematics}
-We give an overview of the shear systematics included in this work.
+We next give an overview of the shear systematics included in this work.
 
@@
 where $\pmb{\epsilon}_{\rm n}$ is a random Gaussian variable with zero mean and redshift dependent variance $\sigma_n(z_s)=0.15+0.035z_s$.
-This is equivalent to say that the cosmic shear inferred from ellipticity observations $\pmb{\gamma}_{\rm m}$ can be written as the sum of the true cosmic shear plus a noise term $\pmb{\gamma}_{\rm n}$ with the same statistical properties as $\pmb{\epsilon}_{\rm n}$.
+This is equivalent to saying that the cosmic shear inferred from ellipticity observations $\pmb{\gamma}_{\rm m}$ can be written as the sum of the true cosmic shear plus a noise term $\pmb{\gamma}_{\rm n}$ with the same statistical properties as $\pmb{\epsilon}_{\rm n}$.
 We add independent random realizations of the shape noise $\pmb{\gamma}_{\rm n}$ to each of the $N_r$ shear catalogs.
@@
 
-In addition to shape noise contributions to the observed galaxy ellipticity we consider photometric redshift errors as an additional contamination source in the simulated catalogs.
-In photometric surveys such as LSST, the source redshift $z_s$ is estimated measuring the source luminosity in a finite small set of optical frequency bands.
+In addition to shape noise contributions to the observed galaxy ellipticity, we consider photometric redshift errors as an additional contamination in the simulated catalogs.
+In photometric surveys such as LSST, the source redshift $z_s$ is estimated measuring the source luminosity in a small finite set of optical frequency bands.
 Using this compressed luminosity information rather than the full spectrum introduces biases in redshift estimation.
@@
 
-The study of photometric redshift errors is an active subject of research, and includes investigation of techniques such as spectroscopic calibration, catastrophic errors and cross-correlation techniques that we do not explore in this work (see for example \citep{HuTomo} for a more throughout discussion).
-We model effect of photo-$z$ errors as a constant bias term $b_{\rm ph}(z_s)$ plus a random Gaussian component with variance $\sigma_{\rm ph}(z_s)$
+The study of photometric redshift errors is an active subject of research, and includes investigation of techniques such as spectroscopic calibration, catastrophic errors and cross-correlation techniques that we do not explore in this work (see for example \citep{HuTomo} for a more thorough discussion).
+We model the effect of photo-$z$ errors as a constant bias term $b_{\rm ph}(z_s)$ plus a random Gaussian component with variance $\sigma_{\rm ph}(z_s)$,
 \begin{equation}
 \label{meth:photoz-correction}
-z_p(z_s) = z_s + b_{\rm ph}(z_s) + \sigma_{\rm ph}(z_s)\mathcal{N}(0,1)   
+z_p(z_s) = z_s + b_{\rm ph}(z_s) + \sigma_{\rm ph}(z_s)\mathcal{N}(0,1),   
 \end{equation}
@@
 where $\mathcal{N}(0,1)$ is the standard normal distribution.
-We bin the $N_g$ galaxies in our simulated catalogs in 5 redshift bins $\bar{z}_b$, $b=1...5$.
+We bin the $N_g$ galaxies in our simulated catalogs into 5 redshift bins $\bar{z}_b$, $b=1...5$.
 Several models have been proposed in the literature for the photometric bias $b_{\rm ph}(z_s)$ (see for example \citep{Huterer2006}) and variance $\sigma_{\rm ph}(z_s)$ (see for example \citep{LSSTSciBook}).
@@
 We generate simulated observations by applying an independent random realization of the photo-$z$ correction (\ref{meth:photoz-correction}) to each catalog realization in the fiducial cosmology $\bb{p}_0$ and by re--binning the galaxies according to their photometric redshifts $z_p$.
-In the remainder of the paper we use the following notation: we indicate a shear realization $r$ in cosmology $\bb{p}$ with shape noise added as $\h{\pmb{\gamma}}_r(\pmb{\theta}_g,z_g;\bb{p})$, and we indicate a simulated observation as $\h{\pmb{\gamma}}_{\rm obs}(\pmb{\theta}_g,z_g)$.
+In the remainder of the paper we use the following notation: we indicate a shear realization $r$ in cosmology $\bb{p}$ with shape noise added as $\h{\pmb{\gamma}}_r(\pmb{\theta}_g,z_g;\bb{p})$, and we indicate a simulated observation in the fiducial cosmology as $\h{\pmb{\gamma}}_{\rm obs}(\pmb{\theta}_g,z_g)$.
 
@@
 %
-The convergence $\kappa(\pmb{\theta}_p)$ can be reconstructed from the $E$--mode of the shear field, which is evaluated from the Fourier Transform of the pixelized shear $\pmb{\gamma}(\pmb{\theta}_p,\bar{z}_b)$
+The convergence $\kappa(\pmb{\theta}_p)$ can be reconstructed from the $E$--mode of the shear field, which is evaluated from the Fourier transform of the pixelized shear $\pmb{\gamma}(\pmb{\theta}_p,\bar{z}_b)$
 \begin{equation}
@@
 We chose the Gaussian filter smoothing scale $\theta_G=0.5\,{\rm arcmin}$ to correspond to the linear pixel resolution.
-Inverting the Fourier Transform yields the pixelized map $\kappa(\pmb{\theta}_p,\bar{z}_b)$.
+Inverting the Fourier transform yields the pixelized map $\kappa(\pmb{\theta}_p,\bar{z}_b)$.
 We apply this procedure to both the shear realizations $\h{\pmb{\gamma}}_r(\pmb{\theta}_g,z_g;\bb{p})$ and the simulated observations $\h{\pmb{\gamma}}_{\rm obs}(\pmb{\theta}_g,z_g)$, yielding convergence realizations $\h{\kappa}_r(\pmb{\theta}_p,\bar{z}_b;\bb{p})$ and simulated convergence observations $\h{\kappa}_{\rm obs}(\pmb{\theta}_p,\bar{z}_b)$.
@@
 We measure a variety of summary statistics from the pixelized convergence maps, which will then be used to forecast parameter constraints and biases.
-We consider three kinds of summary statistics, namely the $\kappa$ tomographic power spectrum $P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})$, the tomographic peak counts $n_{\rm pk}(\nu,\bar{z}_b)$ and a set of $\kappa$ moments $\pmb{\mu}(\bar{z}_b)$.
+We consider three kinds of summary statistics, namely the tomographic power spectrum $P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})$, the tomographic peak counts $n_{\rm pk}(\nu,\bar{z}_b)$ and a set of moments $\pmb{\mu}(\bar{z}_b)$.
 The tomographic power spectrum is defined as
@@
 %
-Because the $\kappa$ field is statistically isotropical, the expectation value $\langle\rangle$, for each realization $r$, is taken over all the modes $\pmb{\ell}$ which have the same magnitude $\ell=\vert\pmb{\ell}\vert$.
-The peak count statistic $n_{\rm pk}(\nu,\bar{z}_b)$ is defined as the number of the $\kappa$ local maxima of a certain height $\kappa_{\rm max}=\nu\sigma_0$, where $\sigma_0$ is the $\kappa$ standard deviation over pixels.
-The $\kappa$ moments $\pmb{\mu}(\bar{z}_b)$ are defined as follows (see \citep{Matsubara10,Munshi12,MinkPetri})
+Because the $\kappa$ field is statistically isotropic, the expectation value $\langle\rangle$, for each realization $r$, is taken over all modes $\pmb{\ell}$ with the same magnitude $\ell=\vert\pmb{\ell}\vert$.
+The peak count statistic $n_{\rm pk}(\nu,\bar{z}_b)$ is defined as the number of the local maxima of a certain height $\kappa_{\rm max}=\nu\sigma_0$, where $\sigma_0$ is the standard deviation over all pixels.
+The set of nine moments $\pmb{\mu}(\bar{z}_b)$ is defined as follows (see \citep{Matsubara10,Munshi12,MinkPetri}):
 %
@@
 \pmb{\mu}_3 = (\langle\kappa^3\rangle,\langle\kappa\vert\nabla\kappa\vert^2\rangle,\langle\kappa^2\nabla^2\kappa\rangle) \\ \\
-\pmb{\mu}_4 = (\langle\kappa^4\rangle_c,\langle\kappa^2\vert\nabla\kappa\vert^2\rangle_c,\langle\kappa^3\nabla^2\kappa\rangle_c,\langle\vert\nabla\kappa\vert^4\rangle_c)
+\pmb{\mu}_4 = (\langle\kappa^4\rangle_c,\langle\kappa^2\vert\nabla\kappa\vert^2\rangle_c,\langle\kappa^3\nabla^2\kappa\rangle_c,\langle\vert\nabla\kappa\vert^4\rangle_c) .
 \end{matrix}
@@
 In the definition of the peak counts and convergence moments we omitted the redshift index $\bar{z}_b$ for notational simplicity.
-In the next paragraph we describe the statistical methods we use to infer cosmological parameter estimates $\bbh{p}$ from simulated observations $\h{\kappa}_{\rm obs}(\pmb{\theta}_p,\bar{z}_b)$ using the summary statistics $P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})$, $n_{\rm pk}(\nu,\bar{z}_b)$, $\pmb{\mu}(\bar{z}_b)$.
+In the next section, we describe the statistical methods we use to infer cosmological parameter estimates $\bbh{p}$ from simulated observations $\h{\kappa}_{\rm obs}(\pmb{\theta}_p,\bar{z}_b)$ using the summary statistics $P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})$, $n_{\rm pk}(\nu,\bar{z}_b)$ and $\pmb{\mu}(\bar{z}_b)$.
 
@@
 We adopt a Bayesian framework to forecast parameter constraints.
-We indicate as $\bb{d}$ a summary statistic vector (which can be any of $P^{\kappa\kappa},n_{\rm pk},\pmb{\mu}$ or a combination of the former).
+We indicate as $\bb{d}$ a summary statistic vector (which can be any of $P^{\kappa\kappa},n_{\rm pk},\pmb{\mu}$ or a combination of these).
 We label $\bb{d}(\bb{p})$ the sample mean of $\bb{d}$ over the $N_r=16000$ simulated realizations in cosmology $\bb{p}$ and we label $\bbh{d}_r$ the summary statistic measured in realization $r$ of the fiducial cosmology $\bb{p}_0$.
@@
 $\bbh{d}_{\rm obs}$ is measured averaging a random sample of $N_{\rm FOV}=1600$ realizations of the fiducial cosmology with photo-$z$ errors added.
-This number has been chosen to mimic the survey are of LSST $\Omega_{\rm LSST}=N_{\rm FOV}\theta_{\rm FOV}^2$.
-Assuming no prior knowledge of the parameters $\bb{p}$, we can write the parameter likelihood $\mathcal{L}$ given the observation $\bbh{d}_{\rm obs}$ using the Bayes theorem
+This number has been chosen to mimic the survey area of LSST $\Omega_{\rm LSST}=N_{\rm FOV}\theta_{\rm FOV}^2$.
+Assuming no prior knowledge of the parameters $\bb{p}$, we can write the parameter likelihood $\mathcal{L}$ given the observation $\bbh{d}_{\rm obs}$ using Bayes' theorem
 %
@@
 \begin{equation}
-\bbh{d}_{\rm mean} = \frac{1}{N_r}\sum_{r=1}^{N_r}\bbh{d}_r 
+\bbh{d}_{\rm mean} = \frac{1}{N_r}\sum_{r=1}^{N_r}\bbh{d}_r ,
 \end{equation}
@@
 \begin{equation}
-\bbh{C} = \frac{1}{N_r-1}\sum_{r=1}^{N_r} (\bbh{d}_r-\bbh{d}_{\rm mean})(\bbh{d}_r-\bbh{d}_{\rm mean})^T
+\bbh{C} = \frac{1}{N_r-1}\sum_{r=1}^{N_r} (\bbh{d}_r-\bbh{d}_{\rm mean})(\bbh{d}_r-\bbh{d}_{\rm mean})^T .
 \end{equation} 
@@
 Parameter errors $\Delta\bbh{p}$ can be inferred from the likelihood confidence contours.
-Approximate estimates of $\bbh{p},\Delta \bbh{p}$ can be obtained approximating the model statistic $\bb{d}(\bb{p})$ dependency on parameters as linear in $\bb{p}$ provided $\bb{p}$ is not too far from the fiducial model $\bb{p}_0$
+Estimates of $\bbh{p},\Delta \bbh{p}$ can be obtained by approximating the model statistic $\bb{d}(\bb{p})$ dependency on parameters as linear in $\bb{p}$, provided $\bb{p}$ is not too far from the fiducial model $\bb{p}_0$
 \begin{equation}
@@
 %
-Where we defined $(\bb{M})_{i\alpha}=(\partial d_i(\bb{p})/\partial p_\alpha)_{\bb{p}_0}$ as the statistic first derivative with respect to cosmology.
+where we defined $(\bb{M})_{i\alpha}=(\partial d_i(\bb{p})/\partial p_\alpha)_{\bb{p}_0}$ as the first derivative of the statistic $d_i(\bb{p})$ with respect to cosmology.
 We evaluate $\bb{M}$ with finite differences on the smooth RBF interpolation of the summary statistic $\bb{d}(\bb{p})$.
@@
 %
-Here we indicated $\bbh{\Psi}=\bbh{C}^{-1}$ as the summary statistic precision matrix.
+Here $\bbh{\Psi}\equiv\bbh{C}^{-1}$ denotes the summary statistic's precision matrix.
 With the linear approximation (\ref{meth:linapprox}) the parameter likelihood (\ref{meth:paramlikelihood}) is a multivariate Gaussian in $\bb{p}$ and its width $\bbh{\Sigma}$ can be estimated as
@@
 The square of the $1\sigma$ parameter errors $\Delta \bbh{p}^2$ are the diagonal entries of $\bbh{\Sigma}$.
-The parameter covariance estimator (\ref{meth:parcovestimator}) is the same that one gets adopting a Fisher Matrix formalism for parameter forecasts (see \citep{astroMLText}).
+The parameter covariance estimator (\ref{meth:parcovestimator}) is the same as one gets adopting a Fisher Matrix formalism for parameter forecasts (see \citep{astroMLText}).
 
 When the dimension $N_b$ of the summary statistics space is large, numerical issues can arise in the estimation of the parameter error bars if the covariance matrix $\bbh{C}$ is measured from simulations.
-When $N_r$ independent realizations are used to estimate $\bbh{C}$, its inverse $\bbh{\Psi}$ is biased by a constant factor (see \citep{Hartlap07,Taylor12,Taylor14}) that can be taken into account.
+When $N_r$ independent realizations are used to estimate $\bbh{C}$, its inverse $\bbh{\Psi}$ is biased by a constant factor (see \citep{Hartlap07,Taylor12,Taylor14}) which can be taken into account.
 When the bias correction is applied, we can calculate the expectation value of the covariance estimator (\ref{meth:parcovestimator}) (see again\citep{Taylor14})
@@
 %
-where $\bb{\Sigma}$ is the asymptotic covariance one obtains with an infinite number of realizations and $N_p$ is the number of parameters we are estimating, in this case 3.
+where $\bb{\Sigma}$ is the asymptotic covariance one obtains with an infinite number of realizations and $N_p=3$ is the number of parameters we are estimating.
 The scatter of the parameter estimates (\ref{meth:parestimate}) on the other hand scales as \citep{Taylor14}
@@
 Although equations (\ref{meth:covdegradation}) and (\ref{meth:estdegradation}) agree in the limit $N_r\rightarrow\infty$, they can be different when a finite number of realizations is used.
-More in detail, the degradation factor in the parameter covariance estimate in (\ref{meth:covdegradation}) is of order $1+(1+N_p)/N_r$, while the actual scatter of the estimates $\bbh{p}$ is of order $1+(N_b-N_p)/N_r$.
-These numbers can very different if $N_b$ is big.
+The degradation factor in the parameter covariance estimate in (\ref{meth:covdegradation}) is of order $1+(1+N_p)/N_r$, while the scatter of the estimates $\bbh{p}$ is of order $1+(N_b-N_p)/N_r$.
+These numbers can be very different if $N_b$ is large.
 This means that the parameter error bar estimate (\ref{meth:covdegradation}) is too conservative if $N_b/N_r$ is of order unity.
 This could be likely the case in our analysis because of the inclusion of tomography information.
-In order to avoid these error degradation issues, we apply dimensional reduction techniques to the summary statistics we are considering.
-These techniques are explained in the next paragraph.
+If we bin the single redshift summary statistic with $N_{\rm st}$ intervals, and consider $N_z$ redshift bins, this can lead to a summary statistic vector of size $N_b = O(N_{\rm st}N_z^2)$ for the power spectrum and $N_b = O(N_{\rm st}N_z)$ for the remaining statistics.
+This can become quickly comparable with $N_r=16000$ once more redshift bins or a finer binning of the summary statistic are considered.
+In order to avoid these error degradation issues, we apply dimensionality reduction techniques to the summary statistics we are considering.
+Even if these techniques might not play a vital role in this work, as the maximum $N_b/N_r$ ratio we use is of order 1\%, they will definitely be relevant in future experiments when using finely binned summary statistics or when combining different cosmological probes.
+We explain the dimensionality reduction techniques we adopted in the next paragraph.
 
@@
 \subsection{Dimensionality reduction}
-We apply Principal Component Analysis techniques (see \citep{astroMLText} for example) to reduce the dimensionality of our summary statistics while preserving the cosmological information content.
-Consider the model statistic $\bb{d}(\bb{p})$, and think of it in terms of a $P\times N_b$ matrix $d_{pi}$.
+We apply a Principal Component Analysis (see \citep{astroMLText} for example) to reduce the dimensionality of our summary statistics while preserving the cosmological information content.
+The model statistic $\bb{d}(\bb{p})$ can be regarded as a$P\times N_b$ matrix $d_{pi}$.
 Consider the whitened model matrix
 \begin{equation}
-\Delta_{pi} = P\frac{d_{pi}}{\sum_{q=1}^Pd_{qi}} - 1
+\label{meth:whitening}
+\Delta_{pi} = P\frac{d_{pi}}{\sum_{q=1}^Pd_{qi}} - 1.
 \end{equation} 
@@
 The singular value $\Lambda_n$ is the variance of the whitened summary statistic along the $n$-th basis vector.
-We assume that only summary statistic projections on the first $N_c$ basis vectors contain relevant cosmological information, and $N_c<N_b$ is a number that has to be determined from the simulations.
+We assume that only summary statistic projections on the first $N_c$ basis vectors contain relevant cosmological information, where $N_c<N_b$ is a number that has to be determined from the simulations.
 Let $\bb{R}(N_c)$ be a matrix made of the first $N_c$ rows of $\bb{R}$ (we assume that the singular values $\Lambda_i$ are sorted).
@@
 %
-In this way we hope to capture the cosmological information contained in $\bbh{d}$ by projecting it on the $N_c<N_b$ principal components that vary the most with cosmology parameters.
+Through the above procedure, we hope to capture the cosmological information contained in $\bbh{d}$ by projecting it on the $N_c<N_b$ principal components that vary the most with cosmology parameters.
 In the next section we outline the main results of this work.
@@
 where we assumed that the best fit parameters are the same $\bb{p}_0$ that appear in equation (\ref{meth:linapprox}). 
-Parameter constraints from the Planck CMB experiment are made available to the public via the parameter Markov Chains (MCMC) published on the Planck Legacy Archive \footnote{\url{http://pla.esac.esa.int/pla/}}.
+Parameter constraints from the Planck CMB experiment are made available to the public via the parameter Markov Chains (MCMC) published on the Planck Legacy Archive \footnote{The archive we used is located \url{http://pla.esac.esa.int/pla/}; we used the MCMC chains contained in the \ttt{base\_w/plikHM\_TT\_lowTEB} directory, labeled as \ttt{base\_w\_plikHM\_TT\_lowTEB\_[1-4].txt}}.
 We can use these MCMC data to estimate the parameter covariance matrix $\bb{\Sigma}_{\rm CMB}$ on the parameter multiplet $(\Omega_m,\Omega_bh^2,\theta_{\rm MC},\tau,w,n_s,\sigma_8)$, marginalized over the Planck nuisance parameters.
@@
 \section{Results}
+\label{sec:results}
 
@@
 In this section we present the main results of this work.
-Figure \ref{fig:pcacomponents} shows the robustness of the dimensionality reduction technique we adopted.
-on the three summary statistics considered, namely the convergence power spectrum $P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})$, peak counts $n_{\rm pk}(\nu,\bar{z}_b)$ and moments $\pmb{\mu}(\bar{z}_b)$.
+Figure \ref{fig:pcacomponents} shows the robustness of the dimensionality reduction technique we adopted for the three summary statistics considered, namely the convergence power spectrum $P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})$, peak counts $n_{\rm pk}(\nu,\bar{z}_b)$ and moments $\pmb{\mu}(\bar{z}_b)$.
 To measure the power spectrum we chose 15 uniformly spaced multipole bands between $(\ell_{\rm min},\ell_{\rm max})=(200,2000)$.
-There are only 15 $(\bar{z}_b,\bar{z}_{b'})$ independent combinations (5 diagonal + 10 off-diagonal), which leads to a total of $N_b=15\times 15=225$ power spectrum measurement bands, including cross redshift information.
-We bin the convergence peak counts in 30 uniformly spaced $\nu$ bins between $(\nu_{\rm min},\nu_{\rm max})=(-2,7)$, for a total of $N_b=30\times5=150$ measurement bands, including redshift information.
-The total size of the moments summary statistic vector is $N_b=9\times 5=45$, including redshift information.
+There are only 15 independent $(\bar{z}_b,\bar{z}_{b'})$ combinations (5 diagonal + 10 off-diagonal), which leads to a total of $N_b=15({\rm multipoles})\times 15({\rm redshift})=225$ power spectrum measurement bands, including cross redshift information.
+We bin the convergence peak counts in 30 uniformly spaced $\nu$ bins between $(\nu_{\rm min},\nu_{\rm max})=(-2,7)$, for a total of $N_b=30 (\rm peak \,\,heights)\times5({\rm redshift})=150$ measurement bands.
+The total size of the moments summary statistic vector is $N_b=9(\rm moments)\times 5(\rm redshift)=45$.
 
-The forecast error bars on $w$ are calculated according to equation (\ref{meth:parcovestimator}), where the covariance matrix $\bbh{C}$ and its inverse $\bbh{\Psi}$ have been estimated with $N_r=16000$ realizations of each summary statistic in the fiducial cosmology.
+The forecast error bars on $w$ are calculated according to equation (\ref{meth:parcovestimator}), where the covariance matrix $\bbh{C}$ and its inverse $\bbh{\Psi}$ have been estimated from $N_r=16000$ realizations of each summary statistic in the fiducial cosmology.
 
@@
 \includegraphics[scale=0.3]{Figures/w_moments_no_pca.pdf}
-\caption{Comparison between single redshift $w$ constraints (marginalized over $(\Omega_m,\sigma_8)$) obtained without PCA (gray shaded bars) and with PCA (colored bars) as a function of the redshift bin $\bar{z}_b$.
-The rightmost black bar shows the same constraint, but obtained with redshift tomography and using the maximum number of PCA components seen in Figure \ref{fig:pcacomponents}.
-We show constrained obtained with the power spectrum (top right), peak counts (top left) and moments (bottom).
-The black dashed lines in the top left panel refer to parameter constraints on $w$ obtained with the public code NICAEA \citep{Nicaea}, assuming a Gaussian covariance model for the power spectrum, as specified by equation (\ref{meth:gausspcov}).
-}
+\caption{Comparison between single-redshift $w$ constraints (marginalized over $\Omega_m$ and $\sigma_8$) obtained without PCA (gray shaded bars) and with PCA (colored bars) as a function of the redshift bin $\bar{z}_b$.
+We show constraints obtained from the power spectrum (top left), peak counts (top right) and moments (bottom).
+Note the different scales on the vertical axis in the three different panels.
+The black dashed lines in the top left panel refer to parameter constraints on $w$ obtained with the public code NICAEA \citep{Nicaea}, assuming a Gaussian covariance model for the power spectrum, as specified by equation (\ref{meth:gausspcov}).}
 \label{fig:nopca}
@@
 
-Figure \ref{fig:constraintsOm-w} shows the $1\sigma$ confidence contours on the $(\Omega_m,w)$ doublet calculated with equation (\ref{meth:parcovestimator}) after the PCA dimensionality reduction performed according to equation (\ref{meth:pcaprojection}), for a variety of choices $({\rm statistic},N_c)$.
+Figure \ref{fig:constraintsOm-w} shows the $1\sigma$ confidence contours on the $(\Omega_m,w)$ doublet calculated from equation (\ref{meth:parcovestimator}) after the PCA dimensionality reduction performed according to equation (\ref{meth:pcaprojection}), for a variety of choices of statistic and $N_c$.
 We also show the improvements on the confidence contours when combining different summary statistics after the corresponding dimensionality reductions have been performed.
-The forecast constraints on the $(\Omega_m,w,\sigma_8)$ parameter space for a variety of summary statistics are summarized in Table \ref{tbl:constraints}.
+The constraints in the $(\Omega_m,w,\sigma_8)$ parameter space for a variety of summary statistics are summarized in Tables \ref{tbl:constraints} (weak lensing only) and \ref{tbl:constraints-cmb} (with priors from Planck added).
 
 Figure \ref{fig:photozbias} shows the effect of ignoring photo-$z$ errors on parameter constraints.
-To evaluate this effect we construct different simulated observations, with and without photo-$z$ effects, and compare the results of the parameter fit according to equation (\ref{meth:parestimate}).
+To evaluate this effect we construct different simulated observations, with and without photo-$z$ errors, and compare the results of the parameter fit according to equation (\ref{meth:parestimate}).
 Using our simulation suite, we construct 20 simulated observations: the summary statistic in each observation is calculated by taking the mean of a random sample of $N_{\rm FOV}$ realizations of the summary statistic in the fiducial cosmology (randomly chosen among the ensemble of $N_r=16000$ that are available in the ensemble).
 The estimated covariance matrix $\bbh{C}$ is scaled by a factor $N_{\rm FOV}$ to take into account the construction process of the simulated observations.
-This procedure allows to forecast the results an LSST-like survey would obtain.
+This procedure allows us to forecast the results for an LSST-like survey would obtain.
 
@@
 \caption{$1\sigma$ confidence contours on the $(\Omega_m,w)$ parameter space, marginalized over $\sigma_8$, obtained using equation (\ref{meth:parcovestimator}).
-The covariance matrix $\bbh{C}$ and its inverse $\bbh{\Psi}$ have been obtained using $16000$ summary statistics realizations, and has been scaled by a factor $N_{\rm FOV}=1600$ to mimic the constraining power of an LSST-like survey.
+The covariance matrix $\bbh{C}$ and its inverse $\bbh{\Psi}$ have been computed from $16000$ summary statistics realizations, and have been scaled by a factor $N_{\rm FOV}=1600$ to mimic the constraining power of an LSST-sized survey.
 The thick line ellipses in the right panel refer to $(\Omega_m,w)$ obtained from the weak lensing statistics considered in this work, but subject to Planck priors as described in equation (\ref{meth:parcovestimator_cmb}).}
@@
 \begin{table*}
-\begin{tabular}{c|c|c|c|c|}
+\begin{tabular}{c|c|c|c|c|c|}
 \toprule
-                        \textbf{Statistic} & $\Delta \Omega_m$ & $\Delta w$ & $\Delta \sigma_8$ & $10^4\sqrt[3]{\rm Volume}$ $(\Omega_m,w,\sigma_8)$ \\ \hline \hline
+                                      \textbf{Statistic} & $\Delta \Omega_m$ & $\Delta w$ & $\Delta \sigma_8$ & $10^6{\rm Area} (\Omega_m,w)$ & $10^9{\rm Volume}$ $(\Omega_m,w,\sigma_8)$ \\ \hline \hline
 \midrule
-     Power spectrum ($\bar{z}_5$) &            0.0222 &     0.0286 &            0.0298 &                                                 86 \\
-      Power spectrum (tomography) &            0.0038 &     0.0213 &            0.0060 &                                                 42 \\
-              Peaks ($\bar{z}_5$) &            0.0049 &     0.0316 &            0.0050 &                                                 46 \\
-               Peaks (tomography) &            0.0042 &     0.0271 &            0.0043 &                                                 49 \\
-            Moments ($\bar{z}_5$) &            0.0027 &     0.0276 &            0.0026 &                                                 33 \\
-             Moments (tomography) &            0.0020 &     0.0214 &            0.0020 &                                                 28 \\ \hline \hline
-           Power spectrum + peaks &            0.0021 &     0.0153 &            0.0026 &                                                 29 \\
-         Power spectrum + moments &            0.0016 &     0.0150 &            0.0019 &                                                 24 \\
- Power spectrum + peaks + moments &            0.0015 &     0.0121 &            0.0018 &                                                 22 \\ \hline
+                   Power spectrum ($\bar{z}_5$) &            0.0222 &     0.0286 &            0.0298 &                           632 &                                        654 \\
+                          Power spectrum (tomo) &            0.0038 &     0.0213 &            0.0060 &                            76 &                                         74 \\
+                            Peaks ($\bar{z}_5$) &            0.0049 &     0.0316 &            0.0050 &                            98 &                                         99 \\
+                                   Peaks (tomo) &            0.0042 &     0.0271 &            0.0043 &                            93 &                                        122 \\
+                          Moments ($\bar{z}_5$) &            0.0027 &     0.0276 &            0.0026 &                            48 &                                         39 \\
+                                 Moments (tomo) &            0.0020 &     0.0214 &            0.0020 &                            28 &                                         21 \\ \hline \hline
+
+           Power spectrum + peaks ($\bar{z}_5$) &            0.0040 &     0.0209 &            0.0044 &                            58 &                                         53 \\
+                  Power spectrum + peaks (tomo) &            0.0021 &     0.0153 &            0.0026 &                            27 &                                         26 \\
+         Power spectrum + moments ($\bar{z}_5$) &            0.0023 &     0.0190 &            0.0025 &                            32 &                                         26 \\
+                Power spectrum + moments (tomo) &            0.0016 &     0.0150 &            0.0019 &                            18 &                                         14 \\
+ Power spectrum + peaks + moments ($\bar{z}_5$) &            0.0020 &     0.0127 &            0.0024 &                            21 &                                         17 \\
+        Power spectrum + peaks + moments (tomo) &            0.0015 &     0.0121 &            0.0018 &                            14 &                                         11 \\ \hline
 \bottomrule
@@
 Each column $(\Delta \Omega_m,\Delta w,\Delta \sigma_8)$ contains the 1$\sigma$ constraints on a particular parameter, marginalized over the other two.
-The last volume contains the volume of the $\sigma$ ellipsoid in $(\Omega_m,w,\sigma_8)$ space, calculated as $\sqrt{\det \bbh{\Sigma}}$.}
+The last two columns contain the respectively the area of the $(\Omega_m,w)$ 68\% confidence level ellipse (marginalized over $\sigma_8$) and the volume of the 68\% confidence level ellipsoid in $(\Omega_m,w,\sigma_8)$ space, both calculated as the square root of the determinant of the relevant $\bbh{\Sigma}$ minors.}
 \label{tbl:constraints}
@@
 \begin{table*}
-\begin{tabular}{c|c|c|c|c|}
+\begin{tabular}{c|c|c|c|c|c|}
 \toprule
-                        \textbf{Statistic} & $\Delta \Omega_m$ & $\Delta w$ & $\Delta \sigma_8$ & $10^4\sqrt[3]{\rm Volume}$ $(\Omega_m,w,\sigma_8)$ \\ \hline \hline
+                                      \textbf{Statistic} & $\Delta \Omega_m$ & $\Delta w$ & $\Delta \sigma_8$ & $10^6{\rm Area} (\Omega_m,w)$ & $10^9{\rm Volume}$ $(\Omega_m,w,\sigma_8)$ \\ \hline \hline
 \midrule
-     Power spectrum ($\bar{z}_5$) &            0.0076 &     0.0274 &            0.0084 &                                                 45 \\
-      Power spectrum (tomography) &            0.0028 &     0.0129 &            0.0035 &                                                 31 \\
-              Peaks ($\bar{z}_5$) &            0.0048 &     0.0237 &            0.0050 &                                                 38 \\
-               Peaks (tomography) &            0.0041 &     0.0204 &            0.0042 &                                                 41 \\
-            Moments ($\bar{z}_5$) &            0.0024 &     0.0172 &            0.0025 &                                                 27 \\
-             Moments (tomography) &            0.0019 &     0.0149 &            0.0020 &                                                 24 \\ \hline \hline
-           Power spectrum + peaks &            0.0021 &     0.0127 &            0.0025 &                                                 26 \\ 
-         Power spectrum + moments &            0.0015 &     0.0120 &            0.0018 &                                                 22 \\
- Power spectrum + peaks + moments &            0.0015 &     0.0104 &            0.0018 &                                                 21 \\ \hline
+                   Power spectrum ($\bar{z}_5$) &            0.0076 &     0.0274 &            0.0084 &                            94 &                                         96 \\
+                          Power spectrum (tomo) &            0.0028 &     0.0129 &            0.0035 &                            32 &                                         31 \\
+                            Peaks ($\bar{z}_5$) &            0.0048 &     0.0237 &            0.0050 &                            57 &                                         57 \\
+                                   Peaks (tomo) &            0.0041 &     0.0204 &            0.0042 &                            55 &                                         70 \\
+                          Moments ($\bar{z}_5$) &            0.0024 &     0.0172 &            0.0025 &                            27 &                                         21 \\
+                                 Moments (tomo) &            0.0019 &     0.0149 &            0.0020 &                            18 &                                         14 \\ \hline \hline
+
+           Power spectrum + peaks ($\bar{z}_5$) &            0.0040 &     0.0184 &            0.0043 &                            40 &                                         36 \\
+                  Power spectrum + peaks (tomo) &            0.0021 &     0.0127 &            0.0025 &                            20 &                                         19 \\
+         Power spectrum + moments ($\bar{z}_5$) &            0.0022 &     0.0145 &            0.0025 &                            22 &                                         17 \\
+                Power spectrum + moments (tomo) &            0.0015 &     0.0120 &            0.0018 &                            14 &                                         11 \\
+ Power spectrum + peaks + moments ($\bar{z}_5$) &            0.0019 &     0.0110 &            0.0023 &                            16 &                                         13 \\
+        Power spectrum + peaks + moments (tomo) &            0.0015 &     0.0104 &            0.0018 &                            12 &                                          9 \\ \hline
 \bottomrule
@@
 Each column $(\Delta \Omega_m,\Delta w,\Delta \sigma_8)$ contains the 1$\sigma$ constraints on a particular parameter, marginalized over the other two.
-The last volume contains the volume of the $\sigma$ ellipsoid in $(\Omega_m,w,\sigma_8)$ space, calculated as $\sqrt{\det \bbh{\Sigma}}$.}
+The last two columns contain the respectively the area of the $(\Omega_m,w)$ 68\% confidence level ellipse (marginalized over $\sigma_8$) and the volume of the 68\% confidence level ellipsoid in $(\Omega_m,w,\sigma_8)$ space, both calculated as the square root of the determinant of the relevant $\bbh{\Sigma}$ minors.}
 \label{tbl:constraints-cmb}
@@
 \caption{Distribution of parameter estimates in the $(\Omega_m,w)$ parameter space using the power spectrum (red), peak counts (green) and moments (blue) to fit 20 LSST-like simulated observations.
-The parameter deviations $(\delta\Omega_m,\delta w)$ are obtained comparing parameter estimates according to equation (\ref{meth:parestimate}) with and without photo-$z$ errors.
+The parameter deviations $(\delta\Omega_m,\delta w)$ are obtained comparing parameter estimates from equation (\ref{meth:parestimate}) with and without photo-$z$ errors.
 The colored squares and the ellipses correspond to respectively to the mean and $1\sigma$ level of the $(\delta\Omega_m,\delta w)$ distribution, assuming the latter is Gaussian.}
@@
 \section{Discussion}
+\label{sec:discussion}
+
 In this section we discuss our findings.
 Figure \ref{fig:pcacomponents} shows that our dimensionality reduction technique is robust.
-For all the summary statistics we consider, we notice that a plateau in the $w$ error is reached for a sufficient high number of principal components $N_c$.
+In particular, for all the summary statistics we consider, a plateau in the $w$ error is reached for a sufficient high number of principal components $N_c$.
 We also see that for single redshift statistics, this plateau is reached for $\sim 5$ components for the power spectrum and the moments, and $\sim 10$ components for the peak counts.
 Moreover, Figure \ref{fig:nopca} shows that, at least for the four highest redshift bins $\{\bar{z}_b: b\geq 2\}$, most of the cosmological information contained in the full (pre-PCA) summary statistic vector can be captured with a limited number of principal components $N_c<N_b$.
+The minimum number of components necessary to capture most of the available information increases when including redshift tomography, and can reach $\sim 30$ for the power spectrum and moments and $\sim 40$ for the peak counts.
 
-The number of components to consider increases when including redshift information, and can reach $\sim 30$ for the power spectrum and moments and $\sim 40$ for the peak counts.
-Figure \ref{fig:nopca} clearly that most of the cosmological information is concentrated in the last redshift bin.
-The use of redshift tomography tightens the $w$ constraints by approximately 33\% for the power spectrum, 16\% for the peaks and 25\% for the moments.
-Redshift tomography seems to play a vital role when constraining the $(\Omega_m,\sigma_8)$ doublet using the convergence power spectrum.
+Figure \ref{fig:nopca} also clearly shows that, when considering a single redshift bin and a single summary statistic, most of the information on $w$ is contained in the highest redshift galaxies.
+PCA does not seem to capture the whole information in the lowest redshift bin, even when enough components (enough for the plateau in Figure \ref{fig:pcacomponents} to be reached) are included.
+This can be attributed to the fact that PCA is not scale-invariant \citep{astroMLText}, because there is freedom in choosing the whitening scale in equation (\ref{meth:whitening}).
+Our choice of the whitening scale seems to affect significantly the first redshift bin, with the effect being mitigated on the highest redshift bins.
+The top left panel of Figure \ref{fig:nopca} also shows reasonable agreement between the results we obtain with our simulations and the ones we calculate with the analytical code NICAEA.
 
-In Figure \ref{fig:constraintsOm-w} we can see that peak counts and moments can significantly improve the constraints on $(\Omega_m,w)$ when combined with the power spectrum.
-Combining the peaks or the moments to the power spectrum improves the $w$ constraint by a factor of 1.7 while considering the three statistics together the error improves by an additional $30\%$.
-This shows that peaks and moments contain cosmological information that is not contained in the power spectrum, because a similar improvement cannot be obtained by simply increasing the number of PCA components in the power spectrum dimensionality reduction procedure.
+There are two possibilities for improving the constraints: the use of redshift tomography and the combination of different statistics.
+Table \ref{tbl:constraints} shows that the area and volume of the $(\Omega_m,w)$ ellipse and $(\Omega_m,w,\sigma_8)$ ellipsoid shrink by a factor of 8 when redshift tomography is added to the power spectrum, while the improvement is more modest for the remaining statistics (negligible for the peaks, and a factor of 2 for the moments).
+Combining the power spectrum and the peak counts in the highest redshift bin leads to a factor of 10 improvement in the $(\Omega_m,w)$ and $(\Omega_m,w,\sigma_8)$ 68\% confidence intervals, with tomography further shrinking the contours by an additional factor of 2.
+Combining the power spectrum and the moments in the highest redshift bin provides 20 times tighter constraints on $(\Omega_m,w)$ and $(\Omega_m,w,\sigma_8)$, with tomography yielding an additional factor of 2 improvement.
+Table \ref{tbl:constraints} also shows that power spectrum tomography can help breaking the degeneracy between $\Omega_m$ and $\sigma_8$.
+The same is not true for peaks and moments tomography, although combining these statistics with the power spectrum yields a factor of respectively 2 and 3 better constraints on $\Omega_m$ and $\sigma_8$.
 
-Figure \ref{fig:photozbias} quantifies the effect of uncorrected photo-$z$ errors on $(\Omega_m,w)$ constraints.
-Because the random nature of the observations, parameter values $\bbh{p}$ estimated from equation (\ref{meth:parestimate}) are affected by statistical fluctuations.
+Table \ref{tbl:constraints-cmb} shows that parameter priors on Planck yield a factor of 6 improvement on the $(\Omega_m,w)$ and $(\Omega_m,w,\sigma_8)$ 68\% confidence intervals, even when a single redshift bin is considered.
+When the Planck priors in equation (\ref{meth:parcovestimator_cmb}) are included, the improvements in constraining power when adding redshift tomography or combining different statistics are more moderate, with power spectrum tomography yielding a factor of 3 improvement, peaks tomography yielding no improvement and moments tomography yielding a factor 1.5 improvement.
+
+Figure \ref{fig:constraintsOm-w} shows that peaks and moments contain cosmological information that is not contained in the power spectrum, because a similar improvement cannot be obtained by simply increasing the number of PCA components in the power spectrum dimensionality reduction procedure.
+This is consistent with previous work (see for example \citep{CFHTMink})
+
+Figure \ref{fig:photozbias} quantifies the effect of uncorrected photo-$z$ errors on the $(\Omega_m,w)$ constraints.
+Because the stochastic nature of the observations, parameter values $\bbh{p}$ estimated from equation (\ref{meth:parestimate}) are affected by statistical fluctuations.
 In Figure \ref{fig:photozbias} we show 20 random draws from the probability distribution of $\delta \bbh{p}=\bbh{p}_{\rm photo-z}-\bbh{p}_{\rm no-photo-z}$.
 We can conclude that the $\bbh{p}$ estimator is biased if $\langle\delta\bbh{p}\rangle\neq 0$.
-Figure \ref{fig:photozbias} clearly show that photo-$z$ errors cause parameter biases at more than $1\sigma$ significance level when using the power spectrum and the moments, while no bias is observed for the peak count statistic within the constraining accuracy.
-We also observe that photo-$z$ errors bias the constraints in different directions, leaving open possibilities for bias self--calibration techniques.
+Figure \ref{fig:photozbias} clearly show that photo-$z$ errors cause parameter biases at more than $1\sigma$ significance level when using the power spectrum and the moments, while no bias is observed for the peak count statistic within its 68\% confidence region.
+We also observe that photo-$z$ errors bias the constraints in slightly different directions, leaving open the possibility of identifying and correcting this bias through self-calibration techniques.
 
@@
 \section{Conclusions}
-In this work we study cosmological parameter constraints forecasts for an LSST-like galaxy survey using the convergence power spectrum and a range of non--Gaussian statistics.
-We make use of redshift tomography to improve the constraints from their single redshift counterparts.
+\label{sec:conclusions}
+
+In this work we have studied cosmological parameter constraint forecasts for an LSST-like galaxy survey using the convergence power spectrum and a range of non-Gaussian statistics.
+We make use of redshift tomography to improve the constraints relative to their single-redshift counterparts.
 We also investigate the effects of uncorrected photo-$z$ systematic effects on the inferred cosmology.
-We find that:
+Our main findings can be summarized as follows:
 \begin{itemize}
-	\item Principal Component analysis is a robust technique to keep the dimensionality of the parameter space under control and avoid the numerical pitfalls explained in \citep{Taylor12,DodelsonSchneider13,Taylor14} and more recently \citep{PetriVariance}.
-In particular we find that only a few components are necessary to characterize the cosmological information content in single redshift statistics, while more components are necessary when tomography is included.
+
+	\item Principal Component analysis is a robust technique to keep the dimensionality of the parameter space under control and to avoid the numerical pitfalls explained in \citep{Taylor12,DodelsonSchneider13,Taylor14} and more recently in \citep{PetriVariance}.
+In particular, we find that only a few components (5-10) are necessary to characterize the cosmological information content in single redshift statistics, while more components (30-40) are necessary when tomography is included.
 Nevertheless we find that the number of required components $N_c$ is significantly smaller than the full summary statistic space dimensionality before performing PCA.
-	\item Most of the cosmological information on $w$ is contained in high redshift galaxies, with tomography improving constraints by only a few $10\%$.
-The advantage using tomography is much bigger when constraining $(\Omega_m,\sigma_8)$ using the convergence power spectrum.
-	\item Peak counts and moments can significantly improve $(\Omega_m,w)$ parameter constraints when used in combination with the power spectrum.
-	\item Uncorrected photo-$z$ systematics can bias parameter constraints obtained from the power spectrum and the moments, but in different parameter directions, leaving open windows for self-calibration
+
+	\item When considering a single redshift bin, most of the cosmological information on $w$ is contained in high redshift galaxies.
+Constraints can be improved with redshift tomography or combining different non-Gaussian statistics with the power spectrum.
+The improvement originating from the combination of different statistics is attributed to the complementary information that non-Gaussian statistics carry, as a similar improvement cannot be obtained simply increasing the number of PCA components in a single statistic.
+
+	\item Redshift tomography on the power spectrum shrinks the $(\Omega_m,w)$ 68\% confidence ellipse by a factor of 8; combining the peak counts with the power spectrum in the highest redshift bin leads to a factor of 10 better constraints, while adding the moments instead reduces the size of the $(\Omega_m,w)$ ellipse by a factor of 20.
+When redshift tomography is added on top of these statistics combinations, an additional factor of 2 improvement is observed.
+Constraint improvements adding redshift tomography and combinations of different statistics are less important when priors from CMB experiments are included in the analysis.
+
+	\item Uncorrected photo-$z$ systematics can bias parameter constraints obtained from the power spectrum and the moments, but in slightly different parameter directions, leaving open possibilities of somewhat eliminating this bias via self-calibration.
+
 \end{itemize}
+
+This work emphasizes the advantage of deep galaxy surveys such as LSST, which have access to shape information of high redshift galaxies and provide valuable cosmological information on the dark energy equation of state.
+We also stress the fact that redshift tomography can in some cases provide more stringent constraints on parameters but, for this technique to be viable, accurate knowledge of galaxy redshifts is necessary.
+Future work needs to address the requirements for photometric measurements accuracy when using non-Gaussian statistics, as well as the self calibration techniques that can be used when different summary statistics are available in addition to the power spectrum.
 
@@
 
+\textbf{To Morgan's attention: the bulk of the simulations were performed at NERSC, I do not know under what terms the allocation was granted though. Can you fill the appropriate details?}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-04-25 code/library/featureDB.py

@@ -534,7 +534,7 @@ class FisherDatabase(Database):
 			for n in range(5):
 				b,p = self.query_parameter_simple(feature+"_z{0}".format(n),table_name,parameter)
 				axes[nfeat].plot(b,np.sqrt(p),label=r"$z\in[{0:.2f},{1:.2f}]$".format(*self.z_bins[n]))
-			axes[nfeat].set_title(r"${\rm " + feature.replace("_pca","").replace("_","\,\,") + r"}$",fontsize=22)
+			axes[nfeat].set_title(r"${\rm " + feature.replace("_pca","").replace("_","\,\,") + r"}$",fontsize=30)
 
 		#Axes labels
 		for ax in axes:

### 2016-04-25 photoz_paper/Figures/generate.py

@@ -87,6 +87,9 @@ def galdistr(cmd_args,fontsize=22):
 	ax.set_ylabel(r"$N_g(z)$",fontsize=fontsize)
 	ax.legend()
 
+	#Ticks
+	ax.tick_params(axis="both",which="major",labelsize=fontsize)
+
 	#Save figure
 	fig.savefig("galdistr."+cmd_args.type)
 
@@ -244,6 +247,9 @@ def pca_components(cmd_args,db_name="data/fisher/constraints_combine.sqlite",fea
 
 	#Labels
 	axes[0].set_ylabel(r"$\Delta$"+par2label[parameter],fontsize=fontsize)
+
+	#Ticks
+	axes[0].tick_params(axis="both",which="major",labelsize=fontsize)
 
 	#Save figure
 	fig.savefig("{0}_{1}.".format(parameter,feature_label)+cmd_args.type)
@@ -489,30 +495,34 @@ def bias_vs_sigma(cmd_args,db_name="data/fisher/constraints_photoz.sqlite",param
 rows = {
 
 "ps5" : {"name" : "power_spectrum_pca_z4" , "table_name" : "pcov_noise" ,"bins" : 14 , "label" : r"Power spectrum ($\bar{z}_5$)"},
-"ps-tomo" : {"name" : "power_spectrum_pca" , "table_name" : "pcov_noise" , "bins" : 70 , "label" : "Power spectrum (tomography)"},
+"ps-tomo" : {"name" : "power_spectrum_pca" , "table_name" : "pcov_noise" , "bins" : 70 , "label" : "Power spectrum (tomo)"},
 "peaks5" : {"name" : "peaks_pca_z4" , "table_name" : "pcov_noise" , "bins" : 27 , "label" : r"Peaks ($\bar{z}_5$)"},
-"peaks-tomo" : {"name" : "peaks_pca" , "table_name" : "pcov_noise" , "bins" : 70 , "label" : "Peaks (tomography)"},
+"peaks-tomo" : {"name" : "peaks_pca" , "table_name" : "pcov_noise" , "bins" : 70 , "label" : "Peaks (tomo)"},
 "moments5" : {"name" : "moments_pca_z4" , "table_name" : "pcov_noise" , "bins" : 9 , "label" : r"Moments ($\bar{z}_5$)"},
[…]

### 2016-04-26 photoz_paper/paper.tex
added acknowledgements

@@
 The covariance matrix $\bbh{C}$ and its inverse $\bbh{\Psi}$ have been computed from $16000$ summary statistics realizations, and have been scaled by a factor $N_{\rm FOV}=1600$ to mimic the constraining power of an LSST-sized survey.
-The thick line ellipses in the right panel refer to $(\Omega_m,w)$ obtained from the weak lensing statistics considered in this work, but subject to Planck priors as described in equation (\ref{meth:parcovestimator_cmb}).}
+The thick line ellipses in the right panel refer to $(\Omega_m,w)$ obtained from the weak lensing statistics considered in this work, but subject to Planck priors as described in equation (\ref{meth:parcovestimator_cmb}).
+The thin solid lines in the left and right panels are the same.}
 \label{fig:constraintsOm-w}
@@
 
-We thank Colin Hill for useful discussions. The simulations in this work
-were performed at the NSF XSEDE facility, supported by grant number
+We thank Colin Hill and Licia Verde for useful discussions. We also thank Martin Kilbinger, Lloyd Knox and Hu Zhan for comments on an earlier version of this manuscript.
+The simulations in this work were performed at the NSF XSEDE facility, supported by grant number
 ACI-1053575, and at the New York Center for Computational Sciences, a

### 2016-05-02 photoz_paper/paper.tex
incorporated latest edits

@@
 
-\title{Cosmology with weak lensing photometric surveys: constraints with redshift tomography of non--Gaussian statistics}
+\title{Cosmology with photometric weak lensing surveys: constraints with redshift tomography of convergence peaks and moments}
 
@@
 \begin{abstract}
-Weak gravitational lensing is becoming a mature technique to constrain cosmological parameters, and future surveys will be able to constrain the dark energy equation of state $w$.
+Weak gravitational lensing is becoming a mature technique for constraining cosmological parameters, and future surveys will be able to constrain the dark energy equation of state $w$.
 When analyzing galaxy surveys, redshift information has proven to be a valuable addition to angular shear correlations.
-We forecast parameter constraints on the triplet $(\Omega_m,w,\sigma_8)$ for an LSST like galaxy photometric survey, using tomography of the shear-shear power spectrum, convergence peak counts and higher convergence moments.
-We find that redshift tomography with the power spectrum shrinks the $1\sigma$ confidence interval area in $(\Omega_m,w)$ space by a factor of 8 with respect to the case of a single redshift bin.
+We forecast parameter constraints on the triplet $(\Omega_m,w,\sigma_8)$ for an LSST-like galaxy photometric survey, using tomography of the shear-shear power spectrum, convergence peak counts and higher convergence moments.
+We find that redshift tomography with the power spectrum shrinks the $1\sigma$ confidence interval area in $(\Omega_m,w)$ space by a factor of 8 with respect to the case of the single highest redshift bin.
 We also find that adding non-Gaussian information from the peak counts and higher moments of the convergence further shrinks the constrained area in $(\Omega_m,w)$ by a factor of respectively 3 and 4.
-When we add parameter priors from Planck to our analysis, we find that the improvements using tomography and non-Gaussian statistics are less important, spanning a factor of 3 at most using power spectrum tomography, but only improving by 30\% when adding the peak counts.
+When we add parameter priors from Planck to our analysis, tomography improves power spectrum constraints by a factor of 3.
+Adding moments improves by an additional factor of 2, and  adding both moments and peaks improves by almost a factor of 3 over power spectrum tomography alone.
 We evaluate the effect of uncorrected photometric redshift systematics on parameter constraints.
-We find that different statistics lead to different bias directions in parameter space, suggesting the possibility of eliminating this bias via self--calibration.
+We find that different statistics lead to different bias directions in parameter space, suggesting the possibility of eliminating this bias via self-calibration.
 \end{abstract}
@@
 The measured galaxy ellipticity $\pmb{\epsilon}$ is an estimate of the cosmic shear $\pmb{\gamma}$ due to large scale structure if the non--lensed galaxy shape is a circle.
-Because the galaxies have intrinsic non circular shapes, the measured galaxy ellipticity $\pmb{\epsilon}_{\rm m}$ is the sum of a cosmic shear term and the intrinsic ellipticity (galaxy shape noise) \citep{wlreview}
+Because the galaxies have intrinsic noncircular shapes, the measured galaxy ellipticity $\pmb{\epsilon}_{\rm m}$ is the sum of a cosmic shear term and the intrinsic ellipticity (galaxy shape noise) \citep{wlreview}
 \begin{equation}
@@
 
-The study of photometric redshift errors is an active subject of research, and includes investigation of techniques such as spectroscopic calibration, catastrophic errors and cross-correlation techniques that we do not explore in this work (see for example \citep{HuTomo} for a more thorough discussion).
+The study of photometric redshift errors is an active subject of research, and includes investigation of techniques such as spectroscopic calibration, catastrophic errors and cross-correlation techniques that we do not explore in this work (see for example \citep{HuTomo,LSSTSciBook} for a more thorough discussion).
 We model the effect of photo-$z$ errors as a constant bias term $b_{\rm ph}(z_s)$ plus a random Gaussian component with variance $\sigma_{\rm ph}(z_s)$,
@@
 We apply a Principal Component Analysis (see \citep{astroMLText} for example) to reduce the dimensionality of our summary statistics while preserving the cosmological information content.
-The model statistic $\bb{d}(\bb{p})$ can be regarded as a$P\times N_b$ matrix $d_{pi}$.
+The model statistic $\bb{d}(\bb{p})$ can be regarded as a $P\times N_b$ matrix $d_{pi}$.
 Consider the whitened model matrix
@@
 \subsection{Priors from CMB experiments}
-In this paragraph we describe how we included prior knowledge of cosmological parameters from previous Cosmic Microwave Background (CMB) observations, such as Planck \citep{PlanckCosmo}.
+In this section we describe how we included prior knowledge of cosmological parameters from previous Cosmic Microwave Background (CMB) observations, such as Planck \citep{PlanckCosmo}.
 CMB experiments provide tight constraints on $(\Omega_m,\sigma_8)$, but they are not sensitive to dark energy parameters such as $w$.
@@
 To evaluate this effect we construct different simulated observations, with and without photo-$z$ errors, and compare the results of the parameter fit according to equation (\ref{meth:parestimate}).
-Using our simulation suite, we construct 20 simulated observations: the summary statistic in each observation is calculated by taking the mean of a random sample of $N_{\rm FOV}$ realizations of the summary statistic in the fiducial cosmology (randomly chosen among the ensemble of $N_r=16000$ that are available in the ensemble).
+Using our simulation suite, we construct 20 simulated observations: the summary statistic in each observation is calculated by taking the mean of a random sample of $N_{\rm FOV}=1600$ realizations of the summary statistic in the fiducial cosmology (randomly chosen among the ensemble of $N_r=16000$ that are available in the ensemble).
 The estimated covariance matrix $\bbh{C}$ is scaled by a factor $N_{\rm FOV}$ to take into account the construction process of the simulated observations.
-This procedure allows us to forecast the results for an LSST-like survey would obtain.
+This procedure allows us to forecast the results an LSST-like survey would obtain.
 
@@
 \includegraphics[scale=0.3]{Figures/constraints_Om-w_lensing_cmb.eps}
-\caption{$1\sigma$ confidence contours on the $(\Omega_m,w)$ parameter space, marginalized over $\sigma_8$, obtained using equation (\ref{meth:parcovestimator}).
+\caption{$1\sigma$ tomographic constraints on the $(\Omega_m,w)$ parameter space, marginalized over $\sigma_8$, obtained using equation (\ref{meth:parcovestimator}).
 The covariance matrix $\bbh{C}$ and its inverse $\bbh{\Psi}$ have been computed from $16000$ summary statistics realizations, and have been scaled by a factor $N_{\rm FOV}=1600$ to mimic the constraining power of an LSST-sized survey.
@@
 Each column $(\Delta \Omega_m,\Delta w,\Delta \sigma_8)$ contains the 1$\sigma$ constraints on a particular parameter, marginalized over the other two.
-The last two columns contain the respectively the area of the $(\Omega_m,w)$ 68\% confidence level ellipse (marginalized over $\sigma_8$) and the volume of the 68\% confidence level ellipsoid in $(\Omega_m,w,\sigma_8)$ space, both calculated as the square root of the determinant of the relevant $\bbh{\Sigma}$ minors.}
+The last two columns contain respectively the area of the $(\Omega_m,w)$ 68\% confidence level ellipse (marginalized over $\sigma_8$) and the volume of the 68\% confidence level ellipsoid in $(\Omega_m,w,\sigma_8)$ space, both calculated as the square root of the determinant of the relevant $\bbh{\Sigma}$ minors.}
 \label{tbl:constraints}
@@
 Each column $(\Delta \Omega_m,\Delta w,\Delta \sigma_8)$ contains the 1$\sigma$ constraints on a particular parameter, marginalized over the other two.
-The last two columns contain the respectively the area of the $(\Omega_m,w)$ 68\% confidence level ellipse (marginalized over $\sigma_8$) and the volume of the 68\% confidence level ellipsoid in $(\Omega_m,w,\sigma_8)$ space, both calculated as the square root of the determinant of the relevant $\bbh{\Sigma}$ minors.}
+The last two columns contain respectively the area of the $(\Omega_m,w)$ 68\% confidence level ellipse (marginalized over $\sigma_8$) and the volume of the 68\% confidence level ellipsoid in $(\Omega_m,w,\sigma_8)$ space, both calculated as the square root of the determinant of the relevant $\bbh{\Sigma}$ minors.}
 \label{tbl:constraints-cmb}
@@
 Figure \ref{fig:nopca} also clearly shows that, when considering a single redshift bin and a single summary statistic, most of the information on $w$ is contained in the highest redshift galaxies.
-PCA does not seem to capture the whole information in the lowest redshift bin, even when enough components (enough for the plateau in Figure \ref{fig:pcacomponents} to be reached) are included.
+PCA does not seem to capture all the information in the lowest redshift bin, even when enough components are included to reach the plateau in Figure \ref{fig:pcacomponents}.
 This can be attributed to the fact that PCA is not scale-invariant \citep{astroMLText}, because there is freedom in choosing the whitening scale in equation (\ref{meth:whitening}).
-Our choice of the whitening scale seems to affect significantly the first redshift bin, with the effect being mitigated on the highest redshift bins.
+Our choice of the whitening scale seems to affect significantly the first redshift bin, with the effect being mitigated for the highest redshift bins.
 The top left panel of Figure \ref{fig:nopca} also shows reasonable agreement between the results we obtain with our simulations and the ones we calculate with the analytical code NICAEA.
@@
 
-Table \ref{tbl:constraints-cmb} shows that parameter priors on Planck yield a factor of 6 improvement on the $(\Omega_m,w)$ and $(\Omega_m,w,\sigma_8)$ 68\% confidence intervals, even when a single redshift bin is considered.
-When the Planck priors in equation (\ref{meth:parcovestimator_cmb}) are included, the improvements in constraining power when adding redshift tomography or combining different statistics are more moderate, with power spectrum tomography yielding a factor of 3 improvement, peaks tomography yielding no improvement and moments tomography yielding a factor 1.5 improvement.
+Table \ref{tbl:constraints-cmb} shows that parameter priors from Planck yield a factor of 6 improvement on the $(\Omega_m,w)$ and $(\Omega_m,w,\sigma_8)$ 68\% confidence intervals, even when a single redshift bin is considered.
+When the Planck priors in equation (\ref{meth:parcovestimator_cmb}) are included, the improvements in constraints when adding redshift tomography or combining different statistics are more moderate.
+Tomography improves power spectrum constraints by a factor of 3.
+Adding moments improves by an additional factor of 2, and  adding both moments and peaks improves by almost a factor of 3 over power spectrum tomography alone.
 
@@
 Constraints can be improved with redshift tomography or combining different non-Gaussian statistics with the power spectrum.
-The improvement originating from the combination of different statistics is attributed to the complementary information that non-Gaussian statistics carry, as a similar improvement cannot be obtained simply increasing the number of PCA components in a single statistic.
+The improvement originating from the combination of different statistics is attributed to the complementary information that non-Gaussian statistics carry, as a similar improvement cannot be obtained from a single statistic.
 
@@
 When redshift tomography is added on top of these statistics combinations, an additional factor of 2 improvement is observed.
-Constraint improvements adding redshift tomography and combinations of different statistics are less important when priors from CMB experiments are included in the analysis.
+Constraint improvements adding redshift tomography and combinations of different statistics are less dramatic when priors from CMB experiments are included in the analysis.
 
@@
 
-This work emphasizes the advantage of deep galaxy surveys such as LSST, which have access to shape information of high redshift galaxies and provide valuable cosmological information on the dark energy equation of state.
+This work explores the advantage of deep galaxy surveys such as LSST, which have access to shape and redshift information of high $z$ galaxies and provide valuable cosmological information on the dark energy equation of state.
 We also stress the fact that redshift tomography can in some cases provide more stringent constraints on parameters but, for this technique to be viable, accurate knowledge of galaxy redshifts is necessary.
@@
 
-We thank Colin Hill and Licia Verde for useful discussions. We also thank Martin Kilbinger, Lloyd Knox and Hu Zhan for comments on an earlier version of this manuscript.
-The simulations in this work were performed at the NSF XSEDE facility, supported by grant number
+Most of the calculations were performed at National Energy Research Scientific Computing Center (NERSC).
+We thank the LSST Dark Energy Science Collaboration (DESC) for the allocation of time, and for many useful discussions.
+We thank Hu Zhan, Salman Habib, Jeffrey Newman, Deborah Bard, and Peter Nugent for technical help.
+We thank Colin Hill and Licia Verde for useful discussions.
+We also thank Martin Kilbinger and Lloyd Knox for comments on an earlier version of this manuscript.
+Part of the simulations in this work were also performed at the NSF XSEDE facility, supported by grant number
 ACI-1053575, and at the New York Center for Computational Sciences, a
@@
 
-\textbf{To Morgan's attention: the bulk of the simulations were performed at NERSC, I do not know under what terms the allocation was granted though. Can you fill the appropriate details?}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-05-02 photoz_paper/paper.tex
update abstract/acknowledgements

@@
 \begin{abstract}
-Weak gravitational lensing is becoming a mature technique for constraining cosmological parameters, and future surveys will be able to constrain the dark energy equation of state $w$.
-When analyzing galaxy surveys, redshift information has proven to be a valuable addition to angular shear correlations.
-We forecast parameter constraints on the triplet $(\Omega_m,w,\sigma_8)$ for an LSST-like galaxy photometric survey, using tomography of the shear-shear power spectrum, convergence peak counts and higher convergence moments.
-We find that redshift tomography with the power spectrum shrinks the $1\sigma$ confidence interval area in $(\Omega_m,w)$ space by a factor of 8 with respect to the case of the single highest redshift bin.
-We also find that adding non-Gaussian information from the peak counts and higher moments of the convergence further shrinks the constrained area in $(\Omega_m,w)$ by a factor of respectively 3 and 4.
-When we add parameter priors from Planck to our analysis, tomography improves power spectrum constraints by a factor of 3.
-Adding moments improves by an additional factor of 2, and  adding both moments and peaks improves by almost a factor of 3 over power spectrum tomography alone.
-We evaluate the effect of uncorrected photometric redshift systematics on parameter constraints.
-We find that different statistics lead to different bias directions in parameter space, suggesting the possibility of eliminating this bias via self-calibration.
+Weak gravitational lensing is becoming a mature technique for
+constraining cosmological parameters, and future surveys will be able
+to constrain the dark energy equation of state $w$. When analyzing
+galaxy surveys, redshift information has proven to be a valuable
+addition to angular shear correlations. We forecast parameter
+constraints on the triplet $(\Omega_m,w,\sigma_8)$ for an LSST-like
+photometric galaxy survey, using tomography of the shear-shear power
+spectrum, convergence peak counts and higher convergence moments. We
+find that redshift tomography with the power spectrum reduces the area
+of the $1\sigma$ confidence interval in $(\Omega_m,w)$ space by a
+factor of 8 with respect to the case of the single highest redshift
+bin. We also find that adding non-Gaussian information from the peak
+counts and higher-order moments of the convergence field and its
+spatial derivatives further reduces the constrained area in
+$(\Omega_m,w)$ by a factor of 3 and 4, respectively. When we add
+cosmic microwave background parameter priors from Planck to our
+analysis, tomography improves power spectrum constraints by a factor
+of 3. Adding moments yields an improvement by an additional factor of
+2, and adding both moments and peaks improves by almost a factor of 3,
+over power spectrum tomography alone. We evaluate the effect of
+uncorrected systematic photometric redshift errors on the parameter
+constraints. We find that different statistics lead to different bias
+directions in parameter space, suggesting the possibility of
+eliminating this bias via self-calibration. 
 \end{abstract}
@@
 
+We thank Hu Zhan, Salman Habib, Jeffrey Newman, Colin Hill and Licia Verde for useful discussions.
+We also thank Martin Kilbinger and Lloyd Knox for comments on an earlier version of this manuscript.
 Most of the calculations were performed at National Energy Research Scientific Computing Center (NERSC).
 We thank the LSST Dark Energy Science Collaboration (DESC) for the allocation of time, and for many useful discussions.
-We thank Hu Zhan, Salman Habib, Jeffrey Newman, Deborah Bard, and Peter Nugent for technical help.
-We thank Colin Hill and Licia Verde for useful discussions.
-We also thank Martin Kilbinger and Lloyd Knox for comments on an earlier version of this manuscript.
 Part of the simulations in this work were also performed at the NSF XSEDE facility, supported by grant number
@@
 work was supported in part by the U.S. Department of Energy under
-Contract Nos. DE-AC02-98CH10886 and DE-SC0012704, and by the NSF Grant
+Contract No. DE-SC00112704, and by the NSF Grant
 No. AST-1210877 (to Z.H.) and by the Research Opportunities and

### 2016-05-03 code/library/driver_mpi.py
choose table from which to read the emulator

@@ -228,6 +228,13 @@ def cosmo_constraints(batch,specs,settings=default_settings):
 		else:
 			features_dbname = getattr(settings,feature).dbname 
 
+		#Models and means table to build the emulator
+		if "models_table" in specs:
+			getattr(settings,feature).model_table = models_table
+
+		if "means_table" in specs:
+			getattr(settings,feature).emulator_table = means_table
+
 		#Query the database
 		feature_dbfile = os.path.join(batch.storage,features_dbname)
 		print("")

### 2016-05-03 code/library/driver_mpi.py
toggle derivative precision

@@ -230,10 +230,13 @@ def cosmo_constraints(batch,specs,settings=default_settings):
 
 		#Models and means table to build the emulator
 		if "models_table" in specs:
-			getattr(settings,feature).model_table = models_table
+			getattr(settings,feature).model_table = specs["models_table"]
 
 		if "means_table" in specs:
-			getattr(settings,feature).emulator_table = means_table
+			getattr(settings,feature).emulator_table = specs["means_table"]
+
+		if "derivative_precision" in specs:
+			settings.derivative_precision = specs["derivative_precision"]
 
 		#Query the database
 		feature_dbfile = os.path.join(batch.storage,features_dbname)

### 2016-05-03 photoz_paper/paper.tex
last edits before submission

@@
 This means that the parameter error bar estimate (\ref{meth:covdegradation}) is too conservative if $N_b/N_r$ is of order unity.
-This could be likely the case in our analysis because of the inclusion of tomography information.
+This could be the case with the inclusion of tomography information.
 If we bin the single redshift summary statistic with $N_{\rm st}$ intervals, and consider $N_z$ redshift bins, this can lead to a summary statistic vector of size $N_b = O(N_{\rm st}N_z^2)$ for the power spectrum and $N_b = O(N_{\rm st}N_z)$ for the remaining statistics.
@@
 We assume that only summary statistic projections on the first $N_c$ basis vectors contain relevant cosmological information, where $N_c<N_b$ is a number that has to be determined from the simulations.
-Let $\bb{R}(N_c)$ be a matrix made of the first $N_c$ rows of $\bb{R}$ (we assume that the singular values $\Lambda_i$ are sorted).
+Let $\bb{R}(N_c)$ be a matrix made of the first $N_c$ rows of $\bb{R}$ (we assume that the singular values $\Lambda_i$ are sorted from highest to lowest).
 We define the PCA projection of a summary statistic $\bbh{d}$ on $N_c$ principal components as
@@
 Through the above procedure, we hope to capture the cosmological information contained in $\bbh{d}$ by projecting it on the $N_c<N_b$ principal components that vary the most with cosmology parameters.
-In the next section we outline the main results of this work.
 
@@
 \subsection{Priors from CMB experiments}
-In this section we describe how we included prior knowledge of cosmological parameters from previous Cosmic Microwave Background (CMB) observations, such as Planck \citep{PlanckCosmo}.
+In this paragraph we describe how we included prior knowledge of cosmological parameters from previous Cosmic Microwave Background (CMB) observations, such as Planck \citep{PlanckCosmo}.
 CMB experiments provide tight constraints on $(\Omega_m,\sigma_8)$, but they are not sensitive to dark energy parameters such as $w$.

### 2016-05-03 photoz_paper/paper.tex
use eps instead of pdf

@@
 \begin{figure}
-\includegraphics[scale=0.3]{Figures/galdistr.pdf}
+\includegraphics[scale=0.3]{Figures/galdistr.eps}
 \caption{Galaxy distribution assumed throughout this work (see equation (\ref{meth:galdistr})), along with the choice of the redshift bins $\bar{z}_b$.
@@
 \begin{figure*}
-\includegraphics[scale=0.3]{Figures/w_power_spectrum_no_pca.pdf}
-\includegraphics[scale=0.3]{Figures/w_peaks_no_pca.pdf}
-\includegraphics[scale=0.3]{Figures/w_moments_no_pca.pdf}
-\caption{Comparison between single-redshift $w$ constraints (marginalized over $\Omega_m$ and $\sigma_8$) obtained without PCA (gray shaded bars) and with PCA (colored bars) as a function of the redshift bin $\bar{z}_b$.
+\includegraphics[scale=0.3]{Figures/w_power_spectrum_no_pca.eps}
+\includegraphics[scale=0.3]{Figures/w_peaks_no_pca.eps}
+\includegraphics[scale=0.3]{Figures/w_moments_no_pca.eps}
+\caption{Comparison between single-redshift $w$ constraints (marginalized over $\Omega_m$ and $\sigma_8$) obtained without PCA (black bars) and with PCA (colored bars) as a function of the redshift bin $\bar{z}_b$.
 We show constraints obtained from the power spectrum (top left), peak counts (top right) and moments (bottom).

### 2016-05-03 photoz_paper/Figures/generate.py

@@ -152,7 +152,7 @@ def constraints_no_pca(cmd_args,db_name="data/fisher/constraints_combine.sqlite"
 		#Plot feature without PCA
 		var_feature = var_db[var_db["feature_label"].str.contains(feature)]["{0}-{0}".format(parameter)].values
 		var_highest_z = var_feature[-1]
-		ax.bar(range(len(var_feature)),np.sqrt(var_feature),width=1,color=base_color,label=r"${\rm No}$ ${\rm PCA}$",alpha=0.3)
+		ax.bar(range(len(var_feature)),np.sqrt(var_feature),width=1,fill=False,edgecolor=base_color,label=r"${\rm No}$ ${\rm PCA}$",alpha=0.3)
 
 		#Plot features with PCA
 		for n,nc in enumerate(pca_components):
@@ -176,7 +176,7 @@ def constraints_no_pca(cmd_args,db_name="data/fisher/constraints_combine.sqlite"
 	ax.legend(prop={"size":25})
 
 	#Title
-	ax.set_title(title,fontsize=fontsize)
+	ax.set_title(title,fontsize=30)
 
 	#Save the figure
 	fig.savefig("{0}_{1}_no_pca.{2}".format(parameter,feature,cmd_args.type))
@@ -209,7 +209,7 @@ def sims_vs_nicaea(cmd_args,db_name="data/fisher/constraints_combine.sqlite",fea
 		#Query parameter variance obtained with the simulations
 		var_db = db.query('SELECT "{0}-{0}",feature_label FROM pcov_noise_no_pca'.format(parameter))
 		var_feature = var_db[var_db["feature_label"].str.contains(feature)]["{0}-{0}".format(parameter)].values
-		ax.bar(range(len(var_feature)),np.sqrt(var_feature),width=1,color="black",label=r"${\rm No}$ ${\rm PCA}$",alpha=0.3)
+		ax.bar(range(len(var_feature)),np.sqrt(var_feature),width=1,fill=False,edgecolor="black",label=r"${\rm No}$ ${\rm PCA}$",alpha=0.3)
 
 		#Overlay the results obtained with PCA
 		var_db = db.query('SELECT "{0}-{0}",feature_label FROM pcov_noise WHERE bins=10'.format(parameter))
[…]

### 2016-05-03 photoz_paper/Figures/generate.py
fix labels

@@ -163,7 +163,7 @@ def constraints_no_pca(cmd_args,db_name="data/fisher/constraints_combine.sqlite"
 		#Plot tomographic constraint with the maximum number of pca components
 		var_db = db.query('SELECT "{0}-{0}",bins,feature_label FROM pcov_noise'.format(parameter))
 		var_feature_tomo,nc,label = var_db.query("feature_label=='{0}'".format(feature+"_pca")).tail(1).values.flat
-		ax.bar(5,np.sqrt(var_feature_tomo),width=1,fill=False,edgecolor=tomo_color,label=r"$(N_c={0})$".format(int(nc)))
+		ax.bar(5,np.sqrt(var_feature_tomo),width=1,fill=False,edgecolor=tomo_color,label=r"$N_c={0}$".format(int(nc)))
 
 		#Put a percent value on the last bar of the graph
 		#ax.text(5.5,np.sqrt(var_highest_z),r"$-{0}\%$".format(int(100*(np.sqrt(var_highest_z/var_feature_tomo)-1))),fontsize=fontsize)

### 2016-09-22 photoz_paper/paper.tex
implemented referee comments

@@
 In this work we concentrate on the constraining power of a subset of non-Gaussian statistics, combined with redshift tomography in an LSST-like survey.
+{\bf \color{red} \citep{MartinetPeaksTomo} investigated the cosmological constraining power of shear peaks tomography}.
 Previous work on redshift tomography with weak lensing Minkowski functionals is also present in the literature \citep{MinkJan}.
@@
 The simulations have a comoving box size of $L_b=260\,{\rm Mpc}/h$ and contain $512^3$ dark matter particles, which correspond to a mass resolution of $M_p\approx 10^{10}M_{\rm sun}$ per particle.
+
+{\bf \color{red} The largest mode observed in our $N$--body simulations corresponds to a wavenumber of $k_b\approx1/L_b\approx 0.004 h{\rm Mpc}^{-1}$.
+For the sake of recovering cosmological information from WL, this limitation does not create a concern, as several authors (see \citep{FangHaiman07} for example) have shown that modes above $L_b$ contribute very little to parameter constraints.
+Moreover, the purpose of this work is to estimate the parameter constraints achievable in a weak lensing analysis incorporating tomography, not to produce simulations accurate enough for analyzing the data set that will be available from LSST and other surveys a decade hence.
+To analyze the datasets that these surveys will produce, mode couplings between large and small scales, which can cause effects such as super sample covariance \citep{Sato12,SSC1,SSC2}, will need to be included.
+Baryonic effects will need to be included as well.
+Larger and more accurate $N$--body simulation techniques are currently under development in the community for this purpose \citep{Qcontinuum,HACC}.}
+
 The three dimensional outputs of the $N$--body simulations are sliced in sequences of two dimensional lenses $120 \,{\rm Mpc}$ thick, which are lined up perpendicular to the line of sight between the observer on Earth and a source at redshift $z_s$.
@@
 Because the $\kappa$ field is statistically isotropic, the expectation value $\langle\rangle$, for each realization $r$, is taken over all modes $\pmb{\ell}$ with the same magnitude $\ell=\vert\pmb{\ell}\vert$.
+{\bf \color{red} Given the fact that our simulation box is small, and we are ignoring non--linear couplings between large and small scale modes, we are likely underestimating the $\kappa$ power spectrum when performing ensemble averages based on a single $N$--body box.
+\citep{NbodySample} estimated the effect of a varying box size on the 3D matter power spectrum, for boxes up to 512Mpc$/h$ in size and found the variations to be small compared to their sample variance, on spatial wavenumbers up to $k\sim 0.3h{\rm Mpc}^{-1}$.
+}
+
 The peak count statistic $n_{\rm pk}(\nu,\bar{z}_b)$ is defined as the number of the local maxima of a certain height $\kappa_{\rm max}=\nu\sigma_0$, where $\sigma_0$ is the standard deviation over all pixels.
@@
 In the next section, we describe the statistical methods we use to infer cosmological parameter estimates $\bbh{p}$ from simulated observations $\h{\kappa}_{\rm obs}(\pmb{\theta}_p,\bar{z}_b)$ using the summary statistics $P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})$, $n_{\rm pk}(\nu,\bar{z}_b)$ and $\pmb{\mu}(\bar{z}_b)$.
+{\bf \color{red} Concerns might arise on the accuracy with which our simulations measure the summary statistics mentioned above, given the small box size and the fact that we recycle a single $N$--body box for building our simulated sample.
+\citep{PetriVariance} studied the dependence of the power spectrum and peak counts sample means as a function of the number of independent $N$--body boxes and found that the variations are less than 10\% in most cases, except for the small scale power spectrum and the highest $\kappa$ peaks, for which the variations are less than 20\%.
+}
 
@@
 This procedure allows us to forecast the results an LSST-like survey would obtain.
+{ \bf \color{red} We stress that, because of the small size of our simulation box the covariance estimate that we obtain is likely not accurate enough to produce constraints from LSST data.
+Full treatment of observables covariance matrices, along with larger $N$--body simulations and SSC effects will be investigated in future work.}
 
@@
 Figure \ref{fig:photozbias} clearly show that photo-$z$ errors cause parameter biases at more than $1\sigma$ significance level when using the power spectrum and the moments, while no bias is observed for the peak count statistic within its 68\% confidence region.
+{\bf \color{red} Peak histogram shapes are more robust to this kind of systematic effect since the peak locations are determined by the information coming from neighboring galaxies, while the photo-z errors have no spatial correlation.
+Photo-z errors are more likely to alter point estimates of the $\kappa$ distribution and larger scale correlations which affect the power spectrum.}
+
 We also observe that photo-$z$ errors bias the constraints in slightly different directions, leaving open the possibility of identifying and correcting this bias through self-calibration techniques.

### 2016-10-06 photoz_paper/paper.tex
removed red typeface

--- 2016-05-03 photoz_paper/paper.tex
@@
 In this work we concentrate on the constraining power of a subset of non-Gaussian statistics, combined with redshift tomography in an LSST-like survey.
+\citep{MartinetPeaksTomo} investigated the cosmological constraining power of shear peaks tomography.
 Previous work on redshift tomography with weak lensing Minkowski functionals is also present in the literature \citep{MinkJan}.
@@
 The simulations have a comoving box size of $L_b=260\,{\rm Mpc}/h$ and contain $512^3$ dark matter particles, which correspond to a mass resolution of $M_p\approx 10^{10}M_{\rm sun}$ per particle.
+
+The largest mode observed in our $N$--body simulations corresponds to a wavenumber of $k_b\approx1/L_b\approx 0.004 h{\rm Mpc}^{-1}$.
+For the sake of recovering cosmological information from WL, this limitation does not create a concern, as several authors (see \citep{FangHaiman07} for example) have shown that modes above $L_b$ contribute very little to parameter constraints.
+Moreover, the purpose of this work is to estimate the parameter constraints achievable in a weak lensing analysis incorporating tomography, not to produce simulations accurate enough for analyzing the data set that will be available from LSST and other surveys a decade hence.
+To analyze the datasets that these surveys will produce, mode couplings between large and small scales, which can cause effects such as super sample covariance \citep{Sato12,SSC1,SSC2}, will need to be included.
+Baryonic effects will need to be included as well.
+Larger and more accurate $N$--body simulation techniques are currently under development in the community for this purpose \citep{Qcontinuum,HACC}.
+
 The three dimensional outputs of the $N$--body simulations are sliced in sequences of two dimensional lenses $120 \,{\rm Mpc}$ thick, which are lined up perpendicular to the line of sight between the observer on Earth and a source at redshift $z_s$.
@@
 Because the $\kappa$ field is statistically isotropic, the expectation value $\langle\rangle$, for each realization $r$, is taken over all modes $\pmb{\ell}$ with the same magnitude $\ell=\vert\pmb{\ell}\vert$.
+Given the fact that our simulation box is small, and we are ignoring non--linear couplings between large and small scale modes, we are likely underestimating the $\kappa$ power spectrum when performing ensemble averages based on a single $N$--body box.
+\citep{NbodySample} estimated the effect of a varying box size on the 3D matter power spectrum, for boxes up to 512Mpc$/h$ in size and found the variations to be small compared to their sample variance, on spatial wavenumbers up to $k\sim 0.3h{\rm Mpc}^{-1}$.
+
 The peak count statistic $n_{\rm pk}(\nu,\bar{z}_b)$ is defined as the number of the local maxima of a certain height $\kappa_{\rm max}=\nu\sigma_0$, where $\sigma_0$ is the standard deviation over all pixels.
@@
 In the next section, we describe the statistical methods we use to infer cosmological parameter estimates $\bbh{p}$ from simulated observations $\h{\kappa}_{\rm obs}(\pmb{\theta}_p,\bar{z}_b)$ using the summary statistics $P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})$, $n_{\rm pk}(\nu,\bar{z}_b)$ and $\pmb{\mu}(\bar{z}_b)$.
+Concerns might arise on the accuracy with which our simulations measure the summary statistics mentioned above, given the small box size and the fact that we recycle a single $N$--body box for building our simulated sample.
+\citep{PetriVariance} studied the dependence of the power spectrum and peak counts sample means as a function of the number of independent $N$--body boxes and found that the variations are less than 10\% in most cases, except for the small scale power spectrum and the highest $\kappa$ peaks, for which the variations are less than 20\%.
 
@@
 This procedure allows us to forecast the results an LSST-like survey would obtain.
+We stress that, because of the small size of our simulation box the covariance estimate that we obtain is likely not accurate enough to produce constraints from LSST data.
+Full treatment of observables covariance matrices, along with larger $N$--body simulations and SSC effects will be investigated in future work.
 
@@
 Figure \ref{fig:photozbias} clearly show that photo-$z$ errors cause parameter biases at more than $1\sigma$ significance level when using the power spectrum and the moments, while no bias is observed for the peak count statistic within its 68\% confidence region.
+Peak histogram shapes are more robust to this kind of systematic effect since the peak locations are determined by the information coming from neighboring galaxies, while the photo-z errors have no spatial correlation.
+Photo-z errors are more likely to alter point estimates of the $\kappa$ distribution and larger scale correlations which affect the power spectrum.
+
 We also observe that photo-$z$ errors bias the constraints in slightly different directions, leaving open the possibility of identifying and correcting this bias through self-calibration techniques.
